---
title: "Analysis"
author: "Yuchan Mou"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.table.format = "html")
```

```{r load packages, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages <- c("MASS", "tidyverse", "mice", "tableone", "openxlsx")
sapply(packages, library, character.only = T)
```

```{r load packages2, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages_2 <- c("tidyverse", "readxl", "data.table", "gt", "writexl")
sapply(packages_2, library, character.only = T)
```


```{r import data}
load("/Users/ymou/helix_project/data/analysis_data/imp_full_ds.Rdata")
analysis_date <- Sys.Date()
```

```{r define variables, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# Exposures: air pollutants and noise level
ap <- c(
  "hs_no2_yr_hs_t",
  "hs_pm25_yr_hs_t",
  "hs_pm25abs_yr_hs_t",
  "hs_pm10_yr_hs_t"
)
ap_supl <- c(
  "hs_no2_yr_hs_h", "hs_no2_yr_hs_s", "hs_no2_yr_hs_r", "hs_no2_yr_hs_p",
  "hs_pm25_yr_hs_h", "hs_pm25_yr_hs_s", "hs_pm25_yr_hs_r", "hs_pm25_yr_hs_p",
  "hs_pm25abs_yr_hs_h", "hs_pm25abs_yr_hs_s", "hs_pm25abs_yr_hs_r", "hs_pm25abs_yr_hs_p",
  "hs_pm10_yr_hs_h", "hs_pm10_yr_hs_s", "hs_pm10_yr_hs_r", "hs_pm10_yr_hs_p"
)


# Outcomes: ALS
out <- c("AL_2_tot", "AL_2_tot_wavg", "AL_z2_tot", "AL_z2_tot_wavg") # sex-specific scores

# Outcomes per physiological systems
out_ps <- c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro", "AL_2_cardio_wavg", "AL_2_metab_wavg", "AL_2_immune_wavg", "AL_2_neuro_wavg")
out_ps_z <- c("AL_z2_cardio", "AL_z2_metab", "AL_z2_immune", "AL_z2_neuro", "AL_z2_cardio_wavg", "AL_z2_metab_wavg", "AL_z2_immune_wavg", "AL_z2_neuro_wavg")


# Models
# full adjusted model is the last model
model <- c(
  "e3_sex + hs_child_age_years + h_ethnicity_cauc",
  "e3_sex + hs_child_age_years + h_ethnicity_cauc + hs_mvpa + hs_sd_wk",
  "e3_sex + hs_child_age_years + h_ethnicity_cauc + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn",
  "e3_sex + hs_child_age_years + h_ethnicity_cauc + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn + hs_globalexp_2cat"
)

# Output directory
outdir <- "/Users/ymou/helix_project/results/sensitivity_analysis/"
```

# Apply increments

```{r}
#  1 micrograms per cubic meter µg/m3 -> 
dat_afimp <- complete(imp_full, action = "long", include = T) %>%
  mutate(
    hs_no2_yr_hs_t = hs_no2_yr_hs_t / 10,
    hs_no2_yr_hs_h = hs_no2_yr_hs_h / 10,
    hs_no2_yr_hs_s = hs_no2_yr_hs_s / 10,
    hs_no2_yr_hs_r = hs_no2_yr_hs_r / 10,
    hs_no2_yr_hs_p = hs_no2_yr_hs_p / 10,
    hs_pm25_yr_hs_t = hs_pm25_yr_hs_t / 5,
    hs_pm25_yr_hs_h = hs_pm25_yr_hs_h / 5,
    hs_pm25_yr_hs_s = hs_pm25_yr_hs_s / 5,
    hs_pm25_yr_hs_r = hs_pm25_yr_hs_r / 5,
    hs_pm25_yr_hs_p = hs_pm25_yr_hs_p / 5,
    hs_pm10_yr_hs_t = hs_pm10_yr_hs_t / 10,
    hs_pm10_yr_hs_h = hs_pm10_yr_hs_h / 10,
    hs_pm10_yr_hs_s = hs_pm10_yr_hs_s / 10,
    hs_pm10_yr_hs_r = hs_pm10_yr_hs_r / 10,
    hs_pm10_yr_hs_p = hs_pm10_yr_hs_p / 10
  )

dat_afimp_al_nonimp <- dat_afimp %>% 
  filter(incl_var_out == 1)

# imputed dataset with full set of variables and all participants
imp_full <- as.mids(dat_afimp_al_nonimp)
```

# ALS of each physiological system associated with road traffic noise levels
## Count-based ALS
```{r}
noise_psystem <- read_excel("/Users/ymou/helix_project/results/noise_outcomepsystem2024-03-21.xlsx")
```

```{r etbl2}
noise_psystem %>%
  dplyr::select(Outcome, Predictor, exp_beta_mod4, exp_ci_mod4) %>%
  dplyr::filter(Outcome == "AL_2_cardio" | Outcome == "AL_2_immune" | Outcome == "AL_2_metab" | 
         Outcome == "AL_2_neuro") %>% 
  gt() %>% 
  tab_header(
    title = "eTable 2. Adjusted relative risk of count-based allostatic load score of each physiological system associated with road traffic noise levels"
  ) %>% 
  fmt_number(decimals = 2, drop_trailing_zeros = F) %>% 
  gt::gtsave(., "/Users/ymou/helix_project/results/Table/eTable2.docx")
```

## Continuous ALS
```{r}
noise_psystem_zscore <- read_excel("/Users/ymou/helix_project/results/noise_outcomepsystem_zscore2024-03-21.xlsx")
```

```{r etbl3}
noise_psystem_zscore %>%
  dplyr::select(Outcome, Predictor, beta_mod4, `95ci_mod4`) %>%
  dplyr::filter(Outcome == "AL_z2_cardio" | Outcome == "AL_z2_immune" | Outcome == "AL_z2_metab" | 
         Outcome == "AL_z2_neuro") %>% 
  gt() %>% 
  tab_header(
    title = "eTable 3. Adjusted effect estimates of continuous allostatic load score of each physiological system associated with road traffic noise levels"
  ) %>% 
  fmt_number(decimals = 2, drop_trailing_zeros = F) %>% 
  gt::gtsave(., "/Users/ymou/helix_project/results/Table/eTable3.docx")
```

# ANALYSIS: highest 25th percentiles of cortisol cut-offs as "high risk"

```{r define biomarkers, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# 19 biomarkers included in the main AL score
# hs_non_hdl_c is calculated with hs_totchol_c - hs_hdlchol_c
biomarker_all <- c(
  "hs_zsys_bp", "hs_zdia_bp", "bp_pulse_sd",
  "hs_zbmi_who", "hs_zwaist_mets", "hs_skf_sum2", "hs_fatprop_bia",
  "hs_hdlchol_c", "hs_non_hdl_c", "hs_triglyc_c", "Leptin",
  "Adiponectin",
  "CRP", "IL1beta", "IL6", "IL8", "IL10", "TNFalfa",
  "cortisol_prod_log10"
)

biomarker_positivescore <- c(
  "hs_zsys_bp", "hs_zdia_bp", "bp_pulse_sd",
  "hs_zbmi_who", "hs_zwaist_mets", "hs_skf_sum2", "hs_fatprop_bia",
  "hs_non_hdl_c", "hs_triglyc_c", "Leptin",
  "CRP", "IL1beta", "IL6", "IL8", "TNFalfa"
)
biomarker_reversescore <- c(
  "hs_hdlchol_c", "Adiponectin", "IL10", "cortisol_prod_log10"
)

# 4 physiological systems
physystems <- c("cardio", "metab", "immune", "neuro")

cardio <- c("hs_zsys_bp", "hs_zdia_bp", "bp_pulse_sd") # 3 biomarkers
metab <- c(
  "hs_zbmi_who", "hs_zwaist_mets", "hs_skf_sum2", "hs_fatprop_bia",
  "hs_hdlchol_c", "hs_non_hdl_c", "hs_triglyc_c", "Leptin", "Adiponectin"
) # 9 biomarkers
immune <- c("CRP", "IL1beta", "IL6", "IL8", "IL10", "TNFalfa") # 6 biomarkers
neuro <- c("cortisol_prod_log10") # 1 biomarkers
```

## Define function to calculate new ALS
```{r}
#' @description Function to automatically apply AL cut-off values
#' @param data: data.frame that contains the biomarkers
#' @param scoreno: character that indicates which AL cutoffs should be use (options: 'cut-off score','continuous score')
#' @param biomarkers: Character vector that includes the biomarkers to serve as colnames
#' @param biomarker_positivescore: Character vector that includes the biomarkers with positive scoring
#' @param biomarker_reversescore: Character vector that includes the biomarkers with reverse scoring

ALscore <- function(data, scoreno, biomarkers, biomarker_positivescore, biomarker_reversescore) {
  if ("cut-off score" %in% scoreno) {
    df_q <- data %>%
      dplyr::select(HelixID, e3_sex, all_of(biomarkers)) %>%
      mutate(
        across(
          .cols = all_of(biomarkers)[1:19],
          .fns = \(x) ntile(x, n = 4),
          .names = "{col}_q"
        )
      ) %>% 
      dplyr::select(HelixID, e3_sex, ends_with("_q"))

    # make quartiles
    # positive scoring
    biomarker_q <- paste(biomarker_positivescore, "q", sep = "_")
    df_q <- df_q %>% mutate(
      across(
        .cols = all_of(biomarker_q),
        .fns = \(x) if_else(x == 4, 1, 0, NA),
        .names = "{col}_as1"
      )
    )

    # reverse scoring
    biomarker_q <- paste(biomarker_reversescore, "q", sep = "_")
    df_q <- df_q %>% mutate(
      across(
        .cols = all_of(biomarker_q),
        .fns = \(x) if_else(x == 1, 1, 0, NA),
        .names = "{col}_as1"
      )
    )


    # summary score
    cardio_q <- paste(cardio, "q_as1", sep = "_")
    metab_q <- paste(metab, "q_as1", sep = "_")
    immune_q <- paste(immune, "q_as1", sep = "_")
    neuro_q <- paste(neuro, "q_as1", sep = "_")
    # formula
    cardio_sum <- paste(cardio_q, collapse = " + ")
    metab_sum <- paste(metab_q, collapse = " + ")
    immune_sum <- paste(immune_q, collapse = " + ")
    neuro_sum <- paste(neuro_q, collapse = " + ")

    df_q <- df_q %>%
      mutate(
        AL_1_cardio = rlang::eval_tidy(rlang::parse_expr(cardio_sum), data = .),
        AL_1_metab = rlang::eval_tidy(rlang::parse_expr(metab_sum), data = .),
        AL_1_immune = rlang::eval_tidy(rlang::parse_expr(immune_sum), data = .),
        AL_1_neuro = rlang::eval_tidy(rlang::parse_expr(neuro_sum), data = .),
        AL_1_tot = AL_1_cardio + AL_1_metab + AL_1_immune + AL_1_neuro
      )

    # weighted average score
    # formula
    cardio_wgtsum <- paste0("(", paste(cardio_q, collapse = " + "), ")/", length(cardio_q), sep = "")
    metab_wgtsum <- paste0("(", paste(metab_q, collapse = " + "), ")/", length(metab_q), sep = "")
    immune_wgtsum <- paste0("(", paste(immune_q, collapse = " + "), ")/", length(immune_q), sep = "")
    neuro_wgtsum <- paste0("(", paste(neuro_q, collapse = " + "), ")/", length(neuro_q), sep = "")

    df_q <- df_q %>%
      mutate(
        AL_1_cardio_wavg = rlang::eval_tidy(rlang::parse_expr(cardio_wgtsum), data = .),
        AL_1_metab_wavg = rlang::eval_tidy(rlang::parse_expr(metab_wgtsum), data = .),
        AL_1_immune_wavg = rlang::eval_tidy(rlang::parse_expr(immune_wgtsum), data = .),
        AL_1_neuro_wavg = rlang::eval_tidy(rlang::parse_expr(neuro_wgtsum), data = .),
        AL_1_tot_wavg = AL_1_cardio_wavg + AL_1_metab_wavg + AL_1_immune_wavg + AL_1_neuro_wavg
      )

    # final dataset
    # assign different score names (AL_2_) to the sex-specific allostatic load score, based on girls and boys separately
    # AL_1 is the allostatic load score based on the whole population
    # AL_2 is the sex-specific allostatic load score
    # df_q <- df_q %>% select(-matches("_q$|_as1$"))
    if (nrow(df_q) < 1301) {
      df_q <- df_q %>% 
        rename(
          AL_2_cardio = AL_1_cardio,
          AL_2_metab = AL_1_metab,
          AL_2_immune = AL_1_immune,
          AL_2_neuro = AL_1_neuro,
          AL_2_tot = AL_1_tot,
          AL_2_cardio_wavg = AL_1_cardio_wavg,
          AL_2_metab_wavg = AL_1_metab_wavg,
          AL_2_immune_wavg = AL_1_immune_wavg,
          AL_2_neuro_wavg = AL_1_neuro_wavg,
          AL_2_tot_wavg = AL_1_tot_wavg
        )
    }
  }
  if ("continuous score" %in% scoreno) {
    # positive scoring
    df_z <- data %>%
      dplyr::select(HelixID, e3_sex, all_of(biomarkers)) %>%
      mutate(
        across(
          .cols = all_of(biomarkers),
          .fns = ~ rescale(.x, to = c(0, 1)), # rescale a variable with min = 0 and max = 1. Linear rescaling will not change the shape of the distribution.
          .names = "{col}_z"
        )
      ) %>%
      mutate(across(ends_with("_z"), as.numeric)) %>%
      dplyr::select(HelixID, e3_sex, ends_with("_z"))

    # reverse scoring
    biomarker_z <- paste(biomarker_reversescore, "z", sep = "_")
    df_z <- df_z %>% mutate(
      across(
        .cols = all_of(biomarker_z),
        .fns = \(x) (1 - x),
        .names = "{col}"
      )
    )

    # summary score
    cardio_z <- paste(cardio, "z", sep = "_")
    metab_z <- paste(metab, "z", sep = "_")
    immune_z <- paste(immune, "z", sep = "_")
    neuro_z <- paste(neuro, "z", sep = "_")
    # formula
    cardio_zsum <- paste(cardio_z, collapse = " + ")
    metab_zsum <- paste(metab_z, collapse = " + ")
    immune_zsum <- paste(immune_z, collapse = " + ")
    neuro_zsum <- paste(neuro_z, collapse = " + ")

    df_z <- df_z %>%
      mutate(
        AL_z1_cardio = rlang::eval_tidy(rlang::parse_expr(cardio_zsum), data = .),
        AL_z1_metab = rlang::eval_tidy(rlang::parse_expr(metab_zsum), data = .),
        AL_z1_immune = rlang::eval_tidy(rlang::parse_expr(immune_zsum), data = .),
        AL_z1_neuro = rlang::eval_tidy(rlang::parse_expr(neuro_zsum), data = .),
        AL_z1_tot = AL_z1_cardio + AL_z1_metab + AL_z1_immune + AL_z1_neuro
      )

    # weighted average score
    # formula
    cardio_wgtzsum <- paste0("(", paste(cardio_z, collapse = " + "), ")/", length(cardio_z), sep = "")
    metab_wgtzsum <- paste0("(", paste(metab_z, collapse = " + "), ")/", length(metab_z), sep = "")
    immune_wgtzsum <- paste0("(", paste(immune_z, collapse = " + "), ")/", length(immune_z), sep = "")
    neuro_wgtzsum <- paste0("(", paste(neuro_z, collapse = " + "), ")/", length(neuro_z), sep = "")

    df_z <- df_z %>%
      mutate(
        AL_z1_cardio_wavg = rlang::eval_tidy(rlang::parse_expr(cardio_wgtzsum), data = .),
        AL_z1_metab_wavg = rlang::eval_tidy(rlang::parse_expr(metab_wgtzsum), data = .),
        AL_z1_immune_wavg = rlang::eval_tidy(rlang::parse_expr(immune_wgtzsum), data = .),
        AL_z1_neuro_wavg = rlang::eval_tidy(rlang::parse_expr(neuro_wgtzsum), data = .),
        AL_z1_tot_wavg = AL_z1_cardio_wavg + AL_z1_metab_wavg + AL_z1_immune_wavg + AL_z1_neuro_wavg
      )

    # final dataset
    # df_z <- df_z %>% select(-matches("_z$"))
    # assign different score name to the AL score based on sub-population (girls and boys separately)
    if (nrow(df_z) < 1301) {
      df_z <- df_z %>% 
        rename(
          AL_z2_cardio = AL_z1_cardio,
          AL_z2_metab = AL_z1_metab,
          AL_z2_immune = AL_z1_immune,
          AL_z2_neuro = AL_z1_neuro,
          AL_z2_tot = AL_z1_tot,
          AL_z2_cardio_wavg = AL_z1_cardio_wavg,
          AL_z2_metab_wavg = AL_z1_metab_wavg,
          AL_z2_immune_wavg = AL_z1_immune_wavg,
          AL_z2_neuro_wavg = AL_z1_neuro_wavg,
          AL_z2_tot_wavg = AL_z1_tot_wavg
        )
    }
  }
  if (exists("df_q")) {
    assign("ALScore_cutoff", df_q, envir = .GlobalEnv)
  }
  if (exists("df_z")) {
    assign("ALScore_z", df_z, envir = .GlobalEnv)
  }
}
```

## Calculate new ALS
```{r}
# create 25 imputed datasets
num <- 0
repeat{
  num = num+1
  dd <- complete(imp_full, num)
  dd_g <- dd %>% filter(e3_sex == "Girls")
  assign(paste('a.g',num,sep=""), dd_g, envir = .GlobalEnv)
  
  dd_b <- dd %>% filter(e3_sex == "Boys")
  assign(paste('a.b',num,sep=""), dd_b, envir = .GlobalEnv)

  if (num == 25){
    print("repeat loop ends");
    break
  }
}

list_a.g <- list(a.g1, a.g2, a.g3, a.g4, a.g5, a.g6, a.g7, a.g8, a.g9, a.g10, a.g11, a.g12, a.g13,
a.g14, a.g15, a.g16, a.g17, a.g18, a.g19, a.g20, a.g21, a.g22, a.g23, a.g24, a.g25)

list_a.b <- list(a.b1, a.b2, a.b3, a.b4, a.b5, a.b6, a.b7, a.b8, a.b9, a.b10, a.b11, a.b12, a.b13,
a.b14, a.b15, a.b16, a.b17, a.b18, a.b19, a.b20, a.b21, a.b22, a.b23, a.b24, a.b25)
```

```{r}
# Calculate ALS a1
# Dataset girls
dsnum <- 0
repeat{
  dsnum <- dsnum+1
  ALscore(data = list_a.g[[dsnum]], scoreno = "cut-off score", biomarkers = biomarker_all,
          biomarker_positivescore, biomarker_reversescore)
  ALscore(data = list_a.g[[dsnum]], scoreno = "continuous score", biomarkers = biomarker_all,
          biomarker_positivescore, biomarker_reversescore)

  df <- cbind(list_a.g[[dsnum]], 
              AL_2_total_a1 = ALScore_cutoff$AL_2_tot, 
              AL_2_cardio_a1 = ALScore_cutoff$AL_2_cardio,
              AL_2_metabolic_a1 = ALScore_cutoff$AL_2_metab, 
              AL_2_immune_a1 = ALScore_cutoff$AL_2_immune,
              AL_2_neuro_a1 = ALScore_cutoff$AL_2_neuro,
              AL_z2_tot_a1 = ALScore_z$AL_z2_tot,
              AL_z2_cardio_a1 = ALScore_z$AL_z2_cardio, 
              AL_z2_metab_a1 = ALScore_z$AL_z2_metab, 
              AL_z2_immune_a1 = ALScore_z$AL_z2_immune, 
              AL_z2_neuro_a1 = ALScore_z$AL_z2_neuro)
  assign(paste("Sup_ag", dsnum, sep = ""), df)
  rm(df)
  if (dsnum == 25){
    SupsetG_complete <- lapply(ls(pattern = "^Sup_"), get)
    rm(list = ls(pattern = "^Sup_"))
    rm(list = ls(pattern = "^ALScore"))
    print("repeat loop ends");
    break
  }
}

rm(list = ls(pattern = "(^a\\.g)"))

# Dataset girls
dsnum <- 0
repeat{
  dsnum <- dsnum+1
  ALscore(data = list_a.b[[dsnum]], scoreno = "cut-off score", biomarkers = biomarker_all,
          biomarker_positivescore, biomarker_reversescore)
  ALscore(data = list_a.b[[dsnum]], scoreno = "continuous score", biomarkers = biomarker_all,
          biomarker_positivescore, biomarker_reversescore)

  df <- cbind(list_a.b[[dsnum]], 
              AL_2_total_a1 = ALScore_cutoff$AL_2_tot, 
              AL_2_cardio_a1 = ALScore_cutoff$AL_2_cardio,
              AL_2_metabolic_a1 = ALScore_cutoff$AL_2_metab, 
              AL_2_immune_a1 = ALScore_cutoff$AL_2_immune,
              AL_2_neuro_a1 = ALScore_cutoff$AL_2_neuro,
              AL_z2_tot_a1 = ALScore_z$AL_z2_tot,
              AL_z2_cardio_a1 = ALScore_z$AL_z2_cardio, 
              AL_z2_metab_a1 = ALScore_z$AL_z2_metab, 
              AL_z2_immune_a1 = ALScore_z$AL_z2_immune, 
              AL_z2_neuro_a1 = ALScore_z$AL_z2_neuro)
  assign(paste("Sup_ag", dsnum, sep = ""), df)
  rm(df)
  if (dsnum == 25){
    SupsetB_complete <- lapply(ls(pattern = "^Sup_"), get)
    rm(list = ls(pattern = "^Sup_"))
    rm(list = ls(pattern = "^ALScore"))
    print("repeat loop ends");
    break
  }
}

rm(list = ls(pattern = "(^a\\.b)"))

# Combine lists of datasets of girls and boys
Supset_complete <- Map(bind_rows, SupsetG_complete, SupsetB_complete)

# Combine list back to MIDS object to use the pool function of R again
library(miceadds)
Suppl_impset  <- datalist2mids(Supset_complete) 
```

RUN ANALYSIS with new sets of ALS with the highest quartile of cortisol production labelled as 'high risk'
```{r define variables, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# Exposures: air pollutants and noise level
ap <- c(
  "hs_no2_yr_hs_t",
  "hs_pm25_yr_hs_t",
  "hs_pm25abs_yr_hs_t",
  "hs_pm10_yr_hs_t"
)
ap_supl <- c(
  "hs_no2_yr_hs_h", "hs_no2_yr_hs_s", "hs_no2_yr_hs_r", "hs_no2_yr_hs_p",
  "hs_pm25_yr_hs_h", "hs_pm25_yr_hs_s", "hs_pm25_yr_hs_r", "hs_pm25_yr_hs_p",
  "hs_pm25abs_yr_hs_h", "hs_pm25abs_yr_hs_s", "hs_pm25abs_yr_hs_r", "hs_pm25abs_yr_hs_p",
  "hs_pm10_yr_hs_h", "hs_pm10_yr_hs_s", "hs_pm10_yr_hs_r", "hs_pm10_yr_hs_p"
)
noise <- c("hs_lden_c_h", "hs_lden_c_s")
noise_supl <- c("hs_lden_h", "hs_lden_s", "hs_lden_t")


# Outcomes: AL scores
out <- c("AL_2_total_a1", "AL_z2_tot_a1") # sex-specific scores

# Outcomes per physiological systems
out_ps <- c("AL_2_cardio_a1", "AL_2_metabolic_a1", "AL_2_immune_a1", "AL_2_neuro_a1")
out_ps_z <- c("AL_z2_cardio_a1", "AL_z2_metab_a1", "AL_z2_immune_a1", "AL_z2_neuro_a1")


# Models
model <- c(
  "e3_sex + hs_child_age_years + h_ethnicity_cauc",
  "e3_sex + hs_child_age_years + h_ethnicity_cauc + hs_mvpa + hs_sd_wk",
  "e3_sex + hs_child_age_years + h_ethnicity_cauc + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn",
  "e3_sex + hs_child_age_years + h_ethnicity_cauc + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn + hs_globalexp_2cat"
)
```

### Air pollution total and main outcomes
```{r}
analysis <- "airpollution_total_mainoutcome"

coefs <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out) {
  if (o %in% c("AL_2_total_a1")) {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- Suppl_impset %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs[count, 1] <- gsub(" ", "_", Sys.time())
        coefs[count, 2] <- o
        coefs[count, 3] <- d
        coefs[count, 4] <- m
        coefs[count, 5] <- res$estimate[2]
        coefs[count, 6] <- res$`2.5 %`[2]
        coefs[count, 7] <- res$`97.5 %`[2]
        coefs[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- Suppl_impset %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs[count, 1] <- gsub(" ", "_", Sys.time())
        coefs[count, 2] <- o
        coefs[count, 3] <- d
        coefs[count, 4] <- m
        coefs[count, 5] <- res$estimate[2]
        coefs[count, 6] <- res$`2.5 %`[2]
        coefs[count, 7] <- res$`97.5 %`[2]
        coefs[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs[count, 9] <- res$p.value[2]
      }
    }
  }
}


mod_tbl <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in ap) {
    sep_coefs <- coefs %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl[count, 1] <- o
    mod_tbl[count, 2] <- d
    mod_tbl[count, 3] <- sep_coefs$Beta[1]
    mod_tbl[count, 4] <- sep_coefs$CI[1]
    mod_tbl[count, 5] <- sep_coefs$P[1]
    mod_tbl[count, 6] <- sep_coefs$Beta[2]
    mod_tbl[count, 7] <- sep_coefs$CI[2]
    mod_tbl[count, 8] <- sep_coefs$P[2]
    mod_tbl[count, 9] <- sep_coefs$Beta[3]
    mod_tbl[count, 10] <- sep_coefs$CI[3]
    mod_tbl[count, 11] <- sep_coefs$P[3]
    mod_tbl[count, 12] <- sep_coefs$Beta[4]
    mod_tbl[count, 13] <- sep_coefs$CI[4]
    mod_tbl[count, 14] <- sep_coefs$P[4]
    mod_tbl[count, 15] <- sep_coefs$cilo[4]
    mod_tbl[count, 16] <- sep_coefs$cihi[4]
  }
}

mod_tbl <- mod_tbl %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_total_a1"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_total_a1"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_total_a1"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl, file = paste("/Users/ymou/helix_project/results/sensitivity_analysis/cortisol_highestquartile_ALS/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

### Air pollution total and outcomes per physiological systems
```{r}
analysis <- "airpollution_total_outcomepsystem"

coefs1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs1) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio_a1", "AL_2_metabolic_a1", "AL_2_immune_a1", "AL_2_neuro_a1")) {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- Suppl_impset %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs1[count, 1] <- gsub(" ", "_", Sys.time())
        coefs1[count, 2] <- o
        coefs1[count, 3] <- d
        coefs1[count, 4] <- m
        coefs1[count, 5] <- res$estimate[2]
        coefs1[count, 6] <- res$`2.5 %`[2]
        coefs1[count, 7] <- res$`97.5 %`[2]
        coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs1[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- Suppl_impset %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs1[count, 1] <- gsub(" ", "_", Sys.time())
        coefs1[count, 2] <- o
        coefs1[count, 3] <- d
        coefs1[count, 4] <- m
        coefs1[count, 5] <- res$estimate[2]
        coefs1[count, 6] <- res$`2.5 %`[2]
        coefs1[count, 7] <- res$`97.5 %`[2]
        coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs1[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl1) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in ap) {
    sep_coefs1 <- coefs1 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl1[count, 1] <- o
    mod_tbl1[count, 2] <- d
    mod_tbl1[count, 3] <- sep_coefs1$Beta[1]
    mod_tbl1[count, 4] <- sep_coefs1$CI[1]
    mod_tbl1[count, 5] <- sep_coefs1$P[1]
    mod_tbl1[count, 6] <- sep_coefs1$Beta[2]
    mod_tbl1[count, 7] <- sep_coefs1$CI[2]
    mod_tbl1[count, 8] <- sep_coefs1$P[2]
    mod_tbl1[count, 9] <- sep_coefs1$Beta[3]
    mod_tbl1[count, 10] <- sep_coefs1$CI[3]
    mod_tbl1[count, 11] <- sep_coefs1$P[3]
    mod_tbl1[count, 12] <- sep_coefs1$Beta[4]
    mod_tbl1[count, 13] <- sep_coefs1$CI[4]
    mod_tbl1[count, 14] <- sep_coefs1$P[4]
    mod_tbl1[count, 15] <- sep_coefs1$cilo[4]
    mod_tbl1[count, 16] <- sep_coefs1$cihi[4]
  }
}

mod_tbl1 <- mod_tbl1 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio_a1", "AL_2_metabolic_a1", "AL_2_immune_a1", "AL_2_neuro_a1") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio_a1", "AL_2_metabolic_a1", "AL_2_immune_a1", "AL_2_neuro_a1") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio_a1", "AL_2_metabolic_a1", "AL_2_immune_a1", "AL_2_neuro_a1") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl1, file = paste("/Users/ymou/helix_project/results/sensitivity_analysis/cortisol_highestquartile_ALS/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "airpollution_total_outcomepsystem_zscore"

coefs1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs1) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps_z) {
  for (d in ap) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <- Suppl_impset %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)

      # Save results
      coefs1[count, 1] <- gsub(" ", "_", Sys.time())
      coefs1[count, 2] <- o
      coefs1[count, 3] <- d
      coefs1[count, 4] <- m
      coefs1[count, 5] <- res$estimate[2]
      coefs1[count, 6] <- res$`2.5 %`[2]
      coefs1[count, 7] <- res$`97.5 %`[2]
      coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs1[count, 9] <- res$p.value[2]
    }
  }
}

mod_tbl1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl1) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in ap) {
    sep_coefs1 <- coefs1 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl1[count, 1] <- o
    mod_tbl1[count, 2] <- d
    mod_tbl1[count, 3] <- sep_coefs1$Beta[1]
    mod_tbl1[count, 4] <- sep_coefs1$CI[1]
    mod_tbl1[count, 5] <- sep_coefs1$P[1]
    mod_tbl1[count, 6] <- sep_coefs1$Beta[2]
    mod_tbl1[count, 7] <- sep_coefs1$CI[2]
    mod_tbl1[count, 8] <- sep_coefs1$P[2]
    mod_tbl1[count, 9] <- sep_coefs1$Beta[3]
    mod_tbl1[count, 10] <- sep_coefs1$CI[3]
    mod_tbl1[count, 11] <- sep_coefs1$P[3]
    mod_tbl1[count, 12] <- sep_coefs1$Beta[4]
    mod_tbl1[count, 13] <- sep_coefs1$CI[4]
    mod_tbl1[count, 14] <- sep_coefs1$P[4]
    mod_tbl1[count, 15] <- sep_coefs1$cilo[4]
    mod_tbl1[count, 16] <- sep_coefs1$cihi[4]
  }
}


write.xlsx(mod_tbl1, file = paste("/Users/ymou/helix_project/results/sensitivity_analysis/cortisol_highestquartile_ALS/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

### Noise home, school and main outcomes
EDEN removed in the analysis because no data available. 
```{r}
analysis <- "noise_mainoutcome"

imp_full_noise <- complete(Suppl_impset, "long", include = T) %>%
  filter(cohort != "EDEN") %>%
  as.mids()

coefs4 <- as.data.frame(matrix(NA, nrow = 1, ncol = 19))
colnames(coefs4) <- c(
  "DateTime", "Outcome", "Predictor", "Model", "Beta1", "cilo1", "cihi1", "CI1", "P1",
  "Beta2", "cilo2", "cihi2", "CI2", "P2", "Beta3", "cilo3", "cihi3", "CI3", "P3"
)

count <- 0
for (o in out) {
  if (o %in% c("AL_2_total_a1")) {
    for (d in noise) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full_noise %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs4[count, 1] <- gsub(" ", "_", Sys.time())
        coefs4[count, 2] <- o
        coefs4[count, 3] <- d
        coefs4[count, 4] <- m
        coefs4[count, 5] <- res$estimate[2]
        coefs4[count, 6] <- res$`2.5 %`[2]
        coefs4[count, 7] <- res$`97.5 %`[2]
        coefs4[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs4[count, 9] <- res$p.value[2]
        coefs4[count, 10] <- res$estimate[3]
        coefs4[count, 11] <- res$`2.5 %`[3]
        coefs4[count, 12] <- res$`97.5 %`[3]
        coefs4[count, 13] <- paste(res$`2.5 %`[3], ",", " ", res$`97.5 %`[3], sep = "")
        coefs4[count, 14] <- res$p.value[3]
        coefs4[count, 15] <- res$estimate[4]
        coefs4[count, 16] <- res$`2.5 %`[4]
        coefs4[count, 17] <- res$`97.5 %`[4]
        coefs4[count, 18] <- paste(res$`2.5 %`[4], ",", " ", res$`97.5 %`[4], sep = "")
        coefs4[count, 19] <- res$p.value[4]
      }
    }
  } else {
    for (d in noise) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full_noise %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs4[count, 1] <- gsub(" ", "_", Sys.time())
        coefs4[count, 2] <- o
        coefs4[count, 3] <- d
        coefs4[count, 4] <- m
        coefs4[count, 5] <- res$estimate[2]
        coefs4[count, 6] <- res$`2.5 %`[2]
        coefs4[count, 7] <- res$`97.5 %`[2]
        coefs4[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs4[count, 9] <- res$p.value[2]
        coefs4[count, 10] <- res$estimate[3]
        coefs4[count, 11] <- res$`2.5 %`[3]
        coefs4[count, 12] <- res$`97.5 %`[3]
        coefs4[count, 13] <- paste(res$`2.5 %`[3], ",", " ", res$`97.5 %`[3], sep = "")
        coefs4[count, 14] <- res$p.value[3]
        coefs4[count, 15] <- res$estimate[4]
        coefs4[count, 16] <- res$`2.5 %`[4]
        coefs4[count, 17] <- res$`97.5 %`[4]
        coefs4[count, 18] <- paste(res$`2.5 %`[4], ",", " ", res$`97.5 %`[4], sep = "")
        coefs4[count, 19] <- res$p.value[4]
      }
    }
  }
}

mod_tbl4 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl4) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in noise) {
    sep_coefs <- coefs4 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl4[count, 1] <- o
    mod_tbl4[count, 2] <- paste(d, "_55-59.9", sep = "")
    mod_tbl4[count, 3] <- sep_coefs$Beta1[1]
    mod_tbl4[count, 4] <- sep_coefs$CI1[1]
    mod_tbl4[count, 5] <- sep_coefs$P1[1]
    mod_tbl4[count, 6] <- sep_coefs$Beta1[2]
    mod_tbl4[count, 7] <- sep_coefs$CI1[2]
    mod_tbl4[count, 8] <- sep_coefs$P1[2]
    mod_tbl4[count, 9] <- sep_coefs$Beta1[3]
    mod_tbl4[count, 10] <- sep_coefs$CI1[3]
    mod_tbl4[count, 11] <- sep_coefs$P1[3]
    mod_tbl4[count, 12] <- sep_coefs$Beta1[4]
    mod_tbl4[count, 13] <- sep_coefs$CI1[4]
    mod_tbl4[count, 14] <- sep_coefs$P1[4]
    mod_tbl4[count, 15] <- sep_coefs$cilo1[4]
    mod_tbl4[count, 16] <- sep_coefs$cihi1[4]

    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl4[count, 1] <- o
    mod_tbl4[count, 2] <- paste(d, "_60-64.9 ", sep = "")
    mod_tbl4[count, 3] <- sep_coefs$Beta2[1]
    mod_tbl4[count, 4] <- sep_coefs$CI2[1]
    mod_tbl4[count, 5] <- sep_coefs$P2[1]
    mod_tbl4[count, 6] <- sep_coefs$Beta2[2]
    mod_tbl4[count, 7] <- sep_coefs$CI2[2]
    mod_tbl4[count, 8] <- sep_coefs$P2[2]
    mod_tbl4[count, 9] <- sep_coefs$Beta2[3]
    mod_tbl4[count, 10] <- sep_coefs$CI2[3]
    mod_tbl4[count, 11] <- sep_coefs$P2[3]
    mod_tbl4[count, 12] <- sep_coefs$Beta2[4]
    mod_tbl4[count, 13] <- sep_coefs$CI2[4]
    mod_tbl4[count, 14] <- sep_coefs$P2[4]
    mod_tbl4[count, 15] <- sep_coefs$cilo2[4]
    mod_tbl4[count, 16] <- sep_coefs$cihi2[4]

    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl4[count, 1] <- o
    mod_tbl4[count, 2] <- paste(d, ">=65 ", sep = "")
    mod_tbl4[count, 3] <- sep_coefs$Beta3[1]
    mod_tbl4[count, 4] <- sep_coefs$CI3[1]
    mod_tbl4[count, 5] <- sep_coefs$P3[1]
    mod_tbl4[count, 6] <- sep_coefs$Beta3[2]
    mod_tbl4[count, 7] <- sep_coefs$CI3[2]
    mod_tbl4[count, 8] <- sep_coefs$P3[2]
    mod_tbl4[count, 9] <- sep_coefs$Beta3[3]
    mod_tbl4[count, 10] <- sep_coefs$CI3[3]
    mod_tbl4[count, 11] <- sep_coefs$P3[3]
    mod_tbl4[count, 12] <- sep_coefs$Beta3[4]
    mod_tbl4[count, 13] <- sep_coefs$CI3[4]
    mod_tbl4[count, 14] <- sep_coefs$P3[4]
    mod_tbl4[count, 15] <- sep_coefs$cilo3[4]
    mod_tbl4[count, 16] <- sep_coefs$cihi3[4]
  }
}

mod_tbl4 <- mod_tbl4 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_total_a1"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_total_a1"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_total_a1"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl4, file = paste("/Users/ymou/helix_project/results/sensitivity_analysis/cortisol_highestquartile_ALS/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)

```


### Noise home, school and outcomes per physiological systems
EDEN removed in the analysis because no data available. 
```{r}
analysis <- "noise_outcomepsystem"

imp_full_noise <- complete(Suppl_impset, "long", include = T) %>%
  filter(cohort != "EDEN") %>%
  as.mids()

coefs5 <- as.data.frame(matrix(NA, nrow = 1, ncol = 19))
colnames(coefs5) <- c(
  "DateTime", "Outcome", "Predictor", "Model", "Beta1", "cilo1", "cihi1", "CI1", "P1",
  "Beta2", "cilo2", "cihi2", "CI2", "P2", "Beta3", "cilo3", "cihi3", "CI3", "P3"
)

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio_a1", "AL_2_metabolic_a1", "AL_2_immune_a1", "AL_2_neuro_a1")) {
    for (d in noise) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full_noise %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs5[count, 1] <- gsub(" ", "_", Sys.time())
        coefs5[count, 2] <- o
        coefs5[count, 3] <- d
        coefs5[count, 4] <- m
        coefs5[count, 5] <- res$estimate[2]
        coefs5[count, 6] <- res$`2.5 %`[2]
        coefs5[count, 7] <- res$`97.5 %`[2]
        coefs5[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs5[count, 9] <- res$p.value[2]
        coefs5[count, 10] <- res$estimate[3]
        coefs5[count, 11] <- res$`2.5 %`[3]
        coefs5[count, 12] <- res$`97.5 %`[3]
        coefs5[count, 13] <- paste(res$`2.5 %`[3], ",", " ", res$`97.5 %`[3], sep = "")
        coefs5[count, 14] <- res$p.value[3]
        coefs5[count, 15] <- res$estimate[4]
        coefs5[count, 16] <- res$`2.5 %`[4]
        coefs5[count, 17] <- res$`97.5 %`[4]
        coefs5[count, 18] <- paste(res$`2.5 %`[4], ",", " ", res$`97.5 %`[4], sep = "")
        coefs5[count, 19] <- res$p.value[4]
      }
    }
  } else {
    for (d in noise) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full_noise %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs5[count, 1] <- gsub(" ", "_", Sys.time())
        coefs5[count, 2] <- o
        coefs5[count, 3] <- d
        coefs5[count, 4] <- m
        coefs5[count, 5] <- res$estimate[2]
        coefs5[count, 6] <- res$`2.5 %`[2]
        coefs5[count, 7] <- res$`97.5 %`[2]
        coefs5[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs5[count, 9] <- res$p.value[2]
        coefs5[count, 10] <- res$estimate[3]
        coefs5[count, 11] <- res$`2.5 %`[3]
        coefs5[count, 12] <- res$`97.5 %`[3]
        coefs5[count, 13] <- paste(res$`2.5 %`[3], ",", " ", res$`97.5 %`[3], sep = "")
        coefs5[count, 14] <- res$p.value[3]
        coefs5[count, 15] <- res$estimate[4]
        coefs5[count, 16] <- res$`2.5 %`[4]
        coefs5[count, 17] <- res$`97.5 %`[4]
        coefs5[count, 18] <- paste(res$`2.5 %`[4], ",", " ", res$`97.5 %`[4], sep = "")
        coefs5[count, 19] <- res$p.value[4]
      }
    }
  }
}

mod_tbl5 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl5) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in noise) {
    sep_coefs <- coefs5 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, "_55-59.9", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta1[1]
    mod_tbl5[count, 4] <- sep_coefs$CI1[1]
    mod_tbl5[count, 5] <- sep_coefs$P1[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta1[2]
    mod_tbl5[count, 7] <- sep_coefs$CI1[2]
    mod_tbl5[count, 8] <- sep_coefs$P1[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta1[3]
    mod_tbl5[count, 10] <- sep_coefs$CI1[3]
    mod_tbl5[count, 11] <- sep_coefs$P1[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta1[4]
    mod_tbl5[count, 13] <- sep_coefs$CI1[4]
    mod_tbl5[count, 14] <- sep_coefs$P1[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo1[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi1[4]

    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, "_60-64.9 ", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta2[1]
    mod_tbl5[count, 4] <- sep_coefs$CI2[1]
    mod_tbl5[count, 5] <- sep_coefs$P2[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta2[2]
    mod_tbl5[count, 7] <- sep_coefs$CI2[2]
    mod_tbl5[count, 8] <- sep_coefs$P2[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta2[3]
    mod_tbl5[count, 10] <- sep_coefs$CI2[3]
    mod_tbl5[count, 11] <- sep_coefs$P2[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta2[4]
    mod_tbl5[count, 13] <- sep_coefs$CI2[4]
    mod_tbl5[count, 14] <- sep_coefs$P2[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo2[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi2[4]

    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, ">=65 ", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta3[1]
    mod_tbl5[count, 4] <- sep_coefs$CI3[1]
    mod_tbl5[count, 5] <- sep_coefs$P3[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta3[2]
    mod_tbl5[count, 7] <- sep_coefs$CI3[2]
    mod_tbl5[count, 8] <- sep_coefs$P3[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta3[3]
    mod_tbl5[count, 10] <- sep_coefs$CI3[3]
    mod_tbl5[count, 11] <- sep_coefs$P3[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta3[4]
    mod_tbl5[count, 13] <- sep_coefs$CI3[4]
    mod_tbl5[count, 14] <- sep_coefs$P3[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo3[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi3[4]
  }
}

mod_tbl5 <- mod_tbl5 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio_a1", "AL_2_metabolic_a1", "AL_2_immune_a1", "AL_2_neuro_a1") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio_a1", "AL_2_metabolic_a1", "AL_2_immune_a1", "AL_2_neuro_a1") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio_a1", "AL_2_metabolic_a1", "AL_2_immune_a1", "AL_2_neuro_a1") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl5, file = paste("/Users/ymou/helix_project/results/sensitivity_analysis/cortisol_highestquartile_ALS/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "noise_outcomepsystem_zscore"

imp_full_noise <- complete(Suppl_impset, "long", include = T) %>%
  filter(cohort != "EDEN") %>%
  as.mids()

coefs5 <- as.data.frame(matrix(NA, nrow = 1, ncol = 19))
colnames(coefs5) <- c(
  "DateTime", "Outcome", "Predictor", "Model", "Beta1", "cilo1", "cihi1", "CI1", "P1",
  "Beta2", "cilo2", "cihi2", "CI2", "P2", "Beta3", "cilo3", "cihi3", "CI3", "P3"
)

count <- 0
for (o in out_ps_z) {
  for (d in noise) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <- imp_full_noise %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)

      # Save results
      coefs5[count, 1] <- gsub(" ", "_", Sys.time())
      coefs5[count, 2] <- o
      coefs5[count, 3] <- d
      coefs5[count, 4] <- m
      coefs5[count, 5] <- res$estimate[2]
      coefs5[count, 6] <- res$`2.5 %`[2]
      coefs5[count, 7] <- res$`97.5 %`[2]
      coefs5[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs5[count, 9] <- res$p.value[2]
      coefs5[count, 10] <- res$estimate[3]
      coefs5[count, 11] <- res$`2.5 %`[3]
      coefs5[count, 12] <- res$`97.5 %`[3]
      coefs5[count, 13] <- paste(res$`2.5 %`[3], ",", " ", res$`97.5 %`[3], sep = "")
      coefs5[count, 14] <- res$p.value[3]
      coefs5[count, 15] <- res$estimate[4]
      coefs5[count, 16] <- res$`2.5 %`[4]
      coefs5[count, 17] <- res$`97.5 %`[4]
      coefs5[count, 18] <- paste(res$`2.5 %`[4], ",", " ", res$`97.5 %`[4], sep = "")
      coefs5[count, 19] <- res$p.value[4]
    }
  }
}

mod_tbl5 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl5) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in noise) {
    sep_coefs <- coefs5 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, "_55-59.9", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta1[1]
    mod_tbl5[count, 4] <- sep_coefs$CI1[1]
    mod_tbl5[count, 5] <- sep_coefs$P1[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta1[2]
    mod_tbl5[count, 7] <- sep_coefs$CI1[2]
    mod_tbl5[count, 8] <- sep_coefs$P1[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta1[3]
    mod_tbl5[count, 10] <- sep_coefs$CI1[3]
    mod_tbl5[count, 11] <- sep_coefs$P1[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta1[4]
    mod_tbl5[count, 13] <- sep_coefs$CI1[4]
    mod_tbl5[count, 14] <- sep_coefs$P1[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo1[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi1[4]

    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, "_60-64.9 ", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta2[1]
    mod_tbl5[count, 4] <- sep_coefs$CI2[1]
    mod_tbl5[count, 5] <- sep_coefs$P2[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta2[2]
    mod_tbl5[count, 7] <- sep_coefs$CI2[2]
    mod_tbl5[count, 8] <- sep_coefs$P2[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta2[3]
    mod_tbl5[count, 10] <- sep_coefs$CI2[3]
    mod_tbl5[count, 11] <- sep_coefs$P2[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta2[4]
    mod_tbl5[count, 13] <- sep_coefs$CI2[4]
    mod_tbl5[count, 14] <- sep_coefs$P2[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo2[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi2[4]


    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, ">=65 ", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta3[1]
    mod_tbl5[count, 4] <- sep_coefs$CI3[1]
    mod_tbl5[count, 5] <- sep_coefs$P3[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta3[2]
    mod_tbl5[count, 7] <- sep_coefs$CI3[2]
    mod_tbl5[count, 8] <- sep_coefs$P3[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta3[3]
    mod_tbl5[count, 10] <- sep_coefs$CI3[3]
    mod_tbl5[count, 11] <- sep_coefs$P3[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta3[4]
    mod_tbl5[count, 13] <- sep_coefs$CI3[4]
    mod_tbl5[count, 14] <- sep_coefs$P3[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo3[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi3[4]
  }
}


write.xlsx(mod_tbl5, file = paste("/Users/ymou/helix_project/results/sensitivity_analysis/cortisol_highestquartile_ALS/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```


# ANALYSIS: no EDEN
```{r}
# imputed dataset excluding participants from cohort EDEN 
imp_noeden <- dat_afimp %>% filter(cohort != "EDEN") %>% filter(incl_var_out == 1)
imp_noeden <- as.mids(imp_noeden)
```

## Air pollution total and main outcomes
```{r}
analysis <- "airpollution_total_mainoutcome_exclEDEN"

coefs <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out) {
  if (o %in% c("AL_2_tot")) {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noeden %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs[count, 1] <- gsub(" ", "_", Sys.time())
        coefs[count, 2] <- o
        coefs[count, 3] <- d
        coefs[count, 4] <- m
        coefs[count, 5] <- res$estimate[2]
        coefs[count, 6] <- res$`2.5 %`[2]
        coefs[count, 7] <- res$`97.5 %`[2]
        coefs[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noeden %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs[count, 1] <- gsub(" ", "_", Sys.time())
        coefs[count, 2] <- o
        coefs[count, 3] <- d
        coefs[count, 4] <- m
        coefs[count, 5] <- res$estimate[2]
        coefs[count, 6] <- res$`2.5 %`[2]
        coefs[count, 7] <- res$`97.5 %`[2]
        coefs[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs[count, 9] <- res$p.value[2]
      }
    }
  }
}


mod_tbl <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in ap) {
    sep_coefs <- coefs %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl[count, 1] <- o
    mod_tbl[count, 2] <- d
    mod_tbl[count, 3] <- sep_coefs$Beta[1]
    mod_tbl[count, 4] <- sep_coefs$CI[1]
    mod_tbl[count, 5] <- sep_coefs$P[1]
    mod_tbl[count, 6] <- sep_coefs$Beta[2]
    mod_tbl[count, 7] <- sep_coefs$CI[2]
    mod_tbl[count, 8] <- sep_coefs$P[2]
    mod_tbl[count, 9] <- sep_coefs$Beta[3]
    mod_tbl[count, 10] <- sep_coefs$CI[3]
    mod_tbl[count, 11] <- sep_coefs$P[3]
    mod_tbl[count, 12] <- sep_coefs$Beta[4]
    mod_tbl[count, 13] <- sep_coefs$CI[4]
    mod_tbl[count, 14] <- sep_coefs$P[4]
    mod_tbl[count, 15] <- sep_coefs$cilo[4]
    mod_tbl[count, 16] <- sep_coefs$cihi[4]
  }
}

mod_tbl <- mod_tbl %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_tot"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

## Air pollution total and outcomes per physiological systems
```{r}
analysis <- "airpollution_total_outcomepsystem_exclEDEN"

coefs1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs1) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro")) {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noeden %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs1[count, 1] <- gsub(" ", "_", Sys.time())
        coefs1[count, 2] <- o
        coefs1[count, 3] <- d
        coefs1[count, 4] <- m
        coefs1[count, 5] <- res$estimate[2]
        coefs1[count, 6] <- res$`2.5 %`[2]
        coefs1[count, 7] <- res$`97.5 %`[2]
        coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs1[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noeden %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs1[count, 1] <- gsub(" ", "_", Sys.time())
        coefs1[count, 2] <- o
        coefs1[count, 3] <- d
        coefs1[count, 4] <- m
        coefs1[count, 5] <- res$estimate[2]
        coefs1[count, 6] <- res$`2.5 %`[2]
        coefs1[count, 7] <- res$`97.5 %`[2]
        coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs1[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl1) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in ap) {
    sep_coefs1 <- coefs1 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl1[count, 1] <- o
    mod_tbl1[count, 2] <- d
    mod_tbl1[count, 3] <- sep_coefs1$Beta[1]
    mod_tbl1[count, 4] <- sep_coefs1$CI[1]
    mod_tbl1[count, 5] <- sep_coefs1$P[1]
    mod_tbl1[count, 6] <- sep_coefs1$Beta[2]
    mod_tbl1[count, 7] <- sep_coefs1$CI[2]
    mod_tbl1[count, 8] <- sep_coefs1$P[2]
    mod_tbl1[count, 9] <- sep_coefs1$Beta[3]
    mod_tbl1[count, 10] <- sep_coefs1$CI[3]
    mod_tbl1[count, 11] <- sep_coefs1$P[3]
    mod_tbl1[count, 12] <- sep_coefs1$Beta[4]
    mod_tbl1[count, 13] <- sep_coefs1$CI[4]
    mod_tbl1[count, 14] <- sep_coefs1$P[4]
    mod_tbl1[count, 15] <- sep_coefs1$cilo[4]
    mod_tbl1[count, 16] <- sep_coefs1$cihi[4]
  }
}

mod_tbl1 <- mod_tbl1 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl1, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "airpollution_total_outcomepsystem_zscore_exclEDEN"

coefs1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs1) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps_z) {
  for (d in ap) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <-  imp_noeden %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)

      # Save results
      coefs1[count, 1] <- gsub(" ", "_", Sys.time())
      coefs1[count, 2] <- o
      coefs1[count, 3] <- d
      coefs1[count, 4] <- m
      coefs1[count, 5] <- res$estimate[2]
      coefs1[count, 6] <- res$`2.5 %`[2]
      coefs1[count, 7] <- res$`97.5 %`[2]
      coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs1[count, 9] <- res$p.value[2]
    }
  }
}

mod_tbl1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl1) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in ap) {
    sep_coefs1 <- coefs1 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl1[count, 1] <- o
    mod_tbl1[count, 2] <- d
    mod_tbl1[count, 3] <- sep_coefs1$Beta[1]
    mod_tbl1[count, 4] <- sep_coefs1$CI[1]
    mod_tbl1[count, 5] <- sep_coefs1$P[1]
    mod_tbl1[count, 6] <- sep_coefs1$Beta[2]
    mod_tbl1[count, 7] <- sep_coefs1$CI[2]
    mod_tbl1[count, 8] <- sep_coefs1$P[2]
    mod_tbl1[count, 9] <- sep_coefs1$Beta[3]
    mod_tbl1[count, 10] <- sep_coefs1$CI[3]
    mod_tbl1[count, 11] <- sep_coefs1$P[3]
    mod_tbl1[count, 12] <- sep_coefs1$Beta[4]
    mod_tbl1[count, 13] <- sep_coefs1$CI[4]
    mod_tbl1[count, 14] <- sep_coefs1$P[4]
    mod_tbl1[count, 15] <- sep_coefs1$cilo[4]
    mod_tbl1[count, 16] <- sep_coefs1$cihi[4]
  }
}


write.xlsx(mod_tbl1, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```


## Air pollution home, school, commuting and other places with main outcomes
```{r}
analysis <- "airpollution_hsrp_mainoutcome_exclEDEN"

coefs2 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs2) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out) {
  if (o %in% c("AL_2_tot")) {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noeden %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs2[count, 1] <- gsub(" ", "_", Sys.time())
        coefs2[count, 2] <- o
        coefs2[count, 3] <- d
        coefs2[count, 4] <- m
        coefs2[count, 5] <- res$estimate[2]
        coefs2[count, 6] <- res$`2.5 %`[2]
        coefs2[count, 7] <- res$`97.5 %`[2]
        coefs2[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs2[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noeden %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs2[count, 1] <- gsub(" ", "_", Sys.time())
        coefs2[count, 2] <- o
        coefs2[count, 3] <- d
        coefs2[count, 4] <- m
        coefs2[count, 5] <- res$estimate[2]
        coefs2[count, 6] <- res$`2.5 %`[2]
        coefs2[count, 7] <- res$`97.5 %`[2]
        coefs2[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs2[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl2 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl2) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in ap_supl) {
    sep_coefs2 <- coefs2 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl2[count, 1] <- o
    mod_tbl2[count, 2] <- d
    mod_tbl2[count, 3] <- sep_coefs2$Beta[1]
    mod_tbl2[count, 4] <- sep_coefs2$CI[1]
    mod_tbl2[count, 5] <- sep_coefs2$P[1]
    mod_tbl2[count, 6] <- sep_coefs2$Beta[2]
    mod_tbl2[count, 7] <- sep_coefs2$CI[2]
    mod_tbl2[count, 8] <- sep_coefs2$P[2]
    mod_tbl2[count, 9] <- sep_coefs2$Beta[3]
    mod_tbl2[count, 10] <- sep_coefs2$CI[3]
    mod_tbl2[count, 11] <- sep_coefs2$P[3]
    mod_tbl2[count, 12] <- sep_coefs2$Beta[4]
    mod_tbl2[count, 13] <- sep_coefs2$CI[4]
    mod_tbl2[count, 14] <- sep_coefs2$P[4]
    mod_tbl2[count, 15] <- sep_coefs2$cilo[4]
    mod_tbl2[count, 16] <- sep_coefs2$cihi[4]
  }
}

mod_tbl2 <- mod_tbl2 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_tot"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl2, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```


## Air pollution home, school, commuting and other places with outcomes per physiological systems
```{r}
analysis <- "airpollution_hsrp_outcomepsystem_exclEDEN"

coefs3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs3) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro")) {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noeden %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs3[count, 1] <- gsub(" ", "_", Sys.time())
        coefs3[count, 2] <- o
        coefs3[count, 3] <- d
        coefs3[count, 4] <- m
        coefs3[count, 5] <- res$estimate[2]
        coefs3[count, 6] <- res$`2.5 %`[2]
        coefs3[count, 7] <- res$`97.5 %`[2]
        coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs3[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noeden %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs3[count, 1] <- gsub(" ", "_", Sys.time())
        coefs3[count, 2] <- o
        coefs3[count, 3] <- d
        coefs3[count, 4] <- m
        coefs3[count, 5] <- res$estimate[2]
        coefs3[count, 6] <- res$`2.5 %`[2]
        coefs3[count, 7] <- res$`97.5 %`[2]
        coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs3[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl3) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in ap_supl) {
    sep_coefs3 <- coefs3 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl3[count, 1] <- o
    mod_tbl3[count, 2] <- d
    mod_tbl3[count, 3] <- sep_coefs3$Beta[1]
    mod_tbl3[count, 4] <- sep_coefs3$CI[1]
    mod_tbl3[count, 5] <- sep_coefs3$P[1]
    mod_tbl3[count, 6] <- sep_coefs3$Beta[2]
    mod_tbl3[count, 7] <- sep_coefs3$CI[2]
    mod_tbl3[count, 8] <- sep_coefs3$P[2]
    mod_tbl3[count, 9] <- sep_coefs3$Beta[3]
    mod_tbl3[count, 10] <- sep_coefs3$CI[3]
    mod_tbl3[count, 11] <- sep_coefs3$P[3]
    mod_tbl3[count, 12] <- sep_coefs3$Beta[4]
    mod_tbl3[count, 13] <- sep_coefs3$CI[4]
    mod_tbl3[count, 14] <- sep_coefs3$P[4]
    mod_tbl3[count, 15] <- sep_coefs3$cilo[4]
    mod_tbl3[count, 16] <- sep_coefs3$cihi[4]
  }
}

mod_tbl3 <- mod_tbl3 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl3, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "airpollution_hsrp_outcomepsystem_zscore_exclEDEN"

coefs3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs3) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps_z) {
  for (d in ap_supl) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <-  imp_noeden %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)

      # Save results
      coefs3[count, 1] <- gsub(" ", "_", Sys.time())
      coefs3[count, 2] <- o
      coefs3[count, 3] <- d
      coefs3[count, 4] <- m
      coefs3[count, 5] <- res$estimate[2]
      coefs3[count, 6] <- res$`2.5 %`[2]
      coefs3[count, 7] <- res$`97.5 %`[2]
      coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs3[count, 9] <- res$p.value[2]
    }
  }
}

mod_tbl3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl3) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in ap_supl) {
    sep_coefs3 <- coefs3 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl3[count, 1] <- o
    mod_tbl3[count, 2] <- d
    mod_tbl3[count, 3] <- sep_coefs3$Beta[1]
    mod_tbl3[count, 4] <- sep_coefs3$CI[1]
    mod_tbl3[count, 5] <- sep_coefs3$P[1]
    mod_tbl3[count, 6] <- sep_coefs3$Beta[2]
    mod_tbl3[count, 7] <- sep_coefs3$CI[2]
    mod_tbl3[count, 8] <- sep_coefs3$P[2]
    mod_tbl3[count, 9] <- sep_coefs3$Beta[3]
    mod_tbl3[count, 10] <- sep_coefs3$CI[3]
    mod_tbl3[count, 11] <- sep_coefs3$P[3]
    mod_tbl3[count, 12] <- sep_coefs3$Beta[4]
    mod_tbl3[count, 13] <- sep_coefs3$CI[4]
    mod_tbl3[count, 14] <- sep_coefs3$P[4]
    mod_tbl3[count, 15] <- sep_coefs3$cilo[4]
    mod_tbl3[count, 16] <- sep_coefs3$cihi[4]
  }
}

write.xlsx(mod_tbl3, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```


```{r import_results}
# Air pollutants
# Count-based AL, Continuous AL and their weighted average
ap_tot_out <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_mainoutcome_exclEDEN2024-05-21.xlsx")
# Count-based AL and weighted average score per system
ap_tot_outps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_exclEDEN2024-05-21.xlsx")
# Continuous AL and weighted average score per system
ap_tot_outzps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_zscore_exclEDEN2024-05-21.xlsx")

tot_res <- bind_rows(ap_tot_out, ap_tot_outps, ap_tot_outzps)
```

# Table S4 Relative risk of count-based allostatic load score associated with outdoor air pollutants (without EDEN)
```{r tblS4}
tot_res %>%
  select(Outcome, Predictor, exp_beta_mod4, exp_ci_mod4) %>%
  filter(Outcome == "AL_2_tot") %>% 
  gt() %>% 
  tab_header(
    title = "Table S4 Relative risk of count-based allostatic load score associated with outdoor air pollutants (without EDEN)"
  ) %>% 
  fmt_number(decimals = 2, drop_trailing_zeros = F) %>% 
  gt::gtsave(., "/Users/ymou/helix_project/results/Table/TableS4-noeden.docx")
```

# Table S5 Effect estimates of continuous allostatic load score associated with outdoor air pollutants (without EDEN)
```{r tblS5}
tot_res %>%
  select(Outcome, Predictor, beta_mod4, `95ci_mod4`) %>%
  filter(Outcome == "AL_z2_tot") %>% 
  gt() %>% 
  tab_header(
    title = "Table S5 Effect estimates of continuous allostatic load score associated with outdoor air pollutants (without EDEN)"
  ) %>% 
  fmt_number(decimals = 2, drop_trailing_zeros = F) %>% 
  gt::gtsave(., "/Users/ymou/helix_project/results/Table/TableS5-noeden.docx")
```

# Results plot
```{r load packages3, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages_3 <- c("tidyverse", "labelled", "openxlsx", "meta", "readxl", "RColorBrewer", "ggsci", "patchwork")
sapply(packages_3, library, character.only = T)
```

```{r}
# Air pollutants
# Count-based AL, Continuous AL and their weighted average
ap_tot_out <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_mainoutcome_exclEDEN2024-05-21.xlsx")
# Count-based AL and weighted average score per system
ap_tot_outps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_exclEDEN2024-05-21.xlsx")
# Continuous AL and weighted average score per system
ap_tot_outzps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_zscore_exclEDEN2024-05-21.xlsx")

# Count-based AL, Continuous AL and their weighted average: Home, school, commuting
ap_hsr_out <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_hsrp_mainoutcome_exclEDEN2024-05-21.xlsx") %>% filter(!str_detect(Predictor, "_p$")) # other places not incl
# Count-based AL and weighted average score per system: Home, school, commuting
ap_hsr_outps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_hsrp_outcomepsystem_exclEDEN2024-05-21.xlsx") %>% filter(!str_detect(Predictor, "_p$")) # other places not incl
# Continuous AL and weighted average score per system: Home, school, commuting
ap_hsr_outzps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_hsrp_outcomepsystem_zscore_exclEDEN2024-05-21.xlsx") %>% filter(!str_detect(Predictor, "_p$")) # other places not incl

```

```{r merge data}
ap_tot_res <- bind_rows(ap_tot_out, ap_tot_outps, ap_tot_outzps)
ap_tot_res <- ap_tot_res %>%
  mutate(al_type = if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == F, "AL_2",
    if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == T, "AL_2_wavg",
      if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == F, "AL_z2",
        if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == T, "AL_z2_wavg", NA)
      )
    )
  )) %>%
  dplyr::rename(
    "beta" = "beta_mod4",
    "low" = "cilo_mod4",
    "hi" = "cihi_mod4"
  ) %>%
  mutate_at(c("Predictor", "Outcome"), as.factor) %>% 
  mutate(Predictor = fct_relevel(Predictor,c("hs_no2_yr_hs_t","hs_pm25_yr_hs_t","hs_pm25abs_yr_hs_t", "hs_pm10_yr_hs_t")),
         Outcome = fct_relevel(Outcome, c("AL_2_tot", "AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro",
                                          "AL_z2_tot", "AL_z2_cardio", "AL_z2_metab", "AL_z2_immune", "AL_z2_neuro",
                                          "AL_2_tot_wavg", "AL_2_cardio_wavg", "AL_2_metab_wavg", "AL_2_immune_wavg", "AL_2_neuro_wavg",
                                          "AL_z2_tot_wavg", "AL_z2_cardio_wavg", "AL_z2_metab_wavg", "AL_z2_immune_wavg", "AL_z2_neuro_wavg"))) %>% 
  mutate(
    Predictor = recode(Predictor,
      "hs_no2_yr_hs_t" = "NO[2]",
      "hs_pm10_yr_hs_t" = "PM[10]",
      "hs_pm25_yr_hs_t" = "PM[2.5]",
      "hs_pm25abs_yr_hs_t" = "PM[2.5][abs]"
    ),
    Outcome = recode(Outcome,
      "AL_2_tot" = "Count-based ALS",
      "AL_2_tot_wavg" = "Count-based weighted average ALS",
      "AL_z2_tot" = "Continuous ALS",
      "AL_z2_tot_wavg" = "Continuous weighted average ALS",
      "AL_2_cardio" = "Count-based cardiovascular ALS",
      "AL_2_metab" = "Count-based metabolic ALS",
      "AL_2_immune" = "Count-based immune/inflammatory ALS",
      "AL_2_neuro" = "Count-based neuroendorine ALS",
      "AL_2_cardio_wavg" = "Count-based cardiovascular weighted average ALS",
      "AL_2_metab_wavg" = "Count-based metabolic weighted average ALS",
      "AL_2_immune_wavg" = "Count-based immune/inflammatory weighted average ALS",
      "AL_2_neuro_wavg" = "Count-based neuroendorine weighted average ALS",
      "AL_z2_cardio" = "Continuous cardiovascular ALS",
      "AL_z2_metab" = "Continuous metabolic ALS",
      "AL_z2_immune" = "Continuous immune/inflammatory ALS",
      "AL_z2_neuro" = "Continuous neuroendorine ALS",
      "AL_z2_cardio_wavg" = "Continuous cardiovascular weighted average ALS",
      "AL_z2_metab_wavg" = "Continuous metabolic weighted average ALS",
      "AL_z2_immune_wavg" = "Continuous immune/inflammatory weighted average ALS",
      "AL_z2_neuro_wavg" = "Continuous neuroendorine weighted average ALS"
    )
  )  %>% 
  rename(Outcomes = Outcome)



ap_hsr_res <- bind_rows(ap_hsr_out, ap_hsr_outps, ap_hsr_outzps)
ap_hsr_res <- ap_hsr_res %>%
  mutate(al_type = if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == F, "AL_2",
    if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == T, "AL_2_wavg",
      if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == F, "AL_z2",
        if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == T, "AL_z2_wavg", NA)
      )
    )
  )) %>%
  dplyr::rename(
    "beta" = "beta_mod4",
    "low" = "cilo_mod4",
    "hi" = "cihi_mod4"
  ) %>%
  mutate(type = if_else(str_detect(Predictor, "_h$"), "Home",
    if_else(str_detect(Predictor, "_s$"), "School", "Commuting")
  )) %>%
  mutate_at(c("Predictor", "Outcome"), as.factor) %>% 
  mutate(Predictor = fct_relevel(Predictor,c("hs_no2_yr_hs_h","hs_no2_yr_hs_s","hs_no2_yr_hs_r",
                                             "hs_pm25_yr_hs_h", "hs_pm25_yr_hs_s", "hs_pm25_yr_hs_r",
                                             "hs_pm25abs_yr_hs_h", "hs_pm25abs_yr_hs_s", "hs_pm25abs_yr_hs_r",
                                             "hs_pm10_yr_hs_h", "hs_pm10_yr_hs_s", "hs_pm10_yr_hs_r")),
         Outcome = fct_relevel(Outcome, c("AL_2_tot", "AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro",
                                          "AL_z2_tot", "AL_z2_cardio", "AL_z2_metab", "AL_z2_immune", "AL_z2_neuro",
                                          "AL_2_tot_wavg", "AL_2_cardio_wavg", "AL_2_metab_wavg", "AL_2_immune_wavg", "AL_2_neuro_wavg",
                                          "AL_z2_tot_wavg", "AL_z2_cardio_wavg", "AL_z2_metab_wavg", "AL_z2_immune_wavg", "AL_z2_neuro_wavg"))) %>% 
  mutate(Predictor = recode(Predictor,
    "hs_no2_yr_hs_h" = "NO[2]",
    "hs_no2_yr_hs_s" = "NO[2]",
    "hs_no2_yr_hs_r" = "NO[2]",
    "hs_pm25_yr_hs_h" = "PM[2.5]",
    "hs_pm25_yr_hs_s" = "PM[2.5]",
    "hs_pm25_yr_hs_r" = "PM[2.5]",
    "hs_pm25abs_yr_hs_h" = "PM[2.5][abs]",
    "hs_pm25abs_yr_hs_s" = "PM[2.5][abs]",
    "hs_pm25abs_yr_hs_r" = "PM[2.5][abs]",
    "hs_pm10_yr_hs_h" = "PM[10]",
    "hs_pm10_yr_hs_s" = "PM[10]",
    "hs_pm10_yr_hs_r" = "PM[10]",
  ),
    Outcome = recode(Outcome,
      "AL_2_tot" = "Count-based ALS",
      "AL_2_tot_wavg" = "Count-based weighted average ALS",
      "AL_z2_tot" = "Continuous ALS",
      "AL_z2_tot_wavg" = "Continuous weighted average ALS",
      "AL_2_cardio" = "Count-based cardiovascular ALS",
      "AL_2_metab" = "Count-based metabolic ALS",
      "AL_2_immune" = "Count-based immune/inflammatory ALS",
      "AL_2_neuro" = "Count-based neuroendorine ALS",
      "AL_2_cardio_wavg" = "Count-based cardiovascular weighted average ALS",
      "AL_2_metab_wavg" = "Count-based metabolic weighted average ALS",
      "AL_2_immune_wavg" = "Count-based immune/inflammatory weighted average ALS",
      "AL_2_neuro_wavg" = "Count-based neuroendorine weighted average ALS",
      "AL_z2_cardio" = "Continuous cardiovascular ALS",
      "AL_z2_metab" = "Continuous metabolic ALS",
      "AL_z2_immune" = "Continuous immune/inflammatory ALS",
      "AL_z2_neuro" = "Continuous neuroendorine ALS",
      "AL_z2_cardio_wavg" = "Continuous cardiovascular weighted average ALS",
      "AL_z2_metab_wavg" = "Continuous metabolic weighted average ALS",
      "AL_z2_immune_wavg" = "Continuous immune/inflammatory weighted average ALS",
      "AL_z2_neuro_wavg" = "Continuous neuroendorine weighted average ALS"
    )) %>% 
  rename(Outcomes = Outcome)
```

# Plots

## Air pollutants

### Count-based ALS
```{r}
dt_p1 <- ap_tot_res %>% filter(al_type == "AL_2")

dt_p1$es <- paste0(
  sprintf("%.2f", dt_p1$exp_beta_mod4), " (",
  sprintf("%.2f", dt_p1$exp_cilo_mod4), "-",
  sprintf("%.2f", dt_p1$exp_cihi_mod4), ")"
)
```

```{r fig.asp = 0.8, fig.width=10}
p1 <- ggplot(
  data = dt_p1,
  aes(x = Outcomes, y = exp_beta_mod4, ymin = exp_cilo_mod4, ymax = exp_cihi_mod4)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 1, linetype = 3) +
  xlab("") +
  ylab("Relative risk (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = exp_cilo_mod4, ymax = exp_cihi_mod4, col = Outcomes), width = 0.5, cex = 1) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, scales = "free_y", labeller = labeller(Predictor = label_parsed)) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  guides(col = guide_legend(nrow = 2, reverse = T, title = "Count-based ALS",
                            title.position = "top")) +
  
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.y.left = element_text(size = 14, angle = 0, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
     labels = c("Count-based neuroendorine ALS" = "Neuroendocrine ALS",
               "Count-based immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Count-based metabolic ALS" = "Metabolic ALS",
               "Count-based cardiovascular ALS" = "Cardiovascular ALS",
               "Count-based ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p1

table_es <- ggplot(dt_p1, aes(x = 0, y = Outcomes, label = es)) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, labeller = labeller(Predictor = label_parsed)) +
  geom_text(hjust = 0, size = 5) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = margin(0, 1, 0, 0),
    strip.text.y = element_blank(),
    panel.background = element_rect(fill = 'white', colour = 'white'),
    strip.background=element_rect(fill="white", colour = 'white')
  )
table_es

# Combine plots using patchwork
combined_plot <- p1 + table_es + plot_layout(ncol = 2, widths = c(0.5, 0.5))

# Display the combined plot
print(combined_plot)
```

```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_eden/fig-countAL.png", width = 15, height = 10, units = "in", dpi = 300)
```

### Continuous ALS
```{r}
dt_p3 <- ap_tot_res %>% filter(al_type == "AL_z2")

dt_p3$es <- paste0(
  sprintf("%.2f", dt_p3$beta), " (",
  sprintf("%.2f", dt_p3$low), "-",
  sprintf("%.2f", dt_p3$hi), ")"
)
```

```{r fig.asp = 0.8, fig.width=10}
p3 <- ggplot(
  data = dt_p3,
  aes(x = Outcomes, y = beta, ymin = low, ymax = hi)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 0, linetype = 3) +
  xlab("") +
  ylab("Effect sizes (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = low, ymax = hi, col = Outcomes), width = 0.5, cex = 1) +
  guides(color = guide_legend(nrow = 2, reverse = T, title = "Continuous ALS",
                              title.position = "top")) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, scales = "free_y", labeller = labeller(Predictor = label_parsed)) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.y.left = element_text(size = 14, angle = 0, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
    labels = c("Continuous neuroendorine ALS" = "Neuroendocrine ALS",
               "Continuous immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Continuous metabolic ALS" = "Metabolic ALS",
               "Continuous cardiovascular ALS" = "Cardiovascular ALS",
               "Continuous ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p3

table_es <- ggplot(dt_p3, aes(x = 0, y = Outcomes, label = es)) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, labeller = labeller(Predictor = label_parsed)) +
  geom_text(hjust = 0, size = 5) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = margin(0, 1, 0, 0),
    strip.text.y = element_blank(),
    panel.background = element_rect(fill = 'white', colour = 'white'),
    strip.background=element_rect(fill="white", colour = 'white')
  )
table_es

# Combine plots using patchwork
combined_plot <- p3 + table_es + plot_layout(ncol = 2, widths = c(0.5, 0.5))

# Display the combined plot
print(combined_plot)
```

```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_eden/fig-continuousAL.png", width = 15, height = 10, units = "in", dpi = 300)
```

## Air pollutants(home, school, commuting) 

### Count-based ALS
```{r}
dt_p5 <- ap_hsr_res %>% filter(al_type == "AL_2")
```

```{r fig.asp = 0.8, fig.width=10}
p5 <- ggplot(
  data = dt_p5,
  aes(x = Outcomes, y = exp_beta_mod4, ymin = exp_cilo_mod4, ymax = exp_cihi_mod4)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 1, linetype = 3) +
  xlab("") +
  ylab("Relative risk (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = exp_cilo_mod4, ymax = exp_cihi_mod4, col = Outcomes), width = 0.5, cex = 1) +
  facet_grid(rows = vars(Predictor), cols = vars(type), switch = "y", labeller = labeller(Predictor = label_parsed)) +
  guides(col = guide_legend(nrow = 2, reverse = T, title = "Count-based ALS",
                            title.position = "top")) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.x = element_text(size = 14, angle = 0),
    strip.text.y.left = element_text(size = 14, angle = 0),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
    labels = c("Count-based neuroendorine ALS" = "Neuroendocrine ALS",
               "Count-based immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Count-based metabolic ALS" = "Metabolic ALS",
               "Count-based cardiovascular ALS" = "Cardiovascular ALS",
               "Count-based ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p5
```

```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_eden/fig-countAL-hsr.png", width = 13, height = 13, units = "in", dpi = 300)
```

### Continuous ALS
```{r}
dt_p7 <- ap_hsr_res %>% filter(al_type == "AL_z2")
```

```{r fig.asp = 0.8, fig.width=10}
p7 <- ggplot(
  data = dt_p7,
  aes(x = Outcomes, y = beta, ymin = low, ymax = hi)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 0, linetype = 3) +
  xlab("") +
  ylab("Relative risk (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = low, ymax = hi, col = Outcomes), width = 0.5, cex = 1) +
  facet_grid(rows = vars(Predictor), cols = vars(type), switch = "y", labeller = labeller(Predictor = label_parsed)) +
  guides(col = guide_legend(nrow = 2, reverse = T, title = "Count-based ALS",
                            title.position = "top")) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.x = element_text(size = 14, angle = 0),
    strip.text.y.left = element_text(size = 14, angle = 0),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
    labels = c("Continuous neuroendorine ALS" = "Neuroendocrine ALS",
               "Continuous immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Continuous metabolic ALS" = "Metabolic ALS",
               "Continuous cardiovascular ALS" = "Cardiovascular ALS",
               "Continuous ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p7
```

```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_eden/fig-continousAL-hsr.png", width = 13, height = 13, units = "in", dpi = 300)
```


# ANALYSIS: no RHEA
```{r}
# imputed dataset excluding participants from cohort RHEA 
imp_norhea <- dat_afimp %>% filter(cohort != "RHEA") %>% filter(incl_var_out == 1)
imp_norhea <- as.mids(imp_norhea)
```

## Air pollution total and main outcomes
```{r}
analysis <- "airpollution_total_mainoutcome_exclRHEA"

coefs <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out) {
  if (o %in% c("AL_2_tot")) {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_norhea %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs[count, 1] <- gsub(" ", "_", Sys.time())
        coefs[count, 2] <- o
        coefs[count, 3] <- d
        coefs[count, 4] <- m
        coefs[count, 5] <- res$estimate[2]
        coefs[count, 6] <- res$`2.5 %`[2]
        coefs[count, 7] <- res$`97.5 %`[2]
        coefs[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_norhea %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs[count, 1] <- gsub(" ", "_", Sys.time())
        coefs[count, 2] <- o
        coefs[count, 3] <- d
        coefs[count, 4] <- m
        coefs[count, 5] <- res$estimate[2]
        coefs[count, 6] <- res$`2.5 %`[2]
        coefs[count, 7] <- res$`97.5 %`[2]
        coefs[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs[count, 9] <- res$p.value[2]
      }
    }
  }
}


mod_tbl <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in ap) {
    sep_coefs <- coefs %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl[count, 1] <- o
    mod_tbl[count, 2] <- d
    mod_tbl[count, 3] <- sep_coefs$Beta[1]
    mod_tbl[count, 4] <- sep_coefs$CI[1]
    mod_tbl[count, 5] <- sep_coefs$P[1]
    mod_tbl[count, 6] <- sep_coefs$Beta[2]
    mod_tbl[count, 7] <- sep_coefs$CI[2]
    mod_tbl[count, 8] <- sep_coefs$P[2]
    mod_tbl[count, 9] <- sep_coefs$Beta[3]
    mod_tbl[count, 10] <- sep_coefs$CI[3]
    mod_tbl[count, 11] <- sep_coefs$P[3]
    mod_tbl[count, 12] <- sep_coefs$Beta[4]
    mod_tbl[count, 13] <- sep_coefs$CI[4]
    mod_tbl[count, 14] <- sep_coefs$P[4]
    mod_tbl[count, 15] <- sep_coefs$cilo[4]
    mod_tbl[count, 16] <- sep_coefs$cihi[4]
  }
}

mod_tbl <- mod_tbl %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_tot"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

## Air pollution total and outcomes per physiological systems
```{r}
analysis <- "airpollution_total_outcomepsystem_exclRHEA"

coefs1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs1) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro")) {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_norhea %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs1[count, 1] <- gsub(" ", "_", Sys.time())
        coefs1[count, 2] <- o
        coefs1[count, 3] <- d
        coefs1[count, 4] <- m
        coefs1[count, 5] <- res$estimate[2]
        coefs1[count, 6] <- res$`2.5 %`[2]
        coefs1[count, 7] <- res$`97.5 %`[2]
        coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs1[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_norhea %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs1[count, 1] <- gsub(" ", "_", Sys.time())
        coefs1[count, 2] <- o
        coefs1[count, 3] <- d
        coefs1[count, 4] <- m
        coefs1[count, 5] <- res$estimate[2]
        coefs1[count, 6] <- res$`2.5 %`[2]
        coefs1[count, 7] <- res$`97.5 %`[2]
        coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs1[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl1) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in ap) {
    sep_coefs1 <- coefs1 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl1[count, 1] <- o
    mod_tbl1[count, 2] <- d
    mod_tbl1[count, 3] <- sep_coefs1$Beta[1]
    mod_tbl1[count, 4] <- sep_coefs1$CI[1]
    mod_tbl1[count, 5] <- sep_coefs1$P[1]
    mod_tbl1[count, 6] <- sep_coefs1$Beta[2]
    mod_tbl1[count, 7] <- sep_coefs1$CI[2]
    mod_tbl1[count, 8] <- sep_coefs1$P[2]
    mod_tbl1[count, 9] <- sep_coefs1$Beta[3]
    mod_tbl1[count, 10] <- sep_coefs1$CI[3]
    mod_tbl1[count, 11] <- sep_coefs1$P[3]
    mod_tbl1[count, 12] <- sep_coefs1$Beta[4]
    mod_tbl1[count, 13] <- sep_coefs1$CI[4]
    mod_tbl1[count, 14] <- sep_coefs1$P[4]
    mod_tbl1[count, 15] <- sep_coefs1$cilo[4]
    mod_tbl1[count, 16] <- sep_coefs1$cihi[4]
  }
}

mod_tbl1 <- mod_tbl1 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl1, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "airpollution_total_outcomepsystem_zscore_exclRHEA"

coefs1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs1) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps_z) {
  for (d in ap) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <-  imp_norhea %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)
      
      # Save results
      coefs1[count, 1] <- gsub(" ", "_", Sys.time())
      coefs1[count, 2] <- o
      coefs1[count, 3] <- d
      coefs1[count, 4] <- m
      coefs1[count, 5] <- res$estimate[2]
      coefs1[count, 6] <- res$`2.5 %`[2]
      coefs1[count, 7] <- res$`97.5 %`[2]
      coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs1[count, 9] <- res$p.value[2]
    }
  }
}

mod_tbl1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl1) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in ap) {
    sep_coefs1 <- coefs1 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl1[count, 1] <- o
    mod_tbl1[count, 2] <- d
    mod_tbl1[count, 3] <- sep_coefs1$Beta[1]
    mod_tbl1[count, 4] <- sep_coefs1$CI[1]
    mod_tbl1[count, 5] <- sep_coefs1$P[1]
    mod_tbl1[count, 6] <- sep_coefs1$Beta[2]
    mod_tbl1[count, 7] <- sep_coefs1$CI[2]
    mod_tbl1[count, 8] <- sep_coefs1$P[2]
    mod_tbl1[count, 9] <- sep_coefs1$Beta[3]
    mod_tbl1[count, 10] <- sep_coefs1$CI[3]
    mod_tbl1[count, 11] <- sep_coefs1$P[3]
    mod_tbl1[count, 12] <- sep_coefs1$Beta[4]
    mod_tbl1[count, 13] <- sep_coefs1$CI[4]
    mod_tbl1[count, 14] <- sep_coefs1$P[4]
    mod_tbl1[count, 15] <- sep_coefs1$cilo[4]
    mod_tbl1[count, 16] <- sep_coefs1$cihi[4]
  }
}


write.xlsx(mod_tbl1, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```


## Air pollution home, school, commuting and other places with main outcomes
```{r}
analysis <- "airpollution_hsrp_mainoutcome_exclRHEA"

coefs2 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs2) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out) {
  if (o %in% c("AL_2_tot")) {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_norhea %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs2[count, 1] <- gsub(" ", "_", Sys.time())
        coefs2[count, 2] <- o
        coefs2[count, 3] <- d
        coefs2[count, 4] <- m
        coefs2[count, 5] <- res$estimate[2]
        coefs2[count, 6] <- res$`2.5 %`[2]
        coefs2[count, 7] <- res$`97.5 %`[2]
        coefs2[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs2[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_norhea %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs2[count, 1] <- gsub(" ", "_", Sys.time())
        coefs2[count, 2] <- o
        coefs2[count, 3] <- d
        coefs2[count, 4] <- m
        coefs2[count, 5] <- res$estimate[2]
        coefs2[count, 6] <- res$`2.5 %`[2]
        coefs2[count, 7] <- res$`97.5 %`[2]
        coefs2[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs2[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl2 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl2) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in ap_supl) {
    sep_coefs2 <- coefs2 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl2[count, 1] <- o
    mod_tbl2[count, 2] <- d
    mod_tbl2[count, 3] <- sep_coefs2$Beta[1]
    mod_tbl2[count, 4] <- sep_coefs2$CI[1]
    mod_tbl2[count, 5] <- sep_coefs2$P[1]
    mod_tbl2[count, 6] <- sep_coefs2$Beta[2]
    mod_tbl2[count, 7] <- sep_coefs2$CI[2]
    mod_tbl2[count, 8] <- sep_coefs2$P[2]
    mod_tbl2[count, 9] <- sep_coefs2$Beta[3]
    mod_tbl2[count, 10] <- sep_coefs2$CI[3]
    mod_tbl2[count, 11] <- sep_coefs2$P[3]
    mod_tbl2[count, 12] <- sep_coefs2$Beta[4]
    mod_tbl2[count, 13] <- sep_coefs2$CI[4]
    mod_tbl2[count, 14] <- sep_coefs2$P[4]
    mod_tbl2[count, 15] <- sep_coefs2$cilo[4]
    mod_tbl2[count, 16] <- sep_coefs2$cihi[4]
  }
}

mod_tbl2 <- mod_tbl2 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_tot"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl2, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```


## Air pollution home, school, commuting and other places with outcomes per physiological systems
```{r}
analysis <- "airpollution_hsrp_outcomepsystem_exclRHEA"

coefs3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs3) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro")) {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_norhea %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs3[count, 1] <- gsub(" ", "_", Sys.time())
        coefs3[count, 2] <- o
        coefs3[count, 3] <- d
        coefs3[count, 4] <- m
        coefs3[count, 5] <- res$estimate[2]
        coefs3[count, 6] <- res$`2.5 %`[2]
        coefs3[count, 7] <- res$`97.5 %`[2]
        coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs3[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_norhea %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs3[count, 1] <- gsub(" ", "_", Sys.time())
        coefs3[count, 2] <- o
        coefs3[count, 3] <- d
        coefs3[count, 4] <- m
        coefs3[count, 5] <- res$estimate[2]
        coefs3[count, 6] <- res$`2.5 %`[2]
        coefs3[count, 7] <- res$`97.5 %`[2]
        coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs3[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl3) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in ap_supl) {
    sep_coefs3 <- coefs3 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl3[count, 1] <- o
    mod_tbl3[count, 2] <- d
    mod_tbl3[count, 3] <- sep_coefs3$Beta[1]
    mod_tbl3[count, 4] <- sep_coefs3$CI[1]
    mod_tbl3[count, 5] <- sep_coefs3$P[1]
    mod_tbl3[count, 6] <- sep_coefs3$Beta[2]
    mod_tbl3[count, 7] <- sep_coefs3$CI[2]
    mod_tbl3[count, 8] <- sep_coefs3$P[2]
    mod_tbl3[count, 9] <- sep_coefs3$Beta[3]
    mod_tbl3[count, 10] <- sep_coefs3$CI[3]
    mod_tbl3[count, 11] <- sep_coefs3$P[3]
    mod_tbl3[count, 12] <- sep_coefs3$Beta[4]
    mod_tbl3[count, 13] <- sep_coefs3$CI[4]
    mod_tbl3[count, 14] <- sep_coefs3$P[4]
    mod_tbl3[count, 15] <- sep_coefs3$cilo[4]
    mod_tbl3[count, 16] <- sep_coefs3$cihi[4]
  }
}

mod_tbl3 <- mod_tbl3 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl3, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "airpollution_hsrp_outcomepsystem_zscore_exclRHEA"

coefs3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs3) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps_z) {
  for (d in ap_supl) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <-  imp_norhea %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)
      
      # Save results
      coefs3[count, 1] <- gsub(" ", "_", Sys.time())
      coefs3[count, 2] <- o
      coefs3[count, 3] <- d
      coefs3[count, 4] <- m
      coefs3[count, 5] <- res$estimate[2]
      coefs3[count, 6] <- res$`2.5 %`[2]
      coefs3[count, 7] <- res$`97.5 %`[2]
      coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs3[count, 9] <- res$p.value[2]
    }
  }
}

mod_tbl3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl3) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in ap_supl) {
    sep_coefs3 <- coefs3 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl3[count, 1] <- o
    mod_tbl3[count, 2] <- d
    mod_tbl3[count, 3] <- sep_coefs3$Beta[1]
    mod_tbl3[count, 4] <- sep_coefs3$CI[1]
    mod_tbl3[count, 5] <- sep_coefs3$P[1]
    mod_tbl3[count, 6] <- sep_coefs3$Beta[2]
    mod_tbl3[count, 7] <- sep_coefs3$CI[2]
    mod_tbl3[count, 8] <- sep_coefs3$P[2]
    mod_tbl3[count, 9] <- sep_coefs3$Beta[3]
    mod_tbl3[count, 10] <- sep_coefs3$CI[3]
    mod_tbl3[count, 11] <- sep_coefs3$P[3]
    mod_tbl3[count, 12] <- sep_coefs3$Beta[4]
    mod_tbl3[count, 13] <- sep_coefs3$CI[4]
    mod_tbl3[count, 14] <- sep_coefs3$P[4]
    mod_tbl3[count, 15] <- sep_coefs3$cilo[4]
    mod_tbl3[count, 16] <- sep_coefs3$cihi[4]
  }
}

write.xlsx(mod_tbl3, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```



```{r load packages2, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages_2 <- c("tidyverse", "readxl", "data.table", "gt", "writexl")
sapply(packages_2, library, character.only = T)
```

```{r import_results}
# Air pollutants
# Count-based AL, Continuous AL and their weighted average
ap_tot_out <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_mainoutcome_exclRHEA2024-05-22.xlsx")
# Count-based AL and weighted average score per system
ap_tot_outps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_exclRHEA2024-05-22.xlsx")
# Continuous AL and weighted average score per system
ap_tot_outzps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_zscore_exclRHEA2024-05-22.xlsx")

tot_res <- bind_rows(ap_tot_out, ap_tot_outps, ap_tot_outzps)
```

# Table S4 Relative risk of count-based allostatic load score associated with outdoor air pollutants (without RHEA)
```{r tblS4}
tot_res %>%
  select(Outcome, Predictor, exp_beta_mod4, exp_ci_mod4) %>%
  filter(Outcome == "AL_2_tot") %>% 
  gt() %>% 
  tab_header(
    title = "Table S4 Relative risk of count-based allostatic load score associated with outdoor air pollutants (without RHEA)"
  ) %>% 
  fmt_number(decimals = 2, drop_trailing_zeros = F) %>% 
  gt::gtsave(., "/Users/ymou/helix_project/results/Table/TableS4-norhea.docx")
```

# Table S5 Effect estimates of continuous allostatic load score associated with outdoor air pollutants (without RHEA)
```{r tblS5}
tot_res %>%
  select(Outcome, Predictor, beta_mod4, `95ci_mod4`) %>%
  filter(Outcome == "AL_z2_tot") %>% 
  gt() %>% 
  tab_header(
    title = "Table S5 Effect estimates of continuous allostatic load score associated with outdoor air pollutants (without RHEA)"
  ) %>% 
  fmt_number(decimals = 2, drop_trailing_zeros = F) %>% 
  gt::gtsave(., "/Users/ymou/helix_project/results/Table/TableS5-norhea.docx")
```

# Results plot
```{r load packages3, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages_3 <- c("tidyverse", "labelled", "openxlsx", "meta", "readxl", "RColorBrewer", "ggsci", "patchwork")
sapply(packages_3, library, character.only = T)
```

```{r}
# Air pollutants
# Count-based AL, Continuous AL and their weighted average
ap_tot_out <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_mainoutcome_exclRHEA2024-05-22.xlsx")
# Count-based AL and weighted average score per system
ap_tot_outps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_exclRHEA2024-05-22.xlsx")
# Continuous AL and weighted average score per system
ap_tot_outzps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_zscore_exclRHEA2024-05-22.xlsx")

# Count-based AL, Continuous AL and their weighted average: Home, school, commuting
ap_hsr_out <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_hsrp_mainoutcome_exclRHEA2024-05-22.xlsx") %>% filter(!str_detect(Predictor, "_p$")) # other places not incl
# Count-based AL and weighted average score per system: Home, school, commuting
ap_hsr_outps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_hsrp_outcomepsystem_exclRHEA2024-05-22.xlsx") %>% filter(!str_detect(Predictor, "_p$")) # other places not incl
# Continuous AL and weighted average score per system: Home, school, commuting
ap_hsr_outzps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_hsrp_outcomepsystem_zscore_exclRHEA2024-05-22.xlsx") %>% filter(!str_detect(Predictor, "_p$")) # other places not incl

```

```{r merge data}
ap_tot_res <- bind_rows(ap_tot_out, ap_tot_outps, ap_tot_outzps)
ap_tot_res <- ap_tot_res %>%
  mutate(al_type = if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == F, "AL_2",
                           if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == T, "AL_2_wavg",
                                   if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == F, "AL_z2",
                                           if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == T, "AL_z2_wavg", NA)
                                   )
                           )
  )) %>%
  dplyr::rename(
    "beta" = "beta_mod4",
    "low" = "cilo_mod4",
    "hi" = "cihi_mod4"
  ) %>%
  mutate_at(c("Predictor", "Outcome"), as.factor) %>% 
  mutate(Predictor = fct_relevel(Predictor,c("hs_no2_yr_hs_t","hs_pm25_yr_hs_t","hs_pm25abs_yr_hs_t", "hs_pm10_yr_hs_t")),
         Outcome = fct_relevel(Outcome, c("AL_2_tot", "AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro",
                                          "AL_z2_tot", "AL_z2_cardio", "AL_z2_metab", "AL_z2_immune", "AL_z2_neuro",
                                          "AL_2_tot_wavg", "AL_2_cardio_wavg", "AL_2_metab_wavg", "AL_2_immune_wavg", "AL_2_neuro_wavg",
                                          "AL_z2_tot_wavg", "AL_z2_cardio_wavg", "AL_z2_metab_wavg", "AL_z2_immune_wavg", "AL_z2_neuro_wavg"))) %>% 
  mutate(
    Predictor = recode(Predictor,
                       "hs_no2_yr_hs_t" = "NO[2]",
                       "hs_pm10_yr_hs_t" = "PM[10]",
                       "hs_pm25_yr_hs_t" = "PM[2.5]",
                       "hs_pm25abs_yr_hs_t" = "PM[2.5][abs]"
    ),
    Outcome = recode(Outcome,
                     "AL_2_tot" = "Count-based ALS",
                     "AL_2_tot_wavg" = "Count-based weighted average ALS",
                     "AL_z2_tot" = "Continuous ALS",
                     "AL_z2_tot_wavg" = "Continuous weighted average ALS",
                     "AL_2_cardio" = "Count-based cardiovascular ALS",
                     "AL_2_metab" = "Count-based metabolic ALS",
                     "AL_2_immune" = "Count-based immune/inflammatory ALS",
                     "AL_2_neuro" = "Count-based neuroendorine ALS",
                     "AL_2_cardio_wavg" = "Count-based cardiovascular weighted average ALS",
                     "AL_2_metab_wavg" = "Count-based metabolic weighted average ALS",
                     "AL_2_immune_wavg" = "Count-based immune/inflammatory weighted average ALS",
                     "AL_2_neuro_wavg" = "Count-based neuroendorine weighted average ALS",
                     "AL_z2_cardio" = "Continuous cardiovascular ALS",
                     "AL_z2_metab" = "Continuous metabolic ALS",
                     "AL_z2_immune" = "Continuous immune/inflammatory ALS",
                     "AL_z2_neuro" = "Continuous neuroendorine ALS",
                     "AL_z2_cardio_wavg" = "Continuous cardiovascular weighted average ALS",
                     "AL_z2_metab_wavg" = "Continuous metabolic weighted average ALS",
                     "AL_z2_immune_wavg" = "Continuous immune/inflammatory weighted average ALS",
                     "AL_z2_neuro_wavg" = "Continuous neuroendorine weighted average ALS"
    )
  ) %>% 
  rename(Outcomes = Outcome)



ap_hsr_res <- bind_rows(ap_hsr_out, ap_hsr_outps, ap_hsr_outzps)
ap_hsr_res <- ap_hsr_res %>%
  mutate(al_type = if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == F, "AL_2",
                           if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == T, "AL_2_wavg",
                                   if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == F, "AL_z2",
                                           if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == T, "AL_z2_wavg", NA)
                                   )
                           )
  )) %>%
  dplyr::rename(
    "beta" = "beta_mod4",
    "low" = "cilo_mod4",
    "hi" = "cihi_mod4"
  ) %>%
  mutate(type = if_else(str_detect(Predictor, "_h$"), "Home",
                        if_else(str_detect(Predictor, "_s$"), "School", "Commuting")
  )) %>%
  mutate_at(c("Predictor", "Outcome"), as.factor) %>% 
  mutate(Predictor = fct_relevel(Predictor,c("hs_no2_yr_hs_h","hs_no2_yr_hs_s","hs_no2_yr_hs_r",
                                             "hs_pm25_yr_hs_h", "hs_pm25_yr_hs_s", "hs_pm25_yr_hs_r",
                                             "hs_pm25abs_yr_hs_h", "hs_pm25abs_yr_hs_s", "hs_pm25abs_yr_hs_r",
                                             "hs_pm10_yr_hs_h", "hs_pm10_yr_hs_s", "hs_pm10_yr_hs_r")),
         Outcome = fct_relevel(Outcome, c("AL_2_tot", "AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro",
                                          "AL_z2_tot", "AL_z2_cardio", "AL_z2_metab", "AL_z2_immune", "AL_z2_neuro",
                                          "AL_2_tot_wavg", "AL_2_cardio_wavg", "AL_2_metab_wavg", "AL_2_immune_wavg", "AL_2_neuro_wavg",
                                          "AL_z2_tot_wavg", "AL_z2_cardio_wavg", "AL_z2_metab_wavg", "AL_z2_immune_wavg", "AL_z2_neuro_wavg"))) %>% 
  mutate(Predictor = recode(Predictor,
                            "hs_no2_yr_hs_h" = "NO[2]",
                            "hs_no2_yr_hs_s" = "NO[2]",
                            "hs_no2_yr_hs_r" = "NO[2]",
                            "hs_pm25_yr_hs_h" = "PM[2.5]",
                            "hs_pm25_yr_hs_s" = "PM[2.5]",
                            "hs_pm25_yr_hs_r" = "PM[2.5]",
                            "hs_pm25abs_yr_hs_h" = "PM[2.5][abs]",
                            "hs_pm25abs_yr_hs_s" = "PM[2.5][abs]",
                            "hs_pm25abs_yr_hs_r" = "PM[2.5][abs]",
                            "hs_pm10_yr_hs_h" = "PM[10]",
                            "hs_pm10_yr_hs_s" = "PM[10]",
                            "hs_pm10_yr_hs_r" = "PM[10]",
  ),
  Outcome = recode(Outcome,
                   "AL_2_tot" = "Count-based ALS",
                   "AL_2_tot_wavg" = "Count-based weighted average ALS",
                   "AL_z2_tot" = "Continuous ALS",
                   "AL_z2_tot_wavg" = "Continuous weighted average ALS",
                   "AL_2_cardio" = "Count-based cardiovascular ALS",
                   "AL_2_metab" = "Count-based metabolic ALS",
                   "AL_2_immune" = "Count-based immune/inflammatory ALS",
                   "AL_2_neuro" = "Count-based neuroendorine ALS",
                   "AL_2_cardio_wavg" = "Count-based cardiovascular weighted average ALS",
                   "AL_2_metab_wavg" = "Count-based metabolic weighted average ALS",
                   "AL_2_immune_wavg" = "Count-based immune/inflammatory weighted average ALS",
                   "AL_2_neuro_wavg" = "Count-based neuroendorine weighted average ALS",
                   "AL_z2_cardio" = "Continuous cardiovascular ALS",
                   "AL_z2_metab" = "Continuous metabolic ALS",
                   "AL_z2_immune" = "Continuous immune/inflammatory ALS",
                   "AL_z2_neuro" = "Continuous neuroendorine ALS",
                   "AL_z2_cardio_wavg" = "Continuous cardiovascular weighted average ALS",
                   "AL_z2_metab_wavg" = "Continuous metabolic weighted average ALS",
                   "AL_z2_immune_wavg" = "Continuous immune/inflammatory weighted average ALS",
                   "AL_z2_neuro_wavg" = "Continuous neuroendorine weighted average ALS"
  ))  %>% 
  rename(Outcomes = Outcome)
```

# Plots

## Air pollutants

### Count-based ALS
```{r}
dt_p1 <- ap_tot_res %>% filter(al_type == "AL_2")

dt_p1$es <- paste0(
  sprintf("%.2f", dt_p1$exp_beta_mod4), " (",
  sprintf("%.2f", dt_p1$exp_cilo_mod4), "-",
  sprintf("%.2f", dt_p1$exp_cihi_mod4), ")"
)
```

```{r fig.asp = 0.8, fig.width=10}
p1 <- ggplot(
  data = dt_p1,
  aes(x = Outcomes, y = exp_beta_mod4, ymin = exp_cilo_mod4, ymax = exp_cihi_mod4)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 1, linetype = 3) +
  xlab("") +
  ylab("Relative risk (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = exp_cilo_mod4, ymax = exp_cihi_mod4, col = Outcomes), width = 0.5, cex = 1) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, scales = "free_y", labeller = labeller(Predictor = label_parsed)) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  guides(col = guide_legend(nrow = 2, reverse = T, title = "Count-based ALS",
                            title.position = "top")) +
  
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.y.left = element_text(size = 14, angle = 0, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
     labels = c("Count-based neuroendorine ALS" = "Neuroendocrine ALS",
               "Count-based immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Count-based metabolic ALS" = "Metabolic ALS",
               "Count-based cardiovascular ALS" = "Cardiovascular ALS",
               "Count-based ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p1

table_es <- ggplot(dt_p1, aes(x = 0, y = Outcomes, label = es)) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, labeller = labeller(Predictor = label_parsed)) +
  geom_text(hjust = 0, size = 5) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = margin(0, 1, 0, 0),
    strip.text.y = element_blank(),
    panel.background = element_rect(fill = 'white', colour = 'white'),
    strip.background=element_rect(fill="white", colour = 'white')
  )
table_es

# Combine plots using patchwork
combined_plot <- p1 + table_es + plot_layout(ncol = 2, widths = c(0.5, 0.5))

# Display the combined plot
print(combined_plot)
```

```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_RHEA/fig-countAL.png", width = 15, height = 10, units = "in", dpi = 300)
```

### Continuous ALS
```{r}
dt_p3 <- ap_tot_res %>% filter(al_type == "AL_z2")

dt_p3$es <- paste0(
  sprintf("%.2f", dt_p3$beta), " (",
  sprintf("%.2f", dt_p3$low), "-",
  sprintf("%.2f", dt_p3$hi), ")"
)
```

```{r fig.asp = 0.8, fig.width=10}
p3 <- ggplot(
  data = dt_p3,
  aes(x = Outcomes, y = beta, ymin = low, ymax = hi)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 0, linetype = 3) +
  xlab("") +
  ylab("Effect sizes (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = low, ymax = hi, col = Outcomes), width = 0.5, cex = 1) +
  guides(color = guide_legend(nrow = 2, reverse = T, title = "Continuous ALS",
                              title.position = "top")) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, scales = "free_y", labeller = labeller(Predictor = label_parsed)) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.y.left = element_text(size = 14, angle = 0, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
    labels = c("Continuous neuroendorine ALS" = "Neuroendocrine ALS",
               "Continuous immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Continuous metabolic ALS" = "Metabolic ALS",
               "Continuous cardiovascular ALS" = "Cardiovascular ALS",
               "Continuous ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p3

table_es <- ggplot(dt_p3, aes(x = 0, y = Outcomes, label = es)) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, labeller = labeller(Predictor = label_parsed)) +
  geom_text(hjust = 0, size = 5) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = margin(0, 1, 0, 0),
    strip.text.y = element_blank(),
    panel.background = element_rect(fill = 'white', colour = 'white'),
    strip.background=element_rect(fill="white", colour = 'white')
  )
table_es

# Combine plots using patchwork
combined_plot <- p3 + table_es + plot_layout(ncol = 2, widths = c(0.5, 0.5))

# Display the combined plot
print(combined_plot)
```

```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_RHEA/fig-continuousAL.png", width = 15, height = 10, units = "in", dpi = 300)
```

## Air pollutants(home, school, commuting) 

### Count-based ALS
```{r}
dt_p5 <- ap_hsr_res %>% filter(al_type == "AL_2")
```

```{r fig.asp = 0.8, fig.width=10}
p5 <- ggplot(
  data = dt_p5,
  aes(x = Outcomes, y = exp_beta_mod4, ymin = exp_cilo_mod4, ymax = exp_cihi_mod4)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 1, linetype = 3) +
  xlab("") +
  ylab("Relative risk (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = exp_cilo_mod4, ymax = exp_cihi_mod4, col = Outcomes), width = 0.5, cex = 1) +
  facet_grid(rows = vars(Predictor), cols = vars(type), switch = "y", labeller = labeller(Predictor = label_parsed)) +
  guides(col = guide_legend(nrow = 2, reverse = T, title = "Count-based ALS",
                            title.position = "top")) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.x = element_text(size = 14, angle = 0),
    strip.text.y.left = element_text(size = 14, angle = 0),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
    labels = c("Count-based neuroendorine ALS" = "Neuroendocrine ALS",
               "Count-based immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Count-based metabolic ALS" = "Metabolic ALS",
               "Count-based cardiovascular ALS" = "Cardiovascular ALS",
               "Count-based ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p5
```


```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_RHEA/fig-countAL-hsr.png", width = 13, height = 13, units = "in", dpi = 300)
```

### Continuous ALS
```{r}
dt_p7 <- ap_hsr_res %>% filter(al_type == "AL_z2")
```

```{r fig.asp = 0.8, fig.width=10}
p7 <- ggplot(
  data = dt_p7,
  aes(x = Outcomes, y = beta, ymin = low, ymax = hi)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 0, linetype = 3) +
  xlab("") +
  ylab("Relative risk (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = low, ymax = hi, col = Outcomes), width = 0.5, cex = 1) +
  facet_grid(rows = vars(Predictor), cols = vars(type), switch = "y", labeller = labeller(Predictor = label_parsed)) +
  guides(col = guide_legend(nrow = 2, reverse = T, title = "Count-based ALS",
                            title.position = "top")) +
  scale_y_continuous(limits = c(-0.25, 0.95), breaks = c(-0.25, 0, 0.25, 0.5, 0.75)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.x = element_text(size = 14, angle = 0),
    strip.text.y.left = element_text(size = 14, angle = 0),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.spacing.x = unit(4, "mm"),
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white'),
  ) +
  scale_color_npg(
    labels = c("Continuous neuroendorine ALS" = "Neuroendocrine ALS",
               "Continuous immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Continuous metabolic ALS" = "Metabolic ALS",
               "Continuous cardiovascular ALS" = "Cardiovascular ALS",
               "Continuous ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p7
```

```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_RHEA/fig-continousAL-hsr.png", width = 13, height = 13, units = "in", dpi = 300)
```


# ANALYSIS: no RHEA and EDEN
```{r}
# imputed dataset excluding participants from cohort RHEA and EDEN
imp_noedenrhea <- dat_afimp %>% filter(cohort != "RHEA" & cohort != "EDEN") %>% filter(incl_var_out == 1)
imp_noedenrhea <- as.mids(imp_noedenrhea)
```

## Air pollution total and main outcomes
```{r}
analysis <- "airpollution_total_mainoutcome_exclEDENRHEA"

coefs <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out) {
  if (o %in% c("AL_2_tot")) {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noedenrhea %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs[count, 1] <- gsub(" ", "_", Sys.time())
        coefs[count, 2] <- o
        coefs[count, 3] <- d
        coefs[count, 4] <- m
        coefs[count, 5] <- res$estimate[2]
        coefs[count, 6] <- res$`2.5 %`[2]
        coefs[count, 7] <- res$`97.5 %`[2]
        coefs[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noedenrhea %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs[count, 1] <- gsub(" ", "_", Sys.time())
        coefs[count, 2] <- o
        coefs[count, 3] <- d
        coefs[count, 4] <- m
        coefs[count, 5] <- res$estimate[2]
        coefs[count, 6] <- res$`2.5 %`[2]
        coefs[count, 7] <- res$`97.5 %`[2]
        coefs[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs[count, 9] <- res$p.value[2]
      }
    }
  }
}


mod_tbl <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in ap) {
    sep_coefs <- coefs %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl[count, 1] <- o
    mod_tbl[count, 2] <- d
    mod_tbl[count, 3] <- sep_coefs$Beta[1]
    mod_tbl[count, 4] <- sep_coefs$CI[1]
    mod_tbl[count, 5] <- sep_coefs$P[1]
    mod_tbl[count, 6] <- sep_coefs$Beta[2]
    mod_tbl[count, 7] <- sep_coefs$CI[2]
    mod_tbl[count, 8] <- sep_coefs$P[2]
    mod_tbl[count, 9] <- sep_coefs$Beta[3]
    mod_tbl[count, 10] <- sep_coefs$CI[3]
    mod_tbl[count, 11] <- sep_coefs$P[3]
    mod_tbl[count, 12] <- sep_coefs$Beta[4]
    mod_tbl[count, 13] <- sep_coefs$CI[4]
    mod_tbl[count, 14] <- sep_coefs$P[4]
    mod_tbl[count, 15] <- sep_coefs$cilo[4]
    mod_tbl[count, 16] <- sep_coefs$cihi[4]
  }
}

mod_tbl <- mod_tbl %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_tot"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

## Air pollution total and outcomes per physiological systems
```{r}
analysis <- "airpollution_total_outcomepsystem_exclEDENRHEA"

coefs1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs1) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro")) {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noedenrhea %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs1[count, 1] <- gsub(" ", "_", Sys.time())
        coefs1[count, 2] <- o
        coefs1[count, 3] <- d
        coefs1[count, 4] <- m
        coefs1[count, 5] <- res$estimate[2]
        coefs1[count, 6] <- res$`2.5 %`[2]
        coefs1[count, 7] <- res$`97.5 %`[2]
        coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs1[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noedenrhea %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs1[count, 1] <- gsub(" ", "_", Sys.time())
        coefs1[count, 2] <- o
        coefs1[count, 3] <- d
        coefs1[count, 4] <- m
        coefs1[count, 5] <- res$estimate[2]
        coefs1[count, 6] <- res$`2.5 %`[2]
        coefs1[count, 7] <- res$`97.5 %`[2]
        coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs1[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl1) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in ap) {
    sep_coefs1 <- coefs1 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl1[count, 1] <- o
    mod_tbl1[count, 2] <- d
    mod_tbl1[count, 3] <- sep_coefs1$Beta[1]
    mod_tbl1[count, 4] <- sep_coefs1$CI[1]
    mod_tbl1[count, 5] <- sep_coefs1$P[1]
    mod_tbl1[count, 6] <- sep_coefs1$Beta[2]
    mod_tbl1[count, 7] <- sep_coefs1$CI[2]
    mod_tbl1[count, 8] <- sep_coefs1$P[2]
    mod_tbl1[count, 9] <- sep_coefs1$Beta[3]
    mod_tbl1[count, 10] <- sep_coefs1$CI[3]
    mod_tbl1[count, 11] <- sep_coefs1$P[3]
    mod_tbl1[count, 12] <- sep_coefs1$Beta[4]
    mod_tbl1[count, 13] <- sep_coefs1$CI[4]
    mod_tbl1[count, 14] <- sep_coefs1$P[4]
    mod_tbl1[count, 15] <- sep_coefs1$cilo[4]
    mod_tbl1[count, 16] <- sep_coefs1$cihi[4]
  }
}

mod_tbl1 <- mod_tbl1 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl1, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "airpollution_total_outcomepsystem_zscore_exclEDENRHEA"

coefs1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs1) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps_z) {
  for (d in ap) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <-  imp_noedenrhea %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)
      
      # Save results
      coefs1[count, 1] <- gsub(" ", "_", Sys.time())
      coefs1[count, 2] <- o
      coefs1[count, 3] <- d
      coefs1[count, 4] <- m
      coefs1[count, 5] <- res$estimate[2]
      coefs1[count, 6] <- res$`2.5 %`[2]
      coefs1[count, 7] <- res$`97.5 %`[2]
      coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs1[count, 9] <- res$p.value[2]
    }
  }
}

mod_tbl1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl1) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in ap) {
    sep_coefs1 <- coefs1 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl1[count, 1] <- o
    mod_tbl1[count, 2] <- d
    mod_tbl1[count, 3] <- sep_coefs1$Beta[1]
    mod_tbl1[count, 4] <- sep_coefs1$CI[1]
    mod_tbl1[count, 5] <- sep_coefs1$P[1]
    mod_tbl1[count, 6] <- sep_coefs1$Beta[2]
    mod_tbl1[count, 7] <- sep_coefs1$CI[2]
    mod_tbl1[count, 8] <- sep_coefs1$P[2]
    mod_tbl1[count, 9] <- sep_coefs1$Beta[3]
    mod_tbl1[count, 10] <- sep_coefs1$CI[3]
    mod_tbl1[count, 11] <- sep_coefs1$P[3]
    mod_tbl1[count, 12] <- sep_coefs1$Beta[4]
    mod_tbl1[count, 13] <- sep_coefs1$CI[4]
    mod_tbl1[count, 14] <- sep_coefs1$P[4]
    mod_tbl1[count, 15] <- sep_coefs1$cilo[4]
    mod_tbl1[count, 16] <- sep_coefs1$cihi[4]
  }
}


write.xlsx(mod_tbl1, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```


## Air pollution home, school, commuting and other places with main outcomes
```{r}
analysis <- "airpollution_hsrp_mainoutcome_exclEDENRHEA"

coefs2 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs2) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out) {
  if (o %in% c("AL_2_tot")) {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noedenrhea %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs2[count, 1] <- gsub(" ", "_", Sys.time())
        coefs2[count, 2] <- o
        coefs2[count, 3] <- d
        coefs2[count, 4] <- m
        coefs2[count, 5] <- res$estimate[2]
        coefs2[count, 6] <- res$`2.5 %`[2]
        coefs2[count, 7] <- res$`97.5 %`[2]
        coefs2[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs2[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noedenrhea %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs2[count, 1] <- gsub(" ", "_", Sys.time())
        coefs2[count, 2] <- o
        coefs2[count, 3] <- d
        coefs2[count, 4] <- m
        coefs2[count, 5] <- res$estimate[2]
        coefs2[count, 6] <- res$`2.5 %`[2]
        coefs2[count, 7] <- res$`97.5 %`[2]
        coefs2[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs2[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl2 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl2) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in ap_supl) {
    sep_coefs2 <- coefs2 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl2[count, 1] <- o
    mod_tbl2[count, 2] <- d
    mod_tbl2[count, 3] <- sep_coefs2$Beta[1]
    mod_tbl2[count, 4] <- sep_coefs2$CI[1]
    mod_tbl2[count, 5] <- sep_coefs2$P[1]
    mod_tbl2[count, 6] <- sep_coefs2$Beta[2]
    mod_tbl2[count, 7] <- sep_coefs2$CI[2]
    mod_tbl2[count, 8] <- sep_coefs2$P[2]
    mod_tbl2[count, 9] <- sep_coefs2$Beta[3]
    mod_tbl2[count, 10] <- sep_coefs2$CI[3]
    mod_tbl2[count, 11] <- sep_coefs2$P[3]
    mod_tbl2[count, 12] <- sep_coefs2$Beta[4]
    mod_tbl2[count, 13] <- sep_coefs2$CI[4]
    mod_tbl2[count, 14] <- sep_coefs2$P[4]
    mod_tbl2[count, 15] <- sep_coefs2$cilo[4]
    mod_tbl2[count, 16] <- sep_coefs2$cihi[4]
  }
}

mod_tbl2 <- mod_tbl2 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_tot"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl2, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```


## Air pollution home, school, commuting and other places with outcomes per physiological systems
```{r}
analysis <- "airpollution_hsrp_outcomepsystem_exclEDENRHEA"

coefs3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs3) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro")) {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noedenrhea %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs3[count, 1] <- gsub(" ", "_", Sys.time())
        coefs3[count, 2] <- o
        coefs3[count, 3] <- d
        coefs3[count, 4] <- m
        coefs3[count, 5] <- res$estimate[2]
        coefs3[count, 6] <- res$`2.5 %`[2]
        coefs3[count, 7] <- res$`97.5 %`[2]
        coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs3[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <-  imp_noedenrhea %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)
        
        # Save results
        coefs3[count, 1] <- gsub(" ", "_", Sys.time())
        coefs3[count, 2] <- o
        coefs3[count, 3] <- d
        coefs3[count, 4] <- m
        coefs3[count, 5] <- res$estimate[2]
        coefs3[count, 6] <- res$`2.5 %`[2]
        coefs3[count, 7] <- res$`97.5 %`[2]
        coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs3[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl3) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in ap_supl) {
    sep_coefs3 <- coefs3 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl3[count, 1] <- o
    mod_tbl3[count, 2] <- d
    mod_tbl3[count, 3] <- sep_coefs3$Beta[1]
    mod_tbl3[count, 4] <- sep_coefs3$CI[1]
    mod_tbl3[count, 5] <- sep_coefs3$P[1]
    mod_tbl3[count, 6] <- sep_coefs3$Beta[2]
    mod_tbl3[count, 7] <- sep_coefs3$CI[2]
    mod_tbl3[count, 8] <- sep_coefs3$P[2]
    mod_tbl3[count, 9] <- sep_coefs3$Beta[3]
    mod_tbl3[count, 10] <- sep_coefs3$CI[3]
    mod_tbl3[count, 11] <- sep_coefs3$P[3]
    mod_tbl3[count, 12] <- sep_coefs3$Beta[4]
    mod_tbl3[count, 13] <- sep_coefs3$CI[4]
    mod_tbl3[count, 14] <- sep_coefs3$P[4]
    mod_tbl3[count, 15] <- sep_coefs3$cilo[4]
    mod_tbl3[count, 16] <- sep_coefs3$cihi[4]
  }
}

mod_tbl3 <- mod_tbl3 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl3, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "airpollution_hsrp_outcomepsystem_zscore_exclEDENRHEA"

coefs3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs3) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps_z) {
  for (d in ap_supl) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <-  imp_noedenrhea %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)
      
      # Save results
      coefs3[count, 1] <- gsub(" ", "_", Sys.time())
      coefs3[count, 2] <- o
      coefs3[count, 3] <- d
      coefs3[count, 4] <- m
      coefs3[count, 5] <- res$estimate[2]
      coefs3[count, 6] <- res$`2.5 %`[2]
      coefs3[count, 7] <- res$`97.5 %`[2]
      coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs3[count, 9] <- res$p.value[2]
    }
  }
}

mod_tbl3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl3) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in ap_supl) {
    sep_coefs3 <- coefs3 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl3[count, 1] <- o
    mod_tbl3[count, 2] <- d
    mod_tbl3[count, 3] <- sep_coefs3$Beta[1]
    mod_tbl3[count, 4] <- sep_coefs3$CI[1]
    mod_tbl3[count, 5] <- sep_coefs3$P[1]
    mod_tbl3[count, 6] <- sep_coefs3$Beta[2]
    mod_tbl3[count, 7] <- sep_coefs3$CI[2]
    mod_tbl3[count, 8] <- sep_coefs3$P[2]
    mod_tbl3[count, 9] <- sep_coefs3$Beta[3]
    mod_tbl3[count, 10] <- sep_coefs3$CI[3]
    mod_tbl3[count, 11] <- sep_coefs3$P[3]
    mod_tbl3[count, 12] <- sep_coefs3$Beta[4]
    mod_tbl3[count, 13] <- sep_coefs3$CI[4]
    mod_tbl3[count, 14] <- sep_coefs3$P[4]
    mod_tbl3[count, 15] <- sep_coefs3$cilo[4]
    mod_tbl3[count, 16] <- sep_coefs3$cihi[4]
  }
}

write.xlsx(mod_tbl3, file = paste(outdir, analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```



```{r load packages2, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages_2 <- c("tidyverse", "readxl", "data.table", "gt", "writexl")
sapply(packages_2, library, character.only = T)
```

```{r import_results}
# Air pollutants
# Count-based AL, Continuous AL and their weighted average
ap_tot_out <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_mainoutcome_exclEDENRHEA2024-05-22.xlsx")
# Count-based AL and weighted average score per system
ap_tot_outps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_exclEDENRHEA2024-05-22.xlsx")
# Continuous AL and weighted average score per system
ap_tot_outzps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_zscore_exclEDENRHEA2024-05-22.xlsx")

tot_res <- bind_rows(ap_tot_out, ap_tot_outps, ap_tot_outzps)
```

# Table S4 Relative risk of count-based allostatic load score associated with outdoor air pollutants (without EDEN and RHEA)
```{r tblS4}
tot_res %>%
  select(Outcome, Predictor, exp_beta_mod4, exp_ci_mod4) %>%
  filter(Outcome == "AL_2_tot") %>% 
  gt() %>% 
  tab_header(
    title = "Table S4 Relative risk of count-based allostatic load score associated with outdoor air pollutants (without EDEN and RHEA)"
  ) %>% 
  fmt_number(decimals = 2, drop_trailing_zeros = F) %>% 
  gt::gtsave(., "/Users/ymou/helix_project/results/Table/TableS4-noedenrhea.docx")
```

# Table S5 Effect estimates of continuous allostatic load score associated with outdoor air pollutants (without EDEN and RHEA)
```{r tblS5}
tot_res %>%
  select(Outcome, Predictor, beta_mod4, `95ci_mod4`) %>%
  filter(Outcome == "AL_z2_tot") %>% 
  gt() %>% 
  tab_header(
    title = "Table S5 Effect estimates of continuous allostatic load score associated with outdoor air pollutants (without EDEN and RHEA)"
  ) %>% 
  fmt_number(decimals = 2, drop_trailing_zeros = F) %>% 
  gt::gtsave(., "/Users/ymou/helix_project/results/Table/TableS5-noedenrhea.docx")
```

# Results plot
```{r load packages3, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages_3 <- c("tidyverse", "labelled", "openxlsx", "meta", "readxl", "RColorBrewer", "ggsci", "patchwork")
sapply(packages_3, library, character.only = T)
```

```{r}
# Air pollutants
# Count-based AL, Continuous AL and their weighted average
ap_tot_out <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_mainoutcome_exclEDENRHEA2024-05-22.xlsx")
# Count-based AL and weighted average score per system
ap_tot_outps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_exclEDENRHEA2024-05-22.xlsx")
# Continuous AL and weighted average score per system
ap_tot_outzps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_total_outcomepsystem_zscore_exclEDENRHEA2024-05-22.xlsx")

# Count-based AL, Continuous AL and their weighted average: Home, school, commuting
ap_hsr_out <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_hsrp_mainoutcome_exclEDENRHEA2024-05-22.xlsx") %>% filter(!str_detect(Predictor, "_p$")) # other places not incl
# Count-based AL and weighted average score per system: Home, school, commuting
ap_hsr_outps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_hsrp_outcomepsystem_exclEDENRHEA2024-05-22.xlsx") %>% filter(!str_detect(Predictor, "_p$")) # other places not incl
# Continuous AL and weighted average score per system: Home, school, commuting
ap_hsr_outzps <- read_excel("/Users/ymou/helix_project/results/sensitivity_analysis/airpollution_hsrp_outcomepsystem_zscore_exclEDENRHEA2024-05-22.xlsx") %>% filter(!str_detect(Predictor, "_p$")) # other places not incl

```

```{r merge data}
ap_tot_res <- bind_rows(ap_tot_out, ap_tot_outps, ap_tot_outzps)
ap_tot_res <- ap_tot_res %>%
  mutate(al_type = if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == F, "AL_2",
                           if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == T, "AL_2_wavg",
                                   if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == F, "AL_z2",
                                           if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == T, "AL_z2_wavg", NA)
                                   )
                           )
  )) %>%
  dplyr::rename(
    "beta" = "beta_mod4",
    "low" = "cilo_mod4",
    "hi" = "cihi_mod4"
  ) %>%
  mutate_at(c("Predictor", "Outcome"), as.factor) %>% 
  mutate(Predictor = fct_relevel(Predictor,c("hs_no2_yr_hs_t","hs_pm25_yr_hs_t","hs_pm25abs_yr_hs_t", "hs_pm10_yr_hs_t")),
         Outcome = fct_relevel(Outcome, c("AL_2_tot", "AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro",
                                          "AL_z2_tot", "AL_z2_cardio", "AL_z2_metab", "AL_z2_immune", "AL_z2_neuro",
                                          "AL_2_tot_wavg", "AL_2_cardio_wavg", "AL_2_metab_wavg", "AL_2_immune_wavg", "AL_2_neuro_wavg",
                                          "AL_z2_tot_wavg", "AL_z2_cardio_wavg", "AL_z2_metab_wavg", "AL_z2_immune_wavg", "AL_z2_neuro_wavg"))) %>% 
  mutate(
    Predictor = recode(Predictor,
                       "hs_no2_yr_hs_t" = "NO[2]",
                       "hs_pm10_yr_hs_t" = "PM[10]",
                       "hs_pm25_yr_hs_t" = "PM[2.5]",
                       "hs_pm25abs_yr_hs_t" = "PM[2.5][abs]"
    ),
    Outcome = recode(Outcome,
                     "AL_2_tot" = "Count-based ALS",
                     "AL_2_tot_wavg" = "Count-based weighted average ALS",
                     "AL_z2_tot" = "Continuous ALS",
                     "AL_z2_tot_wavg" = "Continuous weighted average ALS",
                     "AL_2_cardio" = "Count-based cardiovascular ALS",
                     "AL_2_metab" = "Count-based metabolic ALS",
                     "AL_2_immune" = "Count-based immune/inflammatory ALS",
                     "AL_2_neuro" = "Count-based neuroendorine ALS",
                     "AL_2_cardio_wavg" = "Count-based cardiovascular weighted average ALS",
                     "AL_2_metab_wavg" = "Count-based metabolic weighted average ALS",
                     "AL_2_immune_wavg" = "Count-based immune/inflammatory weighted average ALS",
                     "AL_2_neuro_wavg" = "Count-based neuroendorine weighted average ALS",
                     "AL_z2_cardio" = "Continuous cardiovascular ALS",
                     "AL_z2_metab" = "Continuous metabolic ALS",
                     "AL_z2_immune" = "Continuous immune/inflammatory ALS",
                     "AL_z2_neuro" = "Continuous neuroendorine ALS",
                     "AL_z2_cardio_wavg" = "Continuous cardiovascular weighted average ALS",
                     "AL_z2_metab_wavg" = "Continuous metabolic weighted average ALS",
                     "AL_z2_immune_wavg" = "Continuous immune/inflammatory weighted average ALS",
                     "AL_z2_neuro_wavg" = "Continuous neuroendorine weighted average ALS"
    )
  ) %>% 
  rename(Outcomes = Outcome) 



ap_hsr_res <- bind_rows(ap_hsr_out, ap_hsr_outps, ap_hsr_outzps)
ap_hsr_res <- ap_hsr_res %>%
  mutate(al_type = if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == F, "AL_2",
                           if_else(str_detect(Outcome, "^AL_2") == T & str_detect(Outcome, "_wavg$") == T, "AL_2_wavg",
                                   if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == F, "AL_z2",
                                           if_else(str_detect(Outcome, "^AL_z2") == T & str_detect(Outcome, "_wavg$") == T, "AL_z2_wavg", NA)
                                   )
                           )
  )) %>%
  dplyr::rename(
    "beta" = "beta_mod4",
    "low" = "cilo_mod4",
    "hi" = "cihi_mod4"
  ) %>%
  mutate(type = if_else(str_detect(Predictor, "_h$"), "Home",
                        if_else(str_detect(Predictor, "_s$"), "School", "Commuting")
  )) %>%
  mutate_at(c("Predictor", "Outcome"), as.factor) %>% 
  mutate(Predictor = fct_relevel(Predictor,c("hs_no2_yr_hs_h","hs_no2_yr_hs_s","hs_no2_yr_hs_r",
                                             "hs_pm25_yr_hs_h", "hs_pm25_yr_hs_s", "hs_pm25_yr_hs_r",
                                             "hs_pm25abs_yr_hs_h", "hs_pm25abs_yr_hs_s", "hs_pm25abs_yr_hs_r",
                                             "hs_pm10_yr_hs_h", "hs_pm10_yr_hs_s", "hs_pm10_yr_hs_r")),
         Outcome = fct_relevel(Outcome, c("AL_2_tot", "AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro",
                                          "AL_z2_tot", "AL_z2_cardio", "AL_z2_metab", "AL_z2_immune", "AL_z2_neuro",
                                          "AL_2_tot_wavg", "AL_2_cardio_wavg", "AL_2_metab_wavg", "AL_2_immune_wavg", "AL_2_neuro_wavg",
                                          "AL_z2_tot_wavg", "AL_z2_cardio_wavg", "AL_z2_metab_wavg", "AL_z2_immune_wavg", "AL_z2_neuro_wavg"))) %>% 
  mutate(Predictor = recode(Predictor,
                            "hs_no2_yr_hs_h" = "NO[2]",
                            "hs_no2_yr_hs_s" = "NO[2]",
                            "hs_no2_yr_hs_r" = "NO[2]",
                            "hs_pm25_yr_hs_h" = "PM[2.5]",
                            "hs_pm25_yr_hs_s" = "PM[2.5]",
                            "hs_pm25_yr_hs_r" = "PM[2.5]",
                            "hs_pm25abs_yr_hs_h" = "PM[2.5][abs]",
                            "hs_pm25abs_yr_hs_s" = "PM[2.5][abs]",
                            "hs_pm25abs_yr_hs_r" = "PM[2.5][abs]",
                            "hs_pm10_yr_hs_h" = "PM[10]",
                            "hs_pm10_yr_hs_s" = "PM[10]",
                            "hs_pm10_yr_hs_r" = "PM[10]",
  ),
  Outcome = recode(Outcome,
                   "AL_2_tot" = "Count-based ALS",
                   "AL_2_tot_wavg" = "Count-based weighted average ALS",
                   "AL_z2_tot" = "Continuous ALS",
                   "AL_z2_tot_wavg" = "Continuous weighted average ALS",
                   "AL_2_cardio" = "Count-based cardiovascular ALS",
                   "AL_2_metab" = "Count-based metabolic ALS",
                   "AL_2_immune" = "Count-based immune/inflammatory ALS",
                   "AL_2_neuro" = "Count-based neuroendorine ALS",
                   "AL_2_cardio_wavg" = "Count-based cardiovascular weighted average ALS",
                   "AL_2_metab_wavg" = "Count-based metabolic weighted average ALS",
                   "AL_2_immune_wavg" = "Count-based immune/inflammatory weighted average ALS",
                   "AL_2_neuro_wavg" = "Count-based neuroendorine weighted average ALS",
                   "AL_z2_cardio" = "Continuous cardiovascular ALS",
                   "AL_z2_metab" = "Continuous metabolic ALS",
                   "AL_z2_immune" = "Continuous immune/inflammatory ALS",
                   "AL_z2_neuro" = "Continuous neuroendorine ALS",
                   "AL_z2_cardio_wavg" = "Continuous cardiovascular weighted average ALS",
                   "AL_z2_metab_wavg" = "Continuous metabolic weighted average ALS",
                   "AL_z2_immune_wavg" = "Continuous immune/inflammatory weighted average ALS",
                   "AL_z2_neuro_wavg" = "Continuous neuroendorine weighted average ALS"
  )) %>% 
  rename(Outcomes = Outcome)
```

# Plots

## Air pollutants

### Count-based ALS
```{r}
dt_p1 <- ap_tot_res %>% filter(al_type == "AL_2")

dt_p1$es <- paste0(
  sprintf("%.2f", dt_p1$exp_beta_mod4), " (",
  sprintf("%.2f", dt_p1$exp_cilo_mod4), "-",
  sprintf("%.2f", dt_p1$exp_cihi_mod4), ")"
)
```

```{r fig.asp = 0.8, fig.width=10}
p1 <- ggplot(
  data = dt_p1,
  aes(x = Outcomes, y = exp_beta_mod4, ymin = exp_cilo_mod4, ymax = exp_cihi_mod4)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 1, linetype = 3) +
  xlab("") +
  ylab("Relative risk (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = exp_cilo_mod4, ymax = exp_cihi_mod4, col = Outcomes), width = 0.5, cex = 1) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, scales = "free_y", labeller = labeller(Predictor = label_parsed)) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  guides(col = guide_legend(nrow = 2, reverse = T, title = "Count-based ALS",
                            title.position = "top")) +
  
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.y.left = element_text(size = 14, angle = 0, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
     labels = c("Count-based neuroendorine ALS" = "Neuroendocrine ALS",
               "Count-based immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Count-based metabolic ALS" = "Metabolic ALS",
               "Count-based cardiovascular ALS" = "Cardiovascular ALS",
               "Count-based ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p1

table_es <- ggplot(dt_p1, aes(x = 0, y = Outcomes, label = es)) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, labeller = labeller(Predictor = label_parsed)) +
  geom_text(hjust = 0, size = 5) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = margin(0, 1, 0, 0),
    strip.text.y = element_blank(),
    panel.background = element_rect(fill = 'white', colour = 'white'),
    strip.background=element_rect(fill="white", colour = 'white')
  )
table_es

# Combine plots using patchwork
combined_plot <- p1 + table_es + plot_layout(ncol = 2, widths = c(0.5, 0.5))

# Display the combined plot
print(combined_plot)
```

```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_EDENRHEA/fig-countAL.png", width = 15, height = 10, units = "in", dpi = 300)
```

### Continuous ALS
```{r}
dt_p3 <- ap_tot_res %>% filter(al_type == "AL_z2")

dt_p3$es <- paste0(
  sprintf("%.2f", dt_p3$beta), " (",
  sprintf("%.2f", dt_p3$low), "-",
  sprintf("%.2f", dt_p3$hi), ")"
)
```

```{r fig.asp = 0.8, fig.width=10}
p3 <- ggplot(
  data = dt_p3,
  aes(x = Outcomes, y = beta, ymin = low, ymax = hi)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 0, linetype = 3) +
  xlab("") +
  ylab("Effect sizes (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = low, ymax = hi, col = Outcomes), width = 0.5, cex = 1) +
  guides(color = guide_legend(nrow = 2, reverse = T, title = "Continuous ALS",
                              title.position = "top")) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, scales = "free_y", labeller = labeller(Predictor = label_parsed)) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.y.left = element_text(size = 14, angle = 0, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
    labels = c("Continuous neuroendorine ALS" = "Neuroendocrine ALS",
               "Continuous immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Continuous metabolic ALS" = "Metabolic ALS",
               "Continuous cardiovascular ALS" = "Cardiovascular ALS",
               "Continuous ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p3

table_es <- ggplot(dt_p3, aes(x = 0, y = Outcomes, label = es)) +
  facet_wrap(~Predictor, strip.position = "left", nrow = 9, labeller = labeller(Predictor = label_parsed)) +
  geom_text(hjust = 0, size = 5) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = margin(0, 1, 0, 0),
    strip.text.y = element_blank(),
    panel.background = element_rect(fill = 'white', colour = 'white'),
    strip.background=element_rect(fill="white", colour = 'white')
  )
table_es

# Combine plots using patchwork
combined_plot <- p3 + table_es + plot_layout(ncol = 2, widths = c(0.5, 0.5))

# Display the combined plot
print(combined_plot)
```

```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_EDENRHEA/fig-continuousAL.png", width = 15, height = 10, units = "in", dpi = 300)
```

## Air pollutants(home, school, commuting) 

### Count-based ALS
```{r}
dt_p5 <- ap_hsr_res %>% filter(al_type == "AL_2")
```

```{r fig.asp = 0.8, fig.width=10}
p5 <- ggplot(
  data = dt_p5,
  aes(x = Outcomes, y = exp_beta_mod4, ymin = exp_cilo_mod4, ymax = exp_cihi_mod4)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 1, linetype = 3) +
  xlab("") +
  ylab("Relative risk (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = exp_cilo_mod4, ymax = exp_cihi_mod4, col = Outcomes), width = 0.5, cex = 1) +
  facet_grid(rows = vars(Predictor), cols = vars(type), switch = "y", labeller = labeller(Predictor = label_parsed)) +
  guides(col = guide_legend(nrow = 2, reverse = T, title = "Count-based ALS",
                            title.position = "top")) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.x = element_text(size = 14, angle = 0),
    strip.text.y.left = element_text(size = 14, angle = 0),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
    labels = c("Count-based neuroendorine ALS" = "Neuroendocrine ALS",
               "Count-based immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Count-based metabolic ALS" = "Metabolic ALS",
               "Count-based cardiovascular ALS" = "Cardiovascular ALS",
               "Count-based ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p5
```


```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_EDENRHEA/fig-countAL-hsr.png", width = 13, height = 13, units = "in", dpi = 300)
```

### Continuous ALS
```{r}
dt_p7 <- ap_hsr_res %>% filter(al_type == "AL_z2")
```

```{r fig.asp = 0.8, fig.width=10}
p7 <- ggplot(
  data = dt_p7,
  aes(x = Outcomes, y = beta, ymin = low, ymax = hi)
) +
  geom_pointrange(aes(col = Outcomes), show.legend = T) +
  geom_hline(yintercept = 0, linetype = 3) +
  xlab("") +
  ylab("Relative risk (95% Confidence Interval)") +
  geom_errorbar(aes(ymin = low, ymax = hi, col = Outcomes), width = 0.5, cex = 1) +
  facet_grid(rows = vars(Predictor), cols = vars(type), switch = "y", labeller = labeller(Predictor = label_parsed)) +
  guides(col = guide_legend(nrow = 2, reverse = T, title = "Count-based ALS",
                            title.position = "top")) +
  # scale_y_continuous(limits = c(-1, 6), breaks = c(-1, 0, 1, 2, 3, 4, 5, 6)) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 14, face = "bold"),
    strip.text.x = element_text(size = 14, angle = 0),
    strip.text.y.left = element_text(size = 14, angle = 0),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key=element_blank(),
    legend.position = "bottom",
    legend.justification = "left",
    panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.background=element_rect(fill="white", colour = 'white')
  ) +
  scale_color_npg(
    labels = c("Continuous neuroendorine ALS" = "Neuroendocrine ALS",
               "Continuous immune/inflammatory ALS" = "Immune/inflammatory ALS", 
               "Continuous metabolic ALS" = "Metabolic ALS",
               "Continuous cardiovascular ALS" = "Cardiovascular ALS",
               "Continuous ALS" = "Total ALS")
  ) +
  coord_flip() +
  ggtitle("")

p7
```

```{r, eval=F}
ggsave("/Users/ymou/helix_project/results/Fig/without_EDENRHEA/fig-continousAL-hsr.png", width = 13, height = 13, units = "in", dpi = 300)
```
