---
title: 'Descriptive analysis: Air pollution, noise level and allostatic load'
author: "Yuchan Mou"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r set_up, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.table.format = "html")
```

```{r load packages, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages <- c(
  "dplyr", "tidyverse", "readxl", "openxlsx", "ggplot2", "kableExtra",
  "ggcorrplot", "JointAI", "patchwork"
)
sapply(packages, library, character.only = T)
```

```{r import data, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
load("/Users/ymou/helix_project/data/analysis_data/df_al_final.RData")
Sys.Date()
```

```{r define variables, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
out <- c("AL_2_tot", "AL_2_tot_wavg", "AL_z2_tot", "AL_z2_tot_wavg")

cardio <- c("hs_zsys_bp", "hs_zdia_bp", "bp_pulse_sd")
metab <- c("hs_zbmi_who", "hs_zwaist_mets", "hs_skf_sum2", "hs_fatprop_bia",
           "hs_hdlchol_c", "hs_non_hdl_c", "hs_triglyc_c", "Leptin", "Adiponectin")
immune <- c("CRP", "IL1beta", "IL6", "IL8", "IL10", "TNFalfa")
neuro <- c("cortisol_prod_log10")
```


# Descriptive analysis of missing in biomarkers

### Number of biomarkers missing per participants in each cohort
```{r}
test <- df_final %>%
  select(cardio, metab, immune, neuro, cohort) %>% 
  mutate(n_NAs = rowSums(is.na(.))) %>% 
  group_by(cohort, n_NAs) %>%
  summarize(Freq=n(), `%`=round(Freq/length(df_final$cohort)*100, 1))


test %>% kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

## Cardiovascular biomarkers

#### Missing of biomarkers in each cohort
```{r missing cardio}
daf_impcheck <- df_final %>%
  select(cardio, cohort) %>%
  filter(!is.na(cohort)) %>%
  group_by(cohort)

# split group by cohort
daf_impcheck_cohort <- group_split(daf_impcheck)
cohort <- group_keys(daf_impcheck)

prop_missing_pervar <- as.data.frame(cbind(
  "# NA-SAB" = colSums(is.na(daf_impcheck_cohort[[1]])),
  "% NA-SAB" = round(colMeans(is.na(daf_impcheck_cohort[[1]])) * 100, 2),
  "# NA-EDEN" = colSums(is.na(daf_impcheck_cohort[[2]])),
  "% NA-EDEN" = round(colMeans(is.na(daf_impcheck_cohort[[2]])) * 100, 2),
  "# NA-BIB" = colSums(is.na(daf_impcheck_cohort[[3]])),
  "% NA-BIB" = round(colMeans(is.na(daf_impcheck_cohort[[3]])) * 100, 2),
  "# NA-RHEA" = colSums(is.na(daf_impcheck_cohort[[4]])),
  "% NA-RHEA" = round(colMeans(is.na(daf_impcheck_cohort[[4]])) * 100, 2),
  "# NA-KANC" = colSums(is.na(daf_impcheck_cohort[[5]])),
  "% NA-KANC" = round(colMeans(is.na(daf_impcheck_cohort[[5]])) * 100, 2),
  "# NA-MOBA" = colSums(is.na(daf_impcheck_cohort[[6]])),
  "% NA-MOBA" = round(colMeans(is.na(daf_impcheck_cohort[[6]])) * 100, 2)
))

prop_missing_pervar %>%
  tibble::rownames_to_column(var = "Variables") %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

#### Number of biomarkers missing per participants in each cohort
```{r}
test <- df_final %>%
  select(cardio, cohort) %>% 
  mutate(n_NAs = rowSums(is.na(.))) %>% 
  group_by(cohort, n_NAs) %>%
  summarize(Freq=n())

test %>% kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

## Metabolic biomarkers

Unit z score

#### Missing of biomarkers in each cohort
```{r missing metab}
daf_impcheck <- df_final %>%
  select(metab, cohort) %>%
  filter(!is.na(cohort)) %>%
  group_by(cohort)

# split group by cohort
daf_impcheck_cohort <- group_split(daf_impcheck)
cohort <- group_keys(daf_impcheck)

prop_missing_pervar <- as.data.frame(cbind(
  "# NA-SAB" = colSums(is.na(daf_impcheck_cohort[[1]])),
  "% NA-SAB" = round(colMeans(is.na(daf_impcheck_cohort[[1]])) * 100, 2),
  "# NA-EDEN" = colSums(is.na(daf_impcheck_cohort[[2]])),
  "% NA-EDEN" = round(colMeans(is.na(daf_impcheck_cohort[[2]])) * 100, 2),
  "# NA-BIB" = colSums(is.na(daf_impcheck_cohort[[3]])),
  "% NA-BIB" = round(colMeans(is.na(daf_impcheck_cohort[[3]])) * 100, 2),
  "# NA-RHEA" = colSums(is.na(daf_impcheck_cohort[[4]])),
  "% NA-RHEA" = round(colMeans(is.na(daf_impcheck_cohort[[4]])) * 100, 2),
  "# NA-KANC" = colSums(is.na(daf_impcheck_cohort[[5]])),
  "% NA-KANC" = round(colMeans(is.na(daf_impcheck_cohort[[5]])) * 100, 2),
  "# NA-MOBA" = colSums(is.na(daf_impcheck_cohort[[6]])),
  "% NA-MOBA" = round(colMeans(is.na(daf_impcheck_cohort[[6]])) * 100, 2)
))

prop_missing_pervar %>%
  filter(row_number() <= n()-1) %>% # remove last row: cohort
  tibble::rownames_to_column(var = "Variables") %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

#### Number of biomarkers missing per participants in each cohort
```{r}
test <- df_final %>%
  select(metab, cohort) %>% 
  mutate(n_NAs = rowSums(is.na(.))) %>% 
  group_by(cohort, n_NAs) %>%
  summarize(Freq=n())

test %>% kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

## Inflammatory biomarkers

Unit pg/mL, log2 transformed, imputed and normalized

#### Missing of biomarkers in each cohort
```{r missing immune}
daf_impcheck <- df_final %>%
  select(immune, cohort) %>%
  filter(!is.na(cohort)) %>%
  group_by(cohort)

# split group by cohort
daf_impcheck_cohort <- group_split(daf_impcheck)
cohort <- group_keys(daf_impcheck)

prop_missing_pervar <- as.data.frame(cbind(
  "# NA-SAB" = colSums(is.na(daf_impcheck_cohort[[1]])),
  "% NA-SAB" = round(colMeans(is.na(daf_impcheck_cohort[[1]])) * 100, 2),
  "# NA-EDEN" = colSums(is.na(daf_impcheck_cohort[[2]])),
  "% NA-EDEN" = round(colMeans(is.na(daf_impcheck_cohort[[2]])) * 100, 2),
  "# NA-BIB" = colSums(is.na(daf_impcheck_cohort[[3]])),
  "% NA-BIB" = round(colMeans(is.na(daf_impcheck_cohort[[3]])) * 100, 2),
  "# NA-RHEA" = colSums(is.na(daf_impcheck_cohort[[4]])),
  "% NA-RHEA" = round(colMeans(is.na(daf_impcheck_cohort[[4]])) * 100, 2),
  "# NA-KANC" = colSums(is.na(daf_impcheck_cohort[[5]])),
  "% NA-KANC" = round(colMeans(is.na(daf_impcheck_cohort[[5]])) * 100, 2),
  "# NA-MOBA" = colSums(is.na(daf_impcheck_cohort[[6]])),
  "% NA-MOBA" = round(colMeans(is.na(daf_impcheck_cohort[[6]])) * 100, 2)
))

prop_missing_pervar %>%
  filter(row_number() <= n()-1) %>% # remove last row: cohort
  tibble::rownames_to_column(var = "Variables") %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

#### Number of biomarkers missing per participants in each cohort
```{r}
test <- df_final %>%
  select(immune, cohort) %>% 
  mutate(n_NAs = rowSums(is.na(.))) %>% 
  group_by(cohort, n_NAs) %>%
  summarize(Freq=n())

test %>% kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

## Neuroendocrine biomarkers

#### Missing of biomarkers in each cohort
```{r missing neuro}
daf_impcheck <- df_final %>%
  select(neuro, cohort) %>%
  filter(!is.na(cohort)) %>%
  group_by(cohort)

# split group by cohort
daf_impcheck_cohort <- group_split(daf_impcheck)
cohort <- group_keys(daf_impcheck)

prop_missing_pervar <- as.data.frame(cbind(
  "# NA-SAB" = colSums(is.na(daf_impcheck_cohort[[1]])),
  "% NA-SAB" = round(colMeans(is.na(daf_impcheck_cohort[[1]])) * 100, 2),
  "# NA-EDEN" = colSums(is.na(daf_impcheck_cohort[[2]])),
  "% NA-EDEN" = round(colMeans(is.na(daf_impcheck_cohort[[2]])) * 100, 2),
  "# NA-BIB" = colSums(is.na(daf_impcheck_cohort[[3]])),
  "% NA-BIB" = round(colMeans(is.na(daf_impcheck_cohort[[3]])) * 100, 2),
  "# NA-RHEA" = colSums(is.na(daf_impcheck_cohort[[4]])),
  "% NA-RHEA" = round(colMeans(is.na(daf_impcheck_cohort[[4]])) * 100, 2),
  "# NA-KANC" = colSums(is.na(daf_impcheck_cohort[[5]])),
  "% NA-KANC" = round(colMeans(is.na(daf_impcheck_cohort[[5]])) * 100, 2),
  "# NA-MOBA" = colSums(is.na(daf_impcheck_cohort[[6]])),
  "% NA-MOBA" = round(colMeans(is.na(daf_impcheck_cohort[[6]])) * 100, 2)
))

prop_missing_pervar %>%
  filter(row_number() <= n()-1) %>% # remove last row: cohort
  tibble::rownames_to_column(var = "Variables") %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

#### Number of biomarkers missing per participants in each cohort
```{r}
test <- df_final %>%
  select(neuro, cohort) %>% 
  mutate(n_NAs = rowSums(is.na(.))) %>% 
  group_by(cohort, n_NAs) %>%
  summarize(Freq=n()) 

test %>% kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

# Descriptive analysis of outcome
## Complete cases of outcomes
```{r complete_outcome}
out_desc <- df_final %>% 
  filter(!is.na(e3_sex)) %>% 
  select(cohort, all_of(out)) %>%
  group_by(cohort)

as.data.frame(cbind(
  "#" = colSums(!is.na(out_desc))
)) %>% 
  tibble::rownames_to_column(var = "Variables") %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")

out_desc_cohort <- group_split(out_desc)
cohort <- group_keys(out_desc)

outcome_desc <- as.data.frame(cbind(
  "# SAB" = colSums(!is.na(out_desc_cohort[[1]])),
  "# EDEN" = colSums(!is.na(out_desc_cohort[[2]])),
  "# BIB" = colSums(!is.na(out_desc_cohort[[3]])),
  "# RHEA" = colSums(!is.na(out_desc_cohort[[4]])),
  "# KANC" = colSums(!is.na(out_desc_cohort[[5]])),
  "# MOBA" = colSums(!is.na(out_desc_cohort[[6]]))
))

outcome_desc %>%
  tibble::rownames_to_column(var = "Variables") %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, fixed_thead = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

