---
title: "Analysis"
author: "Yuchan Mou"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.table.format = "html")
```

```{r load packages, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages <- c("MASS", "tidyverse", "mice", "tableone", "openxlsx")
sapply(packages, library, character.only = T)
```

```{r import data}
load("/Users/ymou/helix_project/data/analysis_data/imp_full_ds.Rdata")
analysis_date <- Sys.Date()
```

```{r define variables, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# Exposures: air pollutants and noise level
ap <- c(
  "hs_no2_yr_hs_t",
  "hs_pm25_yr_hs_t",
  "hs_pm25abs_yr_hs_t",
  "hs_pm10_yr_hs_t"
)
ap_supl <- c(
  "hs_no2_yr_hs_h", "hs_no2_yr_hs_s", "hs_no2_yr_hs_r", "hs_no2_yr_hs_p",
  "hs_pm25_yr_hs_h", "hs_pm25_yr_hs_s", "hs_pm25_yr_hs_r", "hs_pm25_yr_hs_p",
  "hs_pm25abs_yr_hs_h", "hs_pm25abs_yr_hs_s", "hs_pm25abs_yr_hs_r", "hs_pm25abs_yr_hs_p",
  "hs_pm10_yr_hs_h", "hs_pm10_yr_hs_s", "hs_pm10_yr_hs_r", "hs_pm10_yr_hs_p"
)
noise <- c("hs_lden_c_h", "hs_lden_c_s")
noise_supl <- c("hs_lden_h", "hs_lden_s", "hs_lden_t")


# Outcomes: AL scores
out <- c("AL_2_tot", "AL_2_tot_wavg", "AL_z2_tot", "AL_z2_tot_wavg") # sex-specific scores
out_supl <- c("AL_1_tot", "AL_1_tot_wavg", "AL_z1_tot", "AL_z1_tot_wavg") # scores based on whole study samples, not used in the analysis

# Outcomes per physiological systems
out_ps <- c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro", "AL_2_cardio_wavg", "AL_2_metab_wavg", "AL_2_immune_wavg", "AL_2_neuro_wavg")
out_ps_z <- c("AL_z2_cardio", "AL_z2_metab", "AL_z2_immune", "AL_z2_neuro", "AL_z2_cardio_wavg", "AL_z2_metab_wavg", "AL_z2_immune_wavg", "AL_z2_neuro_wavg")


# Models
model <- c(
  "e3_sex + hs_child_age_years + h_ethnicity_cauc",
  "e3_sex + hs_child_age_years + h_ethnicity_cauc + hs_mvpa + hs_sd_wk",
  "e3_sex + hs_child_age_years + h_ethnicity_cauc + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn",
  "e3_sex + hs_child_age_years + h_ethnicity_cauc + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn + hs_globalexp_2cat"
)
```

# Apply increments

```{r}
#  1 micrograms per cubic meter µg/m3 -> 
dat_afimp <- complete(imp_full, action = "long", include = T) %>%
  mutate(
    hs_no2_yr_hs_t = hs_no2_yr_hs_t / 10,
    hs_no2_yr_hs_h = hs_no2_yr_hs_h / 10,
    hs_no2_yr_hs_s = hs_no2_yr_hs_s / 10,
    hs_no2_yr_hs_r = hs_no2_yr_hs_r / 10,
    hs_no2_yr_hs_p = hs_no2_yr_hs_p / 10,
    hs_pm25_yr_hs_t = hs_pm25_yr_hs_t / 5,
    hs_pm25_yr_hs_h = hs_pm25_yr_hs_h / 5,
    hs_pm25_yr_hs_s = hs_pm25_yr_hs_s / 5,
    hs_pm25_yr_hs_r = hs_pm25_yr_hs_r / 5,
    hs_pm25_yr_hs_p = hs_pm25_yr_hs_p / 5,
    hs_pm10_yr_hs_t = hs_pm10_yr_hs_t / 10,
    hs_pm10_yr_hs_h = hs_pm10_yr_hs_h / 10,
    hs_pm10_yr_hs_s = hs_pm10_yr_hs_s / 10,
    hs_pm10_yr_hs_r = hs_pm10_yr_hs_r / 10,
    hs_pm10_yr_hs_p = hs_pm10_yr_hs_p / 10
  )

dat_afimp_al_nonimp <- dat_afimp %>% filter(incl_var_out == 1)

imp_full <- as.mids(dat_afimp_al_nonimp)
imp_full_supl <- as.mids(dat_afimp)

rm(dat_afimp_al_nonimp, dat_afimp)
```

# ANALYSIS
## Model test and model assumption check
```{r, eval=FALSE}
test <- complete(imp_full, n = 25)

# check mean = variance for y
ggplot(data = test, aes(x = hs_no2_yr_hs_t, AL_2_tot)) +
  geom_point()
ggplot(data = test, aes(x = hs_pm25_yr_hs_t, AL_2_tot)) +
  geom_point()
ggplot(data = test, aes(x = hs_pm25abs_yr_hs_t, AL_2_tot)) +
  geom_point()
ggplot(data = test, aes(x = hs_pm10_yr_hs_t, AL_2_tot)) +
  geom_point()
# violation of assumption: the mean of a Poisson random variable must be equal to its variance.

# check linear association
# linear trend + confidence interval
ggplot(data = test, aes(x = hs_no2_yr_hs_t, y = log(AL_2_tot), color = cohort)) +
  geom_point() +
  geom_smooth(aes(group = FAS_cat), method = lm, se = TRUE)
ggplot(data = test, aes(x = hs_pm25_yr_hs_t, y = log(AL_2_tot), color = FAS_cat)) +
  geom_point() +
  geom_smooth(aes(group = FAS_cat), method = lm, se = TRUE)
ggplot(data = test, aes(x = hs_pm25abs_yr_hs_t, y = log(AL_2_tot), color = FAS_cat)) +
  geom_point() +
  geom_smooth(aes(group = FAS_cat), method = lm, se = TRUE)
ggplot(data = test, aes(x = hs_pm10_yr_hs_t, y = log(AL_2_tot), color = FAS_cat)) +
  geom_point() +
  geom_smooth(aes(group = FAS_cat), method = lm, se = TRUE)

# test in a model
no2 <- glm(
  data = test, formula = AL_2_tot ~ hs_no2_yr_hs_t + e3_sex + hs_child_age_years + h_ethnicity_cauc + cohort + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn + hs_globalexp_2cat,
  family = "poisson"
)
# model deviance/degree of freedom is larger than 1, negative binomial should be considered
summary(no2)

# test for overdispension
fit.overdisp <- glm(
  formula = AL_2_tot ~ hs_no2_yr_hs_t + e3_sex + hs_child_age_years + h_ethnicity_cauc + cohort + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn + hs_globalexp_2cat, family = "quasipoisson",
  data = test
)
summary(fit.overdisp)$dispersion # 2.173566
pchisq(summary(fit.overdisp)$dispersion * no2$df.residual,
  no2$df.residual,
  lower = FALSE
)
# 2.772913e-79, significance for overdispersion

# test negative binomial distribution
no2.nb <- glm.nb(
  data = test, formula = AL_2_tot ~ hs_no2_yr_hs_t + e3_sex + hs_child_age_years + h_ethnicity_cauc + cohort + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn + hs_globalexp_2cat,
  link = "log"
)

summary(no2.nb)
# Okay


# test gaussian for weighted count-based AL scores
no2 <- glm(
  data = test, formula = AL_2_tot_wavg ~ hs_no2_yr_hs_t + e3_sex + hs_child_age_years + h_ethnicity_cauc + cohort + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn + hs_globalexp_2cat,
  family = "gaussian"
)

plot(no2)
summary(no2)
# Okay
```

# Air pollution total and main outcomes
```{r}
analysis <- "airpollution_total_mainoutcome"

coefs <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out) {
  if (o %in% c("AL_2_tot")) {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs[count, 1] <- gsub(" ", "_", Sys.time())
        coefs[count, 2] <- o
        coefs[count, 3] <- d
        coefs[count, 4] <- m
        coefs[count, 5] <- res$estimate[2]
        coefs[count, 6] <- res$`2.5 %`[2]
        coefs[count, 7] <- res$`97.5 %`[2]
        coefs[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs[count, 1] <- gsub(" ", "_", Sys.time())
        coefs[count, 2] <- o
        coefs[count, 3] <- d
        coefs[count, 4] <- m
        coefs[count, 5] <- res$estimate[2]
        coefs[count, 6] <- res$`2.5 %`[2]
        coefs[count, 7] <- res$`97.5 %`[2]
        coefs[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs[count, 9] <- res$p.value[2]
      }
    }
  }
}


mod_tbl <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in ap) {
    sep_coefs <- coefs %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl[count, 1] <- o
    mod_tbl[count, 2] <- d
    mod_tbl[count, 3] <- sep_coefs$Beta[1]
    mod_tbl[count, 4] <- sep_coefs$CI[1]
    mod_tbl[count, 5] <- sep_coefs$P[1]
    mod_tbl[count, 6] <- sep_coefs$Beta[2]
    mod_tbl[count, 7] <- sep_coefs$CI[2]
    mod_tbl[count, 8] <- sep_coefs$P[2]
    mod_tbl[count, 9] <- sep_coefs$Beta[3]
    mod_tbl[count, 10] <- sep_coefs$CI[3]
    mod_tbl[count, 11] <- sep_coefs$P[3]
    mod_tbl[count, 12] <- sep_coefs$Beta[4]
    mod_tbl[count, 13] <- sep_coefs$CI[4]
    mod_tbl[count, 14] <- sep_coefs$P[4]
    mod_tbl[count, 15] <- sep_coefs$cilo[4]
    mod_tbl[count, 16] <- sep_coefs$cihi[4]
  }
}

mod_tbl <- mod_tbl %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_tot"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl, file = paste("/Users/ymou/helix_project/results/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

# Air pollution total and outcomes per physiological systems
```{r}
analysis <- "airpollution_total_outcomepsystem"

coefs1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs1) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro")) {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs1[count, 1] <- gsub(" ", "_", Sys.time())
        coefs1[count, 2] <- o
        coefs1[count, 3] <- d
        coefs1[count, 4] <- m
        coefs1[count, 5] <- res$estimate[2]
        coefs1[count, 6] <- res$`2.5 %`[2]
        coefs1[count, 7] <- res$`97.5 %`[2]
        coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs1[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs1[count, 1] <- gsub(" ", "_", Sys.time())
        coefs1[count, 2] <- o
        coefs1[count, 3] <- d
        coefs1[count, 4] <- m
        coefs1[count, 5] <- res$estimate[2]
        coefs1[count, 6] <- res$`2.5 %`[2]
        coefs1[count, 7] <- res$`97.5 %`[2]
        coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs1[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl1) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in ap) {
    sep_coefs1 <- coefs1 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl1[count, 1] <- o
    mod_tbl1[count, 2] <- d
    mod_tbl1[count, 3] <- sep_coefs1$Beta[1]
    mod_tbl1[count, 4] <- sep_coefs1$CI[1]
    mod_tbl1[count, 5] <- sep_coefs1$P[1]
    mod_tbl1[count, 6] <- sep_coefs1$Beta[2]
    mod_tbl1[count, 7] <- sep_coefs1$CI[2]
    mod_tbl1[count, 8] <- sep_coefs1$P[2]
    mod_tbl1[count, 9] <- sep_coefs1$Beta[3]
    mod_tbl1[count, 10] <- sep_coefs1$CI[3]
    mod_tbl1[count, 11] <- sep_coefs1$P[3]
    mod_tbl1[count, 12] <- sep_coefs1$Beta[4]
    mod_tbl1[count, 13] <- sep_coefs1$CI[4]
    mod_tbl1[count, 14] <- sep_coefs1$P[4]
    mod_tbl1[count, 15] <- sep_coefs1$cilo[4]
    mod_tbl1[count, 16] <- sep_coefs1$cihi[4]
  }
}

mod_tbl1 <- mod_tbl1 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl1, file = paste("/Users/ymou/helix_project/results/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "airpollution_total_outcomepsystem_zscore"

coefs1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs1) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps_z) {
  for (d in ap) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <- imp_full %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)

      # Save results
      coefs1[count, 1] <- gsub(" ", "_", Sys.time())
      coefs1[count, 2] <- o
      coefs1[count, 3] <- d
      coefs1[count, 4] <- m
      coefs1[count, 5] <- res$estimate[2]
      coefs1[count, 6] <- res$`2.5 %`[2]
      coefs1[count, 7] <- res$`97.5 %`[2]
      coefs1[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs1[count, 9] <- res$p.value[2]
    }
  }
}

mod_tbl1 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl1) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in ap) {
    sep_coefs1 <- coefs1 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl1[count, 1] <- o
    mod_tbl1[count, 2] <- d
    mod_tbl1[count, 3] <- sep_coefs1$Beta[1]
    mod_tbl1[count, 4] <- sep_coefs1$CI[1]
    mod_tbl1[count, 5] <- sep_coefs1$P[1]
    mod_tbl1[count, 6] <- sep_coefs1$Beta[2]
    mod_tbl1[count, 7] <- sep_coefs1$CI[2]
    mod_tbl1[count, 8] <- sep_coefs1$P[2]
    mod_tbl1[count, 9] <- sep_coefs1$Beta[3]
    mod_tbl1[count, 10] <- sep_coefs1$CI[3]
    mod_tbl1[count, 11] <- sep_coefs1$P[3]
    mod_tbl1[count, 12] <- sep_coefs1$Beta[4]
    mod_tbl1[count, 13] <- sep_coefs1$CI[4]
    mod_tbl1[count, 14] <- sep_coefs1$P[4]
    mod_tbl1[count, 15] <- sep_coefs1$cilo[4]
    mod_tbl1[count, 16] <- sep_coefs1$cihi[4]
  }
}


write.xlsx(mod_tbl1, file = paste("/Users/ymou/helix_project/results/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```


# Air pollution home, school, commuting and other places with main outcomes
```{r}
analysis <- "airpollution_hsrp_mainoutcome"

coefs2 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs2) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out) {
  if (o %in% c("AL_2_tot")) {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs2[count, 1] <- gsub(" ", "_", Sys.time())
        coefs2[count, 2] <- o
        coefs2[count, 3] <- d
        coefs2[count, 4] <- m
        coefs2[count, 5] <- res$estimate[2]
        coefs2[count, 6] <- res$`2.5 %`[2]
        coefs2[count, 7] <- res$`97.5 %`[2]
        coefs2[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs2[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs2[count, 1] <- gsub(" ", "_", Sys.time())
        coefs2[count, 2] <- o
        coefs2[count, 3] <- d
        coefs2[count, 4] <- m
        coefs2[count, 5] <- res$estimate[2]
        coefs2[count, 6] <- res$`2.5 %`[2]
        coefs2[count, 7] <- res$`97.5 %`[2]
        coefs2[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs2[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl2 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl2) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in ap_supl) {
    sep_coefs2 <- coefs2 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl2[count, 1] <- o
    mod_tbl2[count, 2] <- d
    mod_tbl2[count, 3] <- sep_coefs2$Beta[1]
    mod_tbl2[count, 4] <- sep_coefs2$CI[1]
    mod_tbl2[count, 5] <- sep_coefs2$P[1]
    mod_tbl2[count, 6] <- sep_coefs2$Beta[2]
    mod_tbl2[count, 7] <- sep_coefs2$CI[2]
    mod_tbl2[count, 8] <- sep_coefs2$P[2]
    mod_tbl2[count, 9] <- sep_coefs2$Beta[3]
    mod_tbl2[count, 10] <- sep_coefs2$CI[3]
    mod_tbl2[count, 11] <- sep_coefs2$P[3]
    mod_tbl2[count, 12] <- sep_coefs2$Beta[4]
    mod_tbl2[count, 13] <- sep_coefs2$CI[4]
    mod_tbl2[count, 14] <- sep_coefs2$P[4]
    mod_tbl2[count, 15] <- sep_coefs2$cilo[4]
    mod_tbl2[count, 16] <- sep_coefs2$cihi[4]
  }
}

mod_tbl2 <- mod_tbl2 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_tot"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl2, file = paste("/Users/ymou/helix_project/results/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```


# Air pollution home, school, commuting and other places with outcomes per physiological systems
```{r}
analysis <- "airpollution_hsrp_outcomepsystem"

coefs3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs3) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro")) {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs3[count, 1] <- gsub(" ", "_", Sys.time())
        coefs3[count, 2] <- o
        coefs3[count, 3] <- d
        coefs3[count, 4] <- m
        coefs3[count, 5] <- res$estimate[2]
        coefs3[count, 6] <- res$`2.5 %`[2]
        coefs3[count, 7] <- res$`97.5 %`[2]
        coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs3[count, 9] <- res$p.value[2]
      }
    }
  } else {
    for (d in ap_supl) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs3[count, 1] <- gsub(" ", "_", Sys.time())
        coefs3[count, 2] <- o
        coefs3[count, 3] <- d
        coefs3[count, 4] <- m
        coefs3[count, 5] <- res$estimate[2]
        coefs3[count, 6] <- res$`2.5 %`[2]
        coefs3[count, 7] <- res$`97.5 %`[2]
        coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs3[count, 9] <- res$p.value[2]
      }
    }
  }
}

mod_tbl3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl3) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in ap_supl) {
    sep_coefs3 <- coefs3 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl3[count, 1] <- o
    mod_tbl3[count, 2] <- d
    mod_tbl3[count, 3] <- sep_coefs3$Beta[1]
    mod_tbl3[count, 4] <- sep_coefs3$CI[1]
    mod_tbl3[count, 5] <- sep_coefs3$P[1]
    mod_tbl3[count, 6] <- sep_coefs3$Beta[2]
    mod_tbl3[count, 7] <- sep_coefs3$CI[2]
    mod_tbl3[count, 8] <- sep_coefs3$P[2]
    mod_tbl3[count, 9] <- sep_coefs3$Beta[3]
    mod_tbl3[count, 10] <- sep_coefs3$CI[3]
    mod_tbl3[count, 11] <- sep_coefs3$P[3]
    mod_tbl3[count, 12] <- sep_coefs3$Beta[4]
    mod_tbl3[count, 13] <- sep_coefs3$CI[4]
    mod_tbl3[count, 14] <- sep_coefs3$P[4]
    mod_tbl3[count, 15] <- sep_coefs3$cilo[4]
    mod_tbl3[count, 16] <- sep_coefs3$cihi[4]
  }
}

mod_tbl3 <- mod_tbl3 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl3, file = paste("/Users/ymou/helix_project/results/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "airpollution_hsrp_outcomepsystem_zscore"

coefs3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 9))
colnames(coefs3) <- c("DateTime", "Outcome", "Predictor", "Model", "Beta", "cilo", "cihi", "CI", "P")

count <- 0
for (o in out_ps_z) {
  for (d in ap_supl) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <- imp_full %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)

      # Save results
      coefs3[count, 1] <- gsub(" ", "_", Sys.time())
      coefs3[count, 2] <- o
      coefs3[count, 3] <- d
      coefs3[count, 4] <- m
      coefs3[count, 5] <- res$estimate[2]
      coefs3[count, 6] <- res$`2.5 %`[2]
      coefs3[count, 7] <- res$`97.5 %`[2]
      coefs3[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs3[count, 9] <- res$p.value[2]
    }
  }
}

mod_tbl3 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl3) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in ap_supl) {
    sep_coefs3 <- coefs3 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl3[count, 1] <- o
    mod_tbl3[count, 2] <- d
    mod_tbl3[count, 3] <- sep_coefs3$Beta[1]
    mod_tbl3[count, 4] <- sep_coefs3$CI[1]
    mod_tbl3[count, 5] <- sep_coefs3$P[1]
    mod_tbl3[count, 6] <- sep_coefs3$Beta[2]
    mod_tbl3[count, 7] <- sep_coefs3$CI[2]
    mod_tbl3[count, 8] <- sep_coefs3$P[2]
    mod_tbl3[count, 9] <- sep_coefs3$Beta[3]
    mod_tbl3[count, 10] <- sep_coefs3$CI[3]
    mod_tbl3[count, 11] <- sep_coefs3$P[3]
    mod_tbl3[count, 12] <- sep_coefs3$Beta[4]
    mod_tbl3[count, 13] <- sep_coefs3$CI[4]
    mod_tbl3[count, 14] <- sep_coefs3$P[4]
    mod_tbl3[count, 15] <- sep_coefs3$cilo[4]
    mod_tbl3[count, 16] <- sep_coefs3$cihi[4]
  }
}

write.xlsx(mod_tbl3, file = paste("/Users/ymou/helix_project/results/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

# Noise home, school and main outcomes
EDEN removed in the analysis because no data available. 
```{r}
analysis <- "noise_mainoutcome"

imp_full_noise <- complete(imp_full, "long", include = T) %>%
  filter(cohort != "EDEN") %>%
  as.mids()

coefs4 <- as.data.frame(matrix(NA, nrow = 1, ncol = 19))
colnames(coefs4) <- c(
  "DateTime", "Outcome", "Predictor", "Model", "Beta1", "cilo1", "cihi1", "CI1", "P1",
  "Beta2", "cilo2", "cihi2", "CI2", "P2", "Beta3", "cilo3", "cihi3", "CI3", "P3"
)

count <- 0
for (o in out) {
  if (o %in% c("AL_2_tot")) {
    for (d in noise) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full_noise %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs4[count, 1] <- gsub(" ", "_", Sys.time())
        coefs4[count, 2] <- o
        coefs4[count, 3] <- d
        coefs4[count, 4] <- m
        coefs4[count, 5] <- res$estimate[2]
        coefs4[count, 6] <- res$`2.5 %`[2]
        coefs4[count, 7] <- res$`97.5 %`[2]
        coefs4[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs4[count, 9] <- res$p.value[2]
        coefs4[count, 10] <- res$estimate[3]
        coefs4[count, 11] <- res$`2.5 %`[3]
        coefs4[count, 12] <- res$`97.5 %`[3]
        coefs4[count, 13] <- paste(res$`2.5 %`[3], ",", " ", res$`97.5 %`[3], sep = "")
        coefs4[count, 14] <- res$p.value[3]
        coefs4[count, 15] <- res$estimate[4]
        coefs4[count, 16] <- res$`2.5 %`[4]
        coefs4[count, 17] <- res$`97.5 %`[4]
        coefs4[count, 18] <- paste(res$`2.5 %`[4], ",", " ", res$`97.5 %`[4], sep = "")
        coefs4[count, 19] <- res$p.value[4]
      }
    }
  } else {
    for (d in noise) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full_noise %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs4[count, 1] <- gsub(" ", "_", Sys.time())
        coefs4[count, 2] <- o
        coefs4[count, 3] <- d
        coefs4[count, 4] <- m
        coefs4[count, 5] <- res$estimate[2]
        coefs4[count, 6] <- res$`2.5 %`[2]
        coefs4[count, 7] <- res$`97.5 %`[2]
        coefs4[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs4[count, 9] <- res$p.value[2]
        coefs4[count, 10] <- res$estimate[3]
        coefs4[count, 11] <- res$`2.5 %`[3]
        coefs4[count, 12] <- res$`97.5 %`[3]
        coefs4[count, 13] <- paste(res$`2.5 %`[3], ",", " ", res$`97.5 %`[3], sep = "")
        coefs4[count, 14] <- res$p.value[3]
        coefs4[count, 15] <- res$estimate[4]
        coefs4[count, 16] <- res$`2.5 %`[4]
        coefs4[count, 17] <- res$`97.5 %`[4]
        coefs4[count, 18] <- paste(res$`2.5 %`[4], ",", " ", res$`97.5 %`[4], sep = "")
        coefs4[count, 19] <- res$p.value[4]
      }
    }
  }
}

mod_tbl4 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl4) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out) {
  for (d in noise) {
    sep_coefs <- coefs4 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl4[count, 1] <- o
    mod_tbl4[count, 2] <- paste(d, "_55-59.9", sep = "")
    mod_tbl4[count, 3] <- sep_coefs$Beta1[1]
    mod_tbl4[count, 4] <- sep_coefs$CI1[1]
    mod_tbl4[count, 5] <- sep_coefs$P1[1]
    mod_tbl4[count, 6] <- sep_coefs$Beta1[2]
    mod_tbl4[count, 7] <- sep_coefs$CI1[2]
    mod_tbl4[count, 8] <- sep_coefs$P1[2]
    mod_tbl4[count, 9] <- sep_coefs$Beta1[3]
    mod_tbl4[count, 10] <- sep_coefs$CI1[3]
    mod_tbl4[count, 11] <- sep_coefs$P1[3]
    mod_tbl4[count, 12] <- sep_coefs$Beta1[4]
    mod_tbl4[count, 13] <- sep_coefs$CI1[4]
    mod_tbl4[count, 14] <- sep_coefs$P1[4]
    mod_tbl4[count, 15] <- sep_coefs$cilo1[4]
    mod_tbl4[count, 16] <- sep_coefs$cihi1[4]

    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl4[count, 1] <- o
    mod_tbl4[count, 2] <- paste(d, "_60-64.9 ", sep = "")
    mod_tbl4[count, 3] <- sep_coefs$Beta2[1]
    mod_tbl4[count, 4] <- sep_coefs$CI2[1]
    mod_tbl4[count, 5] <- sep_coefs$P2[1]
    mod_tbl4[count, 6] <- sep_coefs$Beta2[2]
    mod_tbl4[count, 7] <- sep_coefs$CI2[2]
    mod_tbl4[count, 8] <- sep_coefs$P2[2]
    mod_tbl4[count, 9] <- sep_coefs$Beta2[3]
    mod_tbl4[count, 10] <- sep_coefs$CI2[3]
    mod_tbl4[count, 11] <- sep_coefs$P2[3]
    mod_tbl4[count, 12] <- sep_coefs$Beta2[4]
    mod_tbl4[count, 13] <- sep_coefs$CI2[4]
    mod_tbl4[count, 14] <- sep_coefs$P2[4]
    mod_tbl4[count, 15] <- sep_coefs$cilo2[4]
    mod_tbl4[count, 16] <- sep_coefs$cihi2[4]

    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl4[count, 1] <- o
    mod_tbl4[count, 2] <- paste(d, ">=65 ", sep = "")
    mod_tbl4[count, 3] <- sep_coefs$Beta3[1]
    mod_tbl4[count, 4] <- sep_coefs$CI3[1]
    mod_tbl4[count, 5] <- sep_coefs$P3[1]
    mod_tbl4[count, 6] <- sep_coefs$Beta3[2]
    mod_tbl4[count, 7] <- sep_coefs$CI3[2]
    mod_tbl4[count, 8] <- sep_coefs$P3[2]
    mod_tbl4[count, 9] <- sep_coefs$Beta3[3]
    mod_tbl4[count, 10] <- sep_coefs$CI3[3]
    mod_tbl4[count, 11] <- sep_coefs$P3[3]
    mod_tbl4[count, 12] <- sep_coefs$Beta3[4]
    mod_tbl4[count, 13] <- sep_coefs$CI3[4]
    mod_tbl4[count, 14] <- sep_coefs$P3[4]
    mod_tbl4[count, 15] <- sep_coefs$cilo3[4]
    mod_tbl4[count, 16] <- sep_coefs$cihi3[4]
  }
}

mod_tbl4 <- mod_tbl4 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome == "AL_2_tot"~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome == "AL_2_tot"~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl4, file = paste("/Users/ymou/helix_project/results/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)

lden_h <- glm(
  data = complete(imp_full, n = 25), formula = AL_z2_tot ~ hs_lden_c_s + e3_sex + hs_child_age_years + h_ethnicity_cauc + cohort + hs_mvpa + hs_sd_wk + FAS_cat + h_native_2cat + h_edumc + h_edufc + h_marital_2cat + h_age + h_parity + e3_asmokyn_p + e3_alcpreg_yn + hs_globalexp_2cat,
  family = "gaussian"
)

plot(lden_h)
summary(lden_h)
```


# Noise home, school and outcomes per physiological systems
EDEN removed in the analysis because no data available. 
```{r}
analysis <- "noise_outcomepsystem"

imp_full_noise <- complete(imp_full, "long", include = T) %>%
  filter(cohort != "EDEN") %>%
  as.mids()

coefs5 <- as.data.frame(matrix(NA, nrow = 1, ncol = 19))
colnames(coefs5) <- c(
  "DateTime", "Outcome", "Predictor", "Model", "Beta1", "cilo1", "cihi1", "CI1", "P1",
  "Beta2", "cilo2", "cihi2", "CI2", "P2", "Beta3", "cilo3", "cihi3", "CI3", "P3"
)

count <- 0
for (o in out_ps) {
  if (o %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro")) {
    for (d in noise) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full_noise %>%
          mice::complete("all") %>%
          lapply(glm.nb, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), link = "log")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs5[count, 1] <- gsub(" ", "_", Sys.time())
        coefs5[count, 2] <- o
        coefs5[count, 3] <- d
        coefs5[count, 4] <- m
        coefs5[count, 5] <- res$estimate[2]
        coefs5[count, 6] <- res$`2.5 %`[2]
        coefs5[count, 7] <- res$`97.5 %`[2]
        coefs5[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs5[count, 9] <- res$p.value[2]
        coefs5[count, 10] <- res$estimate[3]
        coefs5[count, 11] <- res$`2.5 %`[3]
        coefs5[count, 12] <- res$`97.5 %`[3]
        coefs5[count, 13] <- paste(res$`2.5 %`[3], ",", " ", res$`97.5 %`[3], sep = "")
        coefs5[count, 14] <- res$p.value[3]
        coefs5[count, 15] <- res$estimate[4]
        coefs5[count, 16] <- res$`2.5 %`[4]
        coefs5[count, 17] <- res$`97.5 %`[4]
        coefs5[count, 18] <- paste(res$`2.5 %`[4], ",", " ", res$`97.5 %`[4], sep = "")
        coefs5[count, 19] <- res$p.value[4]
      }
    }
  } else {
    for (d in noise) {
      for (m in 1:length(model)) {
        count <- count + 1
        fit <- imp_full_noise %>%
          mice::complete("all") %>%
          lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
        res <- summary(pool(fit), conf.int = T)
        # Round values
        res <- res %>%
          mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
          mutate_at(c("p.value"), round, 4)

        # Save results
        coefs5[count, 1] <- gsub(" ", "_", Sys.time())
        coefs5[count, 2] <- o
        coefs5[count, 3] <- d
        coefs5[count, 4] <- m
        coefs5[count, 5] <- res$estimate[2]
        coefs5[count, 6] <- res$`2.5 %`[2]
        coefs5[count, 7] <- res$`97.5 %`[2]
        coefs5[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
        coefs5[count, 9] <- res$p.value[2]
        coefs5[count, 10] <- res$estimate[3]
        coefs5[count, 11] <- res$`2.5 %`[3]
        coefs5[count, 12] <- res$`97.5 %`[3]
        coefs5[count, 13] <- paste(res$`2.5 %`[3], ",", " ", res$`97.5 %`[3], sep = "")
        coefs5[count, 14] <- res$p.value[3]
        coefs5[count, 15] <- res$estimate[4]
        coefs5[count, 16] <- res$`2.5 %`[4]
        coefs5[count, 17] <- res$`97.5 %`[4]
        coefs5[count, 18] <- paste(res$`2.5 %`[4], ",", " ", res$`97.5 %`[4], sep = "")
        coefs5[count, 19] <- res$p.value[4]
      }
    }
  }
}

mod_tbl5 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl5) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps) {
  for (d in noise) {
    sep_coefs <- coefs5 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, "_55-59.9", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta1[1]
    mod_tbl5[count, 4] <- sep_coefs$CI1[1]
    mod_tbl5[count, 5] <- sep_coefs$P1[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta1[2]
    mod_tbl5[count, 7] <- sep_coefs$CI1[2]
    mod_tbl5[count, 8] <- sep_coefs$P1[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta1[3]
    mod_tbl5[count, 10] <- sep_coefs$CI1[3]
    mod_tbl5[count, 11] <- sep_coefs$P1[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta1[4]
    mod_tbl5[count, 13] <- sep_coefs$CI1[4]
    mod_tbl5[count, 14] <- sep_coefs$P1[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo1[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi1[4]

    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, "_60-64.9 ", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta2[1]
    mod_tbl5[count, 4] <- sep_coefs$CI2[1]
    mod_tbl5[count, 5] <- sep_coefs$P2[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta2[2]
    mod_tbl5[count, 7] <- sep_coefs$CI2[2]
    mod_tbl5[count, 8] <- sep_coefs$P2[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta2[3]
    mod_tbl5[count, 10] <- sep_coefs$CI2[3]
    mod_tbl5[count, 11] <- sep_coefs$P2[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta2[4]
    mod_tbl5[count, 13] <- sep_coefs$CI2[4]
    mod_tbl5[count, 14] <- sep_coefs$P2[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo2[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi2[4]

    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, ">=65 ", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta3[1]
    mod_tbl5[count, 4] <- sep_coefs$CI3[1]
    mod_tbl5[count, 5] <- sep_coefs$P3[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta3[2]
    mod_tbl5[count, 7] <- sep_coefs$CI3[2]
    mod_tbl5[count, 8] <- sep_coefs$P3[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta3[3]
    mod_tbl5[count, 10] <- sep_coefs$CI3[3]
    mod_tbl5[count, 11] <- sep_coefs$P3[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta3[4]
    mod_tbl5[count, 13] <- sep_coefs$CI3[4]
    mod_tbl5[count, 14] <- sep_coefs$P3[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo3[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi3[4]
  }
}

mod_tbl5 <- mod_tbl5 %>% 
  mutate(exp_beta_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(beta_mod4)),
         exp_cilo_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cilo_mod4)),
         exp_cihi_mod4 = case_when(Outcome %in% c("AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro") ~ exp(cihi_mod4))) %>% 
  mutate_at(c("exp_beta_mod4", "exp_cilo_mod4", "exp_cihi_mod4"), round, 2) %>% 
  mutate(exp_ci_mod4 = paste(format(exp_cilo_mod4,drop0Trailing = F), ", ", format(exp_cihi_mod4,drop0Trailing = F), sep = ""))

write.xlsx(mod_tbl5, file = paste("/Users/ymou/helix_project/results/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```

```{r}
analysis <- "noise_outcomepsystem_zscore"

imp_full_noise <- complete(imp_full, "long", include = T) %>%
  filter(cohort != "EDEN") %>%
  as.mids()

coefs5 <- as.data.frame(matrix(NA, nrow = 1, ncol = 19))
colnames(coefs5) <- c(
  "DateTime", "Outcome", "Predictor", "Model", "Beta1", "cilo1", "cihi1", "CI1", "P1",
  "Beta2", "cilo2", "cihi2", "CI2", "P2", "Beta3", "cilo3", "cihi3", "CI3", "P3"
)

count <- 0
for (o in out_ps_z) {
  for (d in noise) {
    for (m in 1:length(model)) {
      count <- count + 1
      fit <- imp_full_noise %>%
        mice::complete("all") %>%
        lapply(glm, formula = paste(o, "~", d, "+", model[m], " + cohort", sep = ""), family = "gaussian")
      res <- summary(pool(fit), conf.int = T)
      # Round values
      res <- res %>%
        mutate_at(c("estimate", "2.5 %", "97.5 %"), round, 2) %>%
        mutate_at(c("p.value"), round, 4)

      # Save results
      coefs5[count, 1] <- gsub(" ", "_", Sys.time())
      coefs5[count, 2] <- o
      coefs5[count, 3] <- d
      coefs5[count, 4] <- m
      coefs5[count, 5] <- res$estimate[2]
      coefs5[count, 6] <- res$`2.5 %`[2]
      coefs5[count, 7] <- res$`97.5 %`[2]
      coefs5[count, 8] <- paste(res$`2.5 %`[2], ",", " ", res$`97.5 %`[2], sep = "")
      coefs5[count, 9] <- res$p.value[2]
      coefs5[count, 10] <- res$estimate[3]
      coefs5[count, 11] <- res$`2.5 %`[3]
      coefs5[count, 12] <- res$`97.5 %`[3]
      coefs5[count, 13] <- paste(res$`2.5 %`[3], ",", " ", res$`97.5 %`[3], sep = "")
      coefs5[count, 14] <- res$p.value[3]
      coefs5[count, 15] <- res$estimate[4]
      coefs5[count, 16] <- res$`2.5 %`[4]
      coefs5[count, 17] <- res$`97.5 %`[4]
      coefs5[count, 18] <- paste(res$`2.5 %`[4], ",", " ", res$`97.5 %`[4], sep = "")
      coefs5[count, 19] <- res$p.value[4]
    }
  }
}

mod_tbl5 <- as.data.frame(matrix(NA, nrow = 1, ncol = 16))
colnames(mod_tbl5) <- c(
  "Outcome", "Predictor",
  "beta_mod1", "95ci_mod1", "pvalue_mod1",
  "beta_mod2", "95ci_mod2", "pvalue_mod2",
  "beta_mod3", "95ci_mod3", "pvalue_mod3",
  "beta_mod4", "95ci_mod4", "pvalue_mod4",
  "cilo_mod4", "cihi_mod4"
)
count <- 0


for (o in out_ps_z) {
  for (d in noise) {
    sep_coefs <- coefs5 %>%
      filter(Outcome == o) %>%
      filter(Predictor == d)
    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, "_55-59.9", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta1[1]
    mod_tbl5[count, 4] <- sep_coefs$CI1[1]
    mod_tbl5[count, 5] <- sep_coefs$P1[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta1[2]
    mod_tbl5[count, 7] <- sep_coefs$CI1[2]
    mod_tbl5[count, 8] <- sep_coefs$P1[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta1[3]
    mod_tbl5[count, 10] <- sep_coefs$CI1[3]
    mod_tbl5[count, 11] <- sep_coefs$P1[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta1[4]
    mod_tbl5[count, 13] <- sep_coefs$CI1[4]
    mod_tbl5[count, 14] <- sep_coefs$P1[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo1[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi1[4]

    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, "_60-64.9 ", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta2[1]
    mod_tbl5[count, 4] <- sep_coefs$CI2[1]
    mod_tbl5[count, 5] <- sep_coefs$P2[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta2[2]
    mod_tbl5[count, 7] <- sep_coefs$CI2[2]
    mod_tbl5[count, 8] <- sep_coefs$P2[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta2[3]
    mod_tbl5[count, 10] <- sep_coefs$CI2[3]
    mod_tbl5[count, 11] <- sep_coefs$P2[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta2[4]
    mod_tbl5[count, 13] <- sep_coefs$CI2[4]
    mod_tbl5[count, 14] <- sep_coefs$P2[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo2[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi2[4]


    count <- count + 1
    # Loop through each model.In this case, four models
    mod_tbl5[count, 1] <- o
    mod_tbl5[count, 2] <- paste(d, ">=65 ", sep = "")
    mod_tbl5[count, 3] <- sep_coefs$Beta3[1]
    mod_tbl5[count, 4] <- sep_coefs$CI3[1]
    mod_tbl5[count, 5] <- sep_coefs$P3[1]
    mod_tbl5[count, 6] <- sep_coefs$Beta3[2]
    mod_tbl5[count, 7] <- sep_coefs$CI3[2]
    mod_tbl5[count, 8] <- sep_coefs$P3[2]
    mod_tbl5[count, 9] <- sep_coefs$Beta3[3]
    mod_tbl5[count, 10] <- sep_coefs$CI3[3]
    mod_tbl5[count, 11] <- sep_coefs$P3[3]
    mod_tbl5[count, 12] <- sep_coefs$Beta3[4]
    mod_tbl5[count, 13] <- sep_coefs$CI3[4]
    mod_tbl5[count, 14] <- sep_coefs$P3[4]
    mod_tbl5[count, 15] <- sep_coefs$cilo3[4]
    mod_tbl5[count, 16] <- sep_coefs$cihi3[4]
  }
}


write.xlsx(mod_tbl5, file = paste("/Users/ymou/helix_project/results/", analysis, analysis_date, ".xlsx", sep = ""), rowNames = FALSE, colNames = TRUE)
```
