---
title: "Supplementary materials"
author: "Yuchan Mou"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.table.format = "html")
```

```{r load packages, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages <- c("dplyr", "tidyverse", "tableone", "kableExtra", "ggplot2", "ggcorrplot")
sapply(packages, library, character.only = T)
```

```{r import data, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
load("/Users/ymou/helix_project/data/analysis_data/df_al_final_manipulated.RData")
Sys.Date()
```

```{r define variables, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
expo <- c(
  "hs_no2_yr_hs_t", "hs_no2_yr_hs_h", "hs_no2_yr_hs_s", "hs_no2_yr_hs_r",
  "hs_pm25_yr_hs_t", "hs_pm25_yr_hs_h", "hs_pm25_yr_hs_s", "hs_pm25_yr_hs_r",
  "hs_pm25abs_yr_hs_t", "hs_pm25abs_yr_hs_h", "hs_pm25abs_yr_hs_s", "hs_pm25abs_yr_hs_r",
  "hs_pm10_yr_hs_t", "hs_pm10_yr_hs_h", "hs_pm10_yr_hs_s", "hs_pm10_yr_hs_r",
  "hs_lden_c_h", "hs_lden_c_s"
)
exponame <- c(
  "NO2-total", "NO2-home", "NO2-school", "NO2-commuting",
  "PM2.5-total", "PM2.5-home", "PM2.5-school", "PM2.5-commuting",
  "PM2.5abs-total", "PM2.5abs-home", "PM2.5abs-school", "PM2.5abs-commuting",
  "PM10-total", "PM10-home", "PM10-school", "PM10-commuting",
  "Noise-home", "Noise-school"
)

mainexpo <- c("hs_no2_yr_hs_t", "hs_pm25_yr_hs_t", "hs_pm25abs_yr_hs_t", "hs_pm10_yr_hs_t", "hs_lden_c_h", "hs_lden_c_s")

biomarker_name <- c(
  "SBP", "DBP", "Pulse rate",
  "BMI", "Waist circumference", "Skinfold thickness", "Fat mass",
  "HDL-C", "Non-HDL-C", "Triglycerides", "Leptin",
  "Adiponectin",
  "CRP", "IL-1B", "IL-6", "IL-8", "IL-10", "TNFa",
  "Cortisol production"
)

out <- c(
  "AL_2_tot", "AL_2_cardio", "AL_2_metab", "AL_2_immune", "AL_2_neuro",
  "AL_z2_tot", "AL_z2_cardio", "AL_z2_metab", "AL_z2_immune", "AL_z2_neuro"
)
mainout <- c("AL_2_tot", "AL_z2_tot")

outname <- c(
  "Count-based ALS",
  "Count-based cardiovascular ALS",
  "Count-based metabolic ALS",
  "Count-based immune/imflammatory ALS",
  "Count-based neuroendorine ALS",
  "Continuous ALS",
  "Continuous cardiovascular ALS",
  "Continuous metabolic ALS",
  "Continuous immune/imflammatory ALS",
  "Continuous neuroendorine ALS"
)

cov <- c(
  "e3_sex", "hs_mvpa", "hs_sd_wk", "hs_child_age_years",
  "FAS_cat", "h_native_2cat", "h_ethnicity_cauc", "h_edumc", "h_edufc",
  "hs_smk_parents", "hs_globalexp_2cat", "e3_asmokyn_p", "e3_alcpreg_yn", "h_marital_2cat", "h_age", "h_parity"
)
catcov <- c(
  "e3_sex", "FAS_cat", "h_native", "h_ethnicity_cauc", "h_edumc", "h_edufc",
  "hs_smk_parents", "hs_globalexp_2cat", "e3_asmokyn_p", "e3_alcpreg_yn", "h_marital", "h_parity"
)
nonnormalvars <- c("hs_child_age_years", "hs_mvpa", "hs_sd_wk")
```

AL_2 is a sex-specific count-based scores, AL_z2 is a sex-specific continuous scores. The completeness of data is the same among all outcomes. Use AL_2_tot as an example for the responders vs non-responder analysis.

# Non-response to outcome measures

```{r nonresponders}
# 923 with AL, 919 with both air pollutants and AL
df <- df_final %>% filter(!is.na(hs_no2_yr_hs_t))
df$respond <- as.factor(if_else(is.na(df$AL_2_tot), 0, 1, NA)) # 1 as respondents to biomarkers

df <- df %>%
  mutate(
    h_native_2cat = fct_collapse(h_native,
      "None or one native" = c("None native", "One native"),
      "Both native" = "Both native"
    ),
    hs_globalexp_2cat = fct_collapse(hs_globalexp,
      "No" = "No",
      "Yes" = c("Outside", "Inside", "In and outside house")
    ),
    h_marital_2cat = fct_collapse(h_marital,
      "Living with the father" = "Living with the father",
      "Other situation" = c("Living alone", "Other situation")
    )
  )

tbl <- CreateTableOne(
  data = df,
  vars = cov,
  factorVars = catcov,
  strata = c("respond", "cohort")
)

tab_csv <- print(tbl,
  showAllLevels = TRUE, nonnormal = nonnormalvars, contDigits = 1, catDigits = 1, noSpaces = T, format = "fp"
)


write.csv(tab_csv, file = "/Users/ymou/helix_project/results/nonrespondents.csv")
```


# Correlations among allostatic load score
```{r corr_al}
df <- df_final %>% filter(!is.na(hs_no2_yr_hs_t & AL_2_tot))
cor.test(df$AL_2_tot, df$AL_z2_tot)

df <- df %>%
  rename(
    `Count-based ALS` = "AL_2_tot",
    `Count-based cardiovascular ALS` = "AL_2_cardio",
    `Count-based metabolic ALS` = "AL_2_metab",
    `Count-based immune/imflammatory ALS` = "AL_2_immune",
    `Count-based neuroendorine ALS` = "AL_2_neuro",
    `Continuous ALS` = "AL_z2_tot",
    `Continuous cardiovascular ALS` = "AL_z2_cardio",
    `Continuous metabolic ALS` = "AL_z2_metab",
    `Continuous immune/imflammatory ALS` = "AL_z2_immune",
    `Continuous neuroendorine ALS` = "AL_z2_neuro"
  )
```

Main outcomes and outcomes per system
```{r}
df %>%
  dplyr::select(all_of(outname)) %>%
  cor(use = "pairwise.complete.obs", method = "pearson") %>%
  ggcorrplot(
    hc.order = F,
    type = "lower",
    lab = TRUE
  )

ggsave("/Users/ymou/helix_project/results/Fig/corr_outcomes.png", width = 10, height = 10, units = "in", dpi = 300)
```

# Correlation among biomarkers
```{r}
df <- df_final %>% filter(!is.na(hs_no2_yr_hs_t & AL_2_tot))
df <- df %>%
  rename(
    `SBP` = "hs_zsys_bp", `DBP` = "hs_zdia_bp", `Pulse rate` = "bp_pulse_sd",
    `BMI` = "hs_zbmi_who", `Waist circumference` = "hs_zwaist_mets", `Skinfold thickness` = "hs_skf_sum2",
    `Fat mass` = "hs_fatprop_bia",
    `HDL-C` = "hs_hdlchol_c", `Non-HDL-C` = "hs_non_hdl_c", `Triglycerides` = "hs_triglyc_c", `Leptin` = "Leptin",
    `Adiponectin` = "Adiponectin",
    `CRP` = "CRP", `IL-1B` = "IL1beta", `IL-6` = "IL6", `IL-8` = "IL8", `IL-10` = "IL10", `TNFa` = "TNFalfa",
    `Cortisol production` = "cortisol_prod_log10"
  )

df %>%
  dplyr::select(all_of(biomarker_name)) %>%
  cor(use = "pairwise.complete.obs", method = "pearson") %>%
  ggcorrplot(
    hc.order = F,
    type = "lower",
    lab = TRUE
  )

ggsave("/Users/ymou/helix_project/results/Fig/corr_biomarkers.png", width = 10, height = 10, units = "in", dpi = 300)
```

# Correlation between air pollutants
For the continuous-continuous pairs, Pearson correlation was used. For the continuous-categorical pairs, ANOVA was used to calculate the association, and for categorical-categorical pairs, Cramér's V was used. 
```{r corr_biomarkers, fig.width=10, fig.height=10}
df <- df_final %>% filter(!is.na(hs_no2_yr_hs_t & AL_2_tot))

df <- df %>%
  select(all_of(expo)) %>%
  rename(
    `NO2-total` = "hs_no2_yr_hs_t",
    `NO2-home` = "hs_no2_yr_hs_h",
    `NO2-school` = "hs_no2_yr_hs_s",
    `NO2-commuting` = "hs_no2_yr_hs_r",
    `PM2.5-total` = "hs_pm25_yr_hs_t",
    `PM2.5-home` = "hs_pm25_yr_hs_h",
    `PM2.5-school` = "hs_pm25_yr_hs_s",
    `PM2.5-commuting` = "hs_pm25_yr_hs_r",
    `PM2.5abs-total` = "hs_pm25abs_yr_hs_t",
    `PM2.5abs-home` = "hs_pm25abs_yr_hs_h",
    `PM2.5abs-school` = "hs_pm25abs_yr_hs_s",
    `PM2.5abs-commuting` = "hs_pm25abs_yr_hs_r",
    `PM10-total` = "hs_pm10_yr_hs_t",
    `PM10-home` = "hs_pm10_yr_hs_h",
    `PM10-school` = "hs_pm10_yr_hs_s",
    `PM10-commuting` = "hs_pm10_yr_hs_r",
    `Noise-home` = "hs_lden_c_h",
    `Noise-school` = "hs_lden_c_s"
  )

library(lsr) # for Eta-Squared
# Function to calculate Cramér's V
cramers_v <- function(x, y) {
  tbl <- table(x, y) # Contingency table
  chi2 <- chisq.test(tbl)$statistic # Chi-squared statistic
  n <- sum(tbl) # Total number of observations
  return(sqrt(chi2 / (n * (min(ncol(tbl), nrow(tbl)) - 1))))
}

# Initialize a matrix to store the results
var_names <- exponame[1:18]
cor_matrix <- matrix(NA,
  nrow = length(var_names), ncol = length(var_names),
  dimnames = list(var_names, var_names)
)
count_i <- 0


# Loop through pairs to calculate associations, handling missing values
for (i in var_names) {
  count_i <- count_i + 1
  count_j <- 0

  # Break outer loop if count_i reaches 18
  if (count_i > 18) break

  for (j in var_names) {
    count_j <- count_j + 1

    # Break inner loop if count_j reaches 18
    if (count_j > 18) break

    if (is.numeric(df[[i]]) && is.numeric(df[[j]])) {
      cor_matrix[count_i, count_j] <- cor(df[[i]], df[[j]], use = "complete.obs")

      # Handling Continuous-Categorical Pairs
    } else if (is.numeric(df[[i]]) && is.factor(df[[j]])) {
      valid_data <- df %>%
        filter(!is.na(.data[[i]]) & !is.na(.data[[j]])) %>%
        select(all_of(c(i, j))) # Remove rows with missing values
      if (nrow(valid_data) > 0) { # Check if there's anj data left after removing NAs
        aov_model <- aov(valid_data[[i]] ~ valid_data[[j]], data = valid_data)
        cor_matrix[count_i, count_j] <- sqrt(etaSquared(aov_model)[1])
      }
    } else if (is.factor(df[[i]]) && is.numeric(df[[j]])) {
      valid_data <- df %>%
        filter(!is.na(.data[[i]]) & !is.na(.data[[j]])) %>%
        select(all_of(c(i, j))) # Remove rows with missing values
      if (nrow(valid_data) > 0) { # Check if there's anj data left after removing NAs
        aov_model <- aov(valid_data[[j]] ~ valid_data[[i]], data = valid_data)
        cor_matrix[count_i, count_j] <- sqrt(etaSquared(aov_model)[1])
      }

      # Handling Categorical-Categorical Pairs
    } else if (is.factor(df[[i]]) && is.factor(df[[j]])) {
      valid_data <- df %>%
        filter(!is.na(.data[[i]]) & !is.na(.data[[j]])) %>%
        select(all_of(c(i, j))) # Remove rows with missing values
      if (nrow(valid_data) > 0) {
        cor_matrix[count_i, count_j] <- cramers_v(valid_data[[i]], valid_data[[j]])
      }
    }
  }
}

# Visualize the correlation matrix using ggcorrplot
ggcorrplot(cor_matrix, 
           method = "square", 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           title = "", 
           ggtheme = ggplot2::theme_minimal())

ggsave("/Users/ymou/helix_project/results/Fig/corr_expo.png", width = 10, height = 10, units = "in", dpi = 300)
```

# Correlation between noise level at home and at school, categorical variable
```{r corr_noise_cat}
library(polycor)

table(df$hs_lden_c_h, df$hs_lden_c_s)

# calculate polychoric correlation
t <- polychor(df$hs_lden_c_h, df$hs_lden_c_s, ML = T, std.err = T)
```
