---
title: "Air pollution, noise level and allostatic load score"
subtitle: "HELIX Study"
author: "Yuchan Mou"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
  css: [default, rutgers, rutgers-fonts]
  seal: false # false: custom title slide
  nature:
    highlightStyle: arta # highlighting syntax for code
    highlightlines: true # true: enables code line highlighting
    highlightLanguage: ["r"]
    conutIncrementalSlides: false  # false: disables counting of incremental slides
    ratio: "16:9"   
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r load pkg, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# load pkgs
packages <- c("dplyr", "tidyverse", "readxl", "openxlsx", "scales", "ggplot2", "gtools", "kableExtra", "DT", "xaringan", "ggcorrplot") 
sapply(packages, library, character.only = T)
```

```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('/Users/ymou/helix_project/code/helix-allostasis/3a_descriptive_analysis_all_raw_data.R')
knitr::read_chunk('/Users/ymou/helix_project/code/helix-allostasis/2_allostatic_score.R')
```

```{r table, include=FALSE}
al <- read_excel("/Users/ymou/helix_project/data/AL_biomarkers.xlsx", sheet = "AL_biomarker_table")
steroid <- read_excel("/Users/ymou/helix_project/data/AL_biomarkers.xlsx", sheet = "Steroid_profile")
corticosteroids <- read_excel("/Users/ymou/helix_project/data/AL_biomarkers.xlsx", sheet = "corticosteroids_urine")
```

---
## Overview

- Biomarkers included in the allostatic load index
- Overview of distribution of biomarkers
- Overview of allostatic load score
- Corticosteroids data 

---
## Biomarkers included in the allostatic load index

```{r}
al %>%
  filter(includeinscore_oct_18 == "Yes") %>% 
  select(-c("includeinscore_oct_18", `Overview of biomarker function`, `Relationship with stress response/allostatic load theory`, "remarks", "referecnes")) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("condensed", "responsive"), full_width = T, position = "left", font_size = 14, fixed_thead = T) %>% 
  #row_spec(which(al$Biomarkers %in% c("Cardiovascular", "Metabolic", "Immune/Inflammatory", "Neuroendocrine")), color = "black", background = "#bdbdbd") %>% 
  scroll_box(width = "100%", height = "80%")
```

---
## Overview of distribution of biomarkers
```{r import data3, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
```

```{r descriptive statistic func, echo=FALSE}
```

- Cardiovascular biomarkers - blood pressure

```{r cardio_plot_by_cohort, out.width="60%", fig.align = "center"}
```

---
- Cardiovascular biomarkers - anthropometric measures

```{r anthropometrics_plot_by_cohort, fig.align = "center"}
```

---
- Metabolic biomarkers

```{r metabolic_plot_by_cohort, fig.align = "center"}
```

---
- Inflammatory biomarkers

```{r immune_plot_by_cohort, fig.align = "center"}
```

---
## Overview of allostatic load score
- Traditional score: sum of quartiles
```{r import data2, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
```

```{r define biomarkers, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
```

```{r AL score calc function, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
```

.pull-left[ 
- Grils

```{r, allostatic score 1 quantile based girls, echo=FALSE, results='hide', fig.show='hold', fig.align = "center", out.width = "60%"}
```
]

.pull-right[ 
- Boys

```{r, allostatic score 1 quantile based boys, echo=FALSE, results='hide', fig.show='hold', fig.align = "center", out.width = "60%"}
```
]

---
- z score

.pull-left[ 
- Grils

```{r, allostatic score z quantile based girls, echo=FALSE, results='hide', fig.show='hold', fig.align = "center", out.width = "70%"}
```
]

.pull-right[ 
- Boys

```{r, allostatic score z quantile based boys, echo=FALSE, results='hide', fig.show='hold', fig.align = "center", out.width = "70%"}
```
]

---
## Steroid profile - Urine sample

```{r}
steroid %>% kable() %>% 
  kable_styling(bootstrap_options = c("condensed", "responsive"), full_width = F, position = "left", font_size = 14, fixed_thead = T) %>% 
  scroll_box(width = "100%", height = "80%")
```

---
## Corticosteroids - Urine sample
```{r}
corticosteroids %>% kable() %>% 
  kable_styling(bootstrap_options = c("condensed", "responsive"), full_width = F, position = "left", font_size = 14, fixed_thead = T) %>% 
  scroll_box(width = "100%", height = "80%")
```

